### 2014-11-14 paper.tex
First commit

%!TEX program = xelatex
\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm2e}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\usepackage{fontspec}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{407} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\def\vec{\mathbf}
\def\mat{\mathbf}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

\RestyleAlgo{boxruled}

%%%%%%%%% TITLE
\title{Learning From Massive Weakly Labeled Data for Visual Classification}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale strongly supervised datasets are crucial to train deep neural networks for various computer vision problems. Obtaining such well labeled data is usually expensive, but collecting weakly labeled data is much more effortless. In this paper we study how to train a deep neural network to classify objects with limited strong supervisions and massive weakly labeled data. A probabilistic model is proposed to describe the relationship between image data, noisy label and ground truth. We further integrate the model into a deep learning framework. Experiments are conducted on a collected large-scale weakly labeled dataset. The results show that weakly labeled data benefit the training of the deep model, and our approach can further improve the performance.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction} % (fold)
\label{sec:introduction}
Visual classification, which aims at categorizing objects into predefined semantic groups, is a traditional yet fundamental problem in computer vision. Starting from the pioneering work in~\cite{krizhevsky2012imagenet}, researchers have developed various deep learning approaches to solve object classification problem. While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all the methods rely on large-scale strongly supervised training dataset~\cite{deng2009imagenet}, which consumes a lot of manpower to label millions of images. In many real-world applications, we can only get limited well labeled data. Training a deep neural network is thus difficult even if we finetune it from a pretrained ImageNet model. However, we can easily get substantial weakly supervised data by crawling images from the Internet and extracting keywords from their surrounding text. For example, product photos on \emph{Amazon} and \emph{Taobao} usually have relatively reasonable title and tags, which can be converted to weak object class and attributes. Thus it drives us to find some effective ways to do visual recognition by utilizing these massive information.

Without losing generality, we focus on the task of clothes recognition, \ie, determining whether an image is about a T-shirt, a sweater, or a dress, \etc. This specific object classification problem draws much attention to many e-commerce companies, since it is a basic building block of products retrieval and recommendation systems.  The major challenge of using weakly labeled data in training classifier is to identify bad samples and keep them from drifting the model. Figure~\ref{fig:overview} shows some examples of label noise. Existing methods try to solve this problem from two aspects. One way is to model the relationship between true label and noisy label, but the model is too simple to fit in real-world applications. The other one exploits semi-supervised learning algorithms (such as label propagation), but their complexities are usually quadratic with the number of samples, thus cannot be applied on large-scale datasets.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\linewidth]{figure/overview.pdf}
\end{center}
\caption{Overview of our method. Weak labels often suffer from pointless (red) or confusing noise (orange). Our model infers true label (green) based on observed image and weak label, as well as CNN predictions about object class and noise type.}
\label{fig:overview}
\end{figure}

To conquer this problem, we first study why a weak label goes wrong and conclude two types of label noise:
\begin{itemize}
   \item \textbf{Pointless noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}. This kind of noise is often caused by either the mismatch between web image and surrounding text, or false conversion from text to label. The noisy label in this case is not acceptable.
   \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one. This kind of noise happens regularly in some sort of images. For example, the knitwear in the lower orange box of Figure~\ref{fig:overview} can be often misclassified as a sweater. However, in real applications, confusion among several related labels is generally acceptable to users.
\end{itemize}

Our goal is to identify the ground truth label given an image as well as its weak label, and then use the ground truth label as supervision instead of the weak one. Intuitively, we have two kinds of evidence to help us make decision. One comes from the ground truth labels of other similar images, and the other one comes from how confusing is the input image itself. In this paper, we model these two kinds of information as latent variables and use them to bridge the semantic gap between our observed image and weak label. A novel probabilistic model is proposed to build relations among all these factors. We solve the problem by Expectation-Maximization (EM) algorithm and integrate it into a deep learning framework. To validate our approach, we collected a clothes image dataset consisting of about $72,000$ strongly labeled and one million weakly labeled data. Experiments on this dataset show that massive weakly labeled data benefit the training of deep neural networks, and our approach can further improve the performance.

Our contribution comes from two aspects. First, we investigate the cause of weak label in real-world data, and formulate the label noise in a probabilistic model. Second, we integrate the proposed model into a deep learning framework to help it resist bad supervision in training with weakly labeled data.

% section related_work (end)

\section{Related Work} % (fold)
\label{sec:related_work}
Various methods have been proposed to handle label noise in different problem settings. Our work is inspired by~\cite{sukhbaatar2014learning}, where they linearly map the probability distribution of the true label to that of the noisy label. But their assumption --- noisy label and input image are conditionally independent given the true label --- is too strong. It cannot figure out whether an observed label is correct or not. Our proposed method overcomes this problem by first estimating how likely an image suffers from pointless or confusing noise. And then predicting the true label based on this information and our observed noisy label.

Other methods model noisy labels in different context, \eg, visual attributes annotation~\cite{vahdat2013handling}, or roads recognition in aerial images~\cite{mnih2012learning}. It is non-trivial to generalize their approaches to solver our problem, \ie, multi-class object classification.

Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data. Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples. However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets. Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features. But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.

The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features. However, the model parameters cannot be properly learned when training data is not enough. Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task~\cite{krizhevsky2012imagenet,oquab2013learning,azizpour2014generic}. Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related. In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.

% section related_work (end)

\section{Label Noise Model} % (fold)
\label{sec:label_noise_model}
We target on the problem of learning a classifier from a set of weakly labeled image data. To be specific, we have a weakly labeled dataset $\mathcal{D}_w=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes. Based on previous analysis of the noise types, we describe how the weak label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}. Despite the observed image $\vec{x}$ and the weak label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively. Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.6\linewidth]{figure/pgm.pdf}
\end{center}
\caption{Probabilistic graphical model of label noise}
\label{fig:noise_pgm}
\end{figure}

On the other hand, the latent variable $\vec{z}$ representing label noise type is also an 1-of-3 binary random variable. We assign three semantic meanings to each possible state of $\vec{z}$:
\begin{enumerate}
    \item The weak label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
    \item The weak label suffers from a pointless noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
    \item The weak label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
\end{enumerate}

Following this assignment rule, we define the conditional probability of the weak label by
\begin{equation} \label{eq:likelihood}
    p(\tilde{\vec{y}}|\vec{y},\vec{z}) = \begin{cases}
        \mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
        \frac{1}{L-1}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
        \mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
    \end{cases}
\end{equation}
where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are one), and $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denoting the confusion probability between class $i$ and $j$. Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
\begin{equation} \label{eq:joint_distribution}
  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x})
\end{equation}

While the object class probability distribution $p(\vec{y} | \vec{x})$ is comprehensible, the semantic meaning of $p(\vec{z} | \vec{x})$ needs extra clarification: it can be seen as a property of an image, which represents how confusing the image is. Specific to our clothes classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc. See Figure~\ref{fig:compare_noise_level} for some examples.

\begin{figure}[t]
\begin{center}
\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
\end{center}
\caption{The probability of an image suffering from different noise types depend on the image itself. Although all the images belong to class ``T-shirt'', the top two images can be easily recognized, while the bottom two tend to be confused with class ``Chiffon''.}
\label{fig:compare_noise_level}
\end{figure}

To illustrate the relations between weak label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
\begin{equation}
    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x})
\end{equation}
which can be interpreted as a mixture model. Given an input image $\vec{x}$, the conditional probability $p(\vec{z} | \vec{x})$ can be seen as the prior of each mixture component. This makes a key difference between our work and~\cite{sukhbaatar2014learning}, where they assume $\tilde{\vec{y}}$ is conditionally independent with $\vec{x}$ if $\vec{y}$ is given. All the images share a same noise model in~\cite{sukhbaatar2014learning}, while in our approach each data sample has its own.

\subsection{Learning the Parameters} % (fold)
\label{sub:learning_the_parameters}
We exploit two deep neural networks to model $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ separately. Denote the parameter set of each deep model by $\theta_1$ and $\theta_2$. Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$. Expectation-Maximization algorithm is used to solve this problem iteratively.

For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood by
\begin{equation}
\begin{aligned}
    \log p(\tilde{\vec{y}} | \vec{x}; \theta) &= \log \sum_{\vec{y},\vec{z}} p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}
\end{aligned}
\end{equation}
\textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$. Therefore, in each iteration $t$ of the E-Step, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
\begin{multline} \label{eq:posterior}
    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}} | \vec{y}, \vec{z}, \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
\end{multline}
Then the expected complete log-likelihood can be written as
\begin{equation}
    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)
\end{equation}
\textbf{M-Step} Since deep neural networks are exploited to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, we perform gradient ascent on $Q$:
\begin{multline}
    \frac{\partial Q}{\partial \theta} = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta} \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
    = \sum_{\vec{y},\vec{z}} w(\vec{y},\vec{z}) \left\{\frac{\partial}{\partial \theta_1}\log p(\vec{y}|\vec{x};\theta_1) + \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2) \right\}
\end{multline}
where $w(\vec{y},\vec{z}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)})$ can be treated as the weights of each pair of latent variables.

The semantic meaning of this optimization process is straight forward. We enumerate all the possible true labels, and weight each of them by their posterior probability based on our observation of the image and corresponding noisy label. Then we use these weighted labels to supervise the training of our deep neural networks.
% subsection learning_the_parameters (end)

\subsection{Confusion Estimation} % (fold)
\label{sub:confusion_estimation}
Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process. Because without other regularizations, learning all the three parts could lead to trivial solutions. For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$. To avoid this degeneration, we choose to give $\mat{C}$ a good estimation while let the deep model learn to predict $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ for each input image.

We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_s = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both strong label and weak label. As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
\begin{equation}
    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
\end{equation}
Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal. So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
\begin{equation}
\begin{aligned}
\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } K\times K \\
                    & \vec{t} \in \{0,1\}^{N'}
\end{aligned}
\end{equation}
where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples. The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.

Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+K^2)$ time complexity. Before we introduce the algorithm itself, some theorems need to be proved. Denote the optimal solution by $\mat{C}^*$ and $\vec{t}^*$
\begin{lemma}
$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,K\}$
\end{lemma}
\begin{proof}
Suppose there exists some $i,j$ such that $0 < \mat{C}^*_{ij} \leq \alpha$. Then we conduct following operations. First, we set $\mat{C}^*_{ij}=0$ while adding its original value to other elements in column $j$. Second, for all the samples $n$ where $\tilde{\vec{y}}^{(n)}_i=1$ and $\vec{y}^{(n)}_j=1$, we set $\vec{t}_n$ to 1. The resulting $E$ is always greater than the original one, which leads to a contradiction.
\end{proof}
\begin{theorem}
$(\tilde{\vec{y}}^{(i)},\vec{y}^{(i)})=(\tilde{\vec{y}}^{(j)},\vec{y}^{(j)}) \Rightarrow \vec{t}^*_i=\vec{t}^*_j, \forall i,j \in \{1,\dots,N'\}$
\end{theorem}
\begin{proof}
Suppose $\tilde{\vec{y}}^{(i)}_k=\tilde{\vec{y}}^{(j)}_k=1$ and $\vec{y}^{(i)}_l=\vec{y}^{(j)}_l=1$ but $\vec{t}^*_i \neq \vec{t}^*_j$. From Lemma 1 we know that elements in $\mat{C}^*$ is either 0 or greater than $\alpha$. If $\mat{C}^*_{kl}=0$, we can set $\vec{t}^*_i=\vec{t}^*_j=1$, otherwise we can set $\vec{t}^*_i=\vec{t}^*_j=0$. In either case the objective function $E$ is greater than the original one, which draws a contradiction.
\end{proof}
\begin{theorem}
$\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} > \alpha \Leftrightarrow \vec{t}^*_i=0$ and $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0 \Leftrightarrow \vec{t}^*_i=1, \forall i \in \{1,\dots,N'\}$
\end{theorem}
\begin{proof}
The first part is straight forward. For the second part, $\vec{t}^*_i=1$ implies $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} \leq \alpha$. By using Lemma 1 we know that $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0$.
\end{proof}

Notice that if the true label of an image is class $i$ while the noisy label is class $j$, then it can only affect the value of $\mat{C}_{ij}$. Thus each column of $\mat{C}$ can be optimized separately. Theorem 1 further shows that samples with same pair of $(\tilde{\vec{y}},\vec{y})$ share a same noise type. Then what really matters is the frequency of each of the $K\times K$ pairs $(\tilde{\vec{y}},\vec{y})$. Considering a particular column $\vec{c}$, suppose there are $M$ samples affecting this column. We can count the frequency of noisy label class 1 to $K$ as $m_1,\dots,m_K$ and might as well set $m_1\geq m_2\geq \cdots \geq m_K$. The problem is then converted to
\begin{equation}
\begin{aligned}
\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{K} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right)\\
\text{subject to} \quad & \vec{c} \in [0,1]^K, \sum_{k=1}^{K} \vec{c}_k = 1 \\
                    & \vec{t} \in \{0,1\}^{K}
\end{aligned}
\end{equation}

Due to the rearrangement inequality, we can prove that in the optimal solution,
\begin{equation}
    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_K)
\end{equation}
Then by using Theorem 2, there must exist a $k^* \in \{1,\dots,K\}$ such that
\begin{equation} \label{eq:opt_t}
\begin{aligned}
    &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
    &\vec{t}^*_i = 1, i = k^*+1,\dots,K
\end{aligned}
\end{equation}
This also implies that only the first $k^*$ elements of $\vec{c}^*$ have nonzero values (greater than $\alpha$ actually). Furthermore, if $k^*$ is known, finding the optimal $\vec{c}^*$ is to solve the following problem:
\begin{equation}
\begin{aligned}
\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k\\
\text{subject to} \quad & \vec{c} \in [0,1]^K, \sum_{k=1}^{k^*} \vec{c}_k = 1
\end{aligned}
\end{equation}
whose solution is
\begin{equation} \label{eq:opt_c}
\begin{aligned}
    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^* \\
    &\vec{c}^*_i = 0, i = k^*+1,\dots,K
\end{aligned}
\end{equation}

The above analysis leads to a simple algorithm. We enumerate $k^*$ from 1 to $K$. For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively. Then we evaluate the objective function $E$ and record the best solution.

% subsection confusion_estimation (end)

% section label_noise_model (end)

\section{Deep Learning From Weak Labels} % (fold)
\label{sec:weak_label_deep_learning}
\begin{figure*}
\begin{center}
\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
\end{center}
\caption{System diagram of our proposed method. Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively. A label noise model layer infers the ground truths according to CNNs' results and the observed weak label. The ground truth is then used to supervise the CNNs. A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
\label{fig:framework}
\end{figure*}

We integrate the proposed label noise model into a deep learning framework. As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs. Moreover, we append a weak-label-loss layer at the end, which takes as input the CNNs' prediction scores and the observed weak label. Stochastic Gradient Descent (SGD) with backpropagation technique is used to approximately optimize the whole network. In each forward pass, the weak-label-loss layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}. While in the backward pass, it computes the weighted sum of gradients with respect to $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$, thus the errors can be further propagated back. The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.

\begin{algorithm}
    \SetKwData{Sum}{sum}
    \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

    \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
    \Input{Object class scores matrix $Y$ of size $N \times L$}
    \Input{Noise type scores matrix $Z$ of size $N \times 3$}
    \Output{Posterior probability matrix $P$ of size $L \times 3$}
    \BlankLine

    $P_y \leftarrow$ \Softmax{$Y$}\;
    $P_z \leftarrow$ \Softmax{$Z$}\;
    \BlankLine

    \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
    \BlankLine

    \For {$i \leftarrow 1$ \KwTo $N$} {
        \Sum $\leftarrow 0$\;
        \For {$j \leftarrow 1$ \KwTo $L$} {
            \For {$k \leftarrow 1$ \KwTo $3$} {
                $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
            }
        }
        $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
    }

    \caption{Forward pass}
    \label{alg:forward}
\end{algorithm}
\begin{algorithm}
    \SetKwData{Sum}{sum}
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

    \Input{Object class scores matrix $Y$ of size $N \times L$}
    \Input{Posterior probability matrix $P$ of size $L \times 3$}
    \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
    \BlankLine

    \For {$i \leftarrow 1$ \KwTo $N$} {
        \For {$j \leftarrow 1$ \KwTo $L$} {
            \Sum $\leftarrow 0$\;
            \For {$k \leftarrow 1$ \KwTo $3$} {
                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
            }
            $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
            $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
        }
    }

    \caption{Backward pass for computing gradient w.r.t. object class scores}
    \label{alg:backward}
\end{algorithm}

Directly training the whole network with random initialization is impractical, because the posterior computation could be totally wrong. Therefore, we need to pretrain each CNN component with strongly supervised data. Gathering ground truth object classes is straight forward, since we can just manually label some images by expert. The resulting strongly labeled dataset $\mathcal{D}_s$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$. On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and weak labels. For each sample, we choose as ground truth the $\vec{z}$ that maximizes the likelihood in Eq~\eqref{eq:likelihood}.

After both the CNN components are properly pretrained, we can start training the whole network with massive weakly labeled data. However, some practical issues need to be further discussed. First, if we merely use weak data, we will lose precious knowledge that we have gained before and the model could be drifted. Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components. Then each CNN receives two kinds of gradients, one is from the strongly supervised data and the other is from the weakly supervised data. We denote them by $\Delta_s$ and $\Delta_w$, respectively. A potential problem is that $|\Delta_s| \ll |\Delta_w|$, because strongly labeled data is much less than the weak data. To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_s$ to half amount of the weak data $\mathcal{D}_w$. This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.

Our proposed model has the ability to figure out the ground truth label given the image and its weak label. From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself. Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model. Meanwhile, we exploit the second kind of information to bridge the semantic gap between the image and its possible noisy labels.
% section weak_label_deep_learning (end)

\section{Experiments} % (fold)
\label{sec:experiments}

\subsection{Dataset} % (fold)
\label{sub:dataset}
We build a large-scale clothes dataset by crawling images and their surrounding text from some online shopping websites. The surrounding text is valuable, because it usually contains several keywords that can be further converted to visual tags. Specific to our task of clothes classification, we define $14$ classes: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Coat, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.

In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_s$), validation and testing sets. Meanwhile remaining data construct the weakly labeled training dataset $\mathcal{D}_w$. Notice that near duplicate images are removed from training datasets $\mathcal{D}_s$ and $\mathcal{D}_w$ to ensure that our testing protocol is reliable. The size of training datasets are $|\mathcal{D}_s| = 47570$ and $|\mathcal{D}_w| = 1.5M$, while for validation and testing set, there are 14,313 and 10,526 images respectively. The confusion matrix between strong and weak labels are presented in Figure~\ref{fig:cm_strong_weak}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=1.0\linewidth]{figure/cm_strong_weak_labels.pdf}
\end{center}
\caption{Confusion matrix between strong and weak labels. Grid numbers represent the percentage of confusion between true labels and weak labels. We ignore the elements whose values are less than $1\%$ for better demonstration. Frequency of each true label is listed at the top of each column.}
\label{fig:cm_strong_weak}
\end{figure}

% subsection dataset (end)

\subsection{Evaluation} % (fold)
\label{sub:evaluation}
The effectiveness of our model is validated based on a series of experiments. We exploit the AlexNet~\cite{krizhevsky2012imagenet} as our baseline model, which consists of five convolutional layers and three fully connected layers. Although recent models may have better learning capability, we choose AlexNet since it is well studied and much easier to be reimplemented (see the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}}).

We also implement the bottom up method introduced in~\cite{sukhbaatar2014learning}. Briefly speaking, they proposed a noise model with the assumption that a weak label is only related to its true label. The relation is modeled by a confusion matrix $Q$ whose true value can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.

We list all the models and training strategies to be compared in Table~\ref{tab:models}.  In general, we set the initial learning rate to be $0.001$ and is multiplied by $0.1$ every $50000$ iterations. For each method, we keep training the model until it converges. Classification accuracies on both the validation and testing set are presented in Table~\ref{tab:accuracy}.

\begin{table}
\begin{center}
\begin{tabular}{c|p{3.5em}|p{8em}|p{6em}}
\hline
\# & Method & Data & Initialization \\
\hline\hline
1 & AlexNet & $\mathcal{D}_1$ & random \\
\hline
2 & AlexNet & $\mathcal{D}_1$ & \texttt{ilsvrc2012} pretrained model \\
\hline
3 & AlexNet & $\mathcal{D}_1 \cup \mathcal{D}_2$ but treat weak labels in $\mathcal{D}_2$ as ground truth & random \\
\hline
4 & AlexNet & $\mathcal{D}_1 \cup \mathcal{D}_2$ but treat weak labels in $\mathcal{D}_2$ as ground truth & \texttt{ilsvrc2012} pretrained model \\
\hline
5 & Bottom Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_1 \cup \mathcal{D}_2$ & model \#2 \\
\hline
6 & Ours & $\mathcal{D}_1 \cup \mathcal{D}_2$ & model \#2 \\
\hline
\end{tabular}
\end{center}
\caption{Models and corresponding training strategies used in our experiments}
\label{tab:models}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
\hline
\# & Validation Accuracy & Testing Accuracy \\
\hline\hline
1 & 64.28\% & 64.54\% \\
\hline
2 & 72.21\% & 72.63\% \\
\hline
3 & 73.76\% & 74.03\% \\
\hline
4 & 75.57\% & 75.30\% \\
\hline
5 & 75.97\% & 76.22\% \\
\hline
6 & 77.65\% & 78.24\% \\
\hline
\end{tabular}
\end{center}
\caption{Classification accuracies on validation and testing set}
\label{tab:accuracy}
\end{table}

From the table we can see that when only a small amount of supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance. To cope with this problem, finetuning from a model pretrained on related but much larger dataset can significantly improve the accuracy, which is illustrated in the result of model \#2. However, this transfer learning scheme may still suffer from suboptimal model parameters if the two tasks are loosely related, just like the clothes vs. general object classification in our case. We see that sufficiently better performance can be achieved if we train the same model with random initialization on the massive weakly labeled data, but treat weak labels just as ground truth.

Among all the methods listed above, our approach leads to the best performance. In order to understand the way our model handles weak labels, we demonstrate several examples in Figure~\ref{fig:model_output}. We can see that given a noisy label, our model could exploit its current knowledge to correct the noise by setting a large weight to the true label and use it as supervision instead of the noisy one. Another interesting observation is that if one of the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ goes wrong, the model can still figure out the correct label.

\begin{figure*}
\begin{center}
\end{center}
\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
\caption{Examples of ground truth labels inferred by our model}
\label{fig:model_output}
\end{figure*}

Next we explain the meaning of $p(\vec{z}|\vec{x})$ by taking a look at our model's prediction on samples drawn from the weak label class ``Windbreaker''. As shown in Figure~\ref{fig:noise_cluster}, images that have high probability of confusing noise often share similar visual patterns. This observation indicates that $p(\vec{z}|\vec{x})$ is a property of an image itself, which represents how the image tends to be confused. Our model is trained to capture these information and exploit them to clarify the noisy labels. Figure~\ref{fig:noise_prediction_rp} further shows the rank-precision curve of our model's noise prediction. We can see that nearly $80\%$ of the top-500 high confident ``confusing'' samples actually suffer from noise, which again verifies our feasibility of our proposed noise model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
\end{center}
\caption{Images tend to suffer from confusing noise usually share similar visual patterns. After training, our model predicts high probability of ``noise free'' for the five images on the top, while predicting high probability of ``confusing noise'' for the bottom five. All the images share same the weak label ``Windbreaker'', but the ground truth of the bottom five images should be ``Jacket''.}
\label{fig:noise_cluster}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.8\linewidth]{figure/noise_prediction_rank_precision.pdf}
\end{center}
\caption{We first sort our model's ``confusing noise'' prediction on the validation set, and then check whether the weak label of the corresponding image mismatch its true label. The rank-precision curve is plotted.}
\label{fig:noise_prediction_rp}
\end{figure}
% subsection evaluation (end)
% section experiments (end)

\section{Conclusion} % (fold)
\label{sec:conclusion}
In this paper, we raised the problem of training a deep neural network with limited strongly labeled data and massive weakly labeled data. By investigating the source of weak labels, a novel probabilistic model is proposed to describe how a noisy label is generated. Two latent variables --- ground truth and noise type -- are introduced to bridge the semantic gap between the observed image and its corresponding weak label. We exploit EM algorithm to learn the parameters and integrate it into a deep learning framework. Experiments on a large-scale clothes dataset show that learning from massive weakly labeled data is significantly better than using merely the limited strongly supervised data. Utilizing our proposed label noise model can further improve the performance.
% section conclusion (end)

{\small
\bibliographystyle{ieee}
\bibliography{references}
}

\end{document}

### 2014-11-14 figure/make_cm.py

@@ -1,0 +1,70 @@
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import cPickle
+from argparse import ArgumentParser
+
+_label_names = [
+    'T-Shirt', 'Shirt', 'Knitwear', 'Chiffon', 'Sweater', 'Coat', 'Windbreaker',
+    'Jacket', 'Down Coat', 'Suit', 'Shawl', 'Dress', 'Vest', 'Underwear']
+
+def _unpickle(file_path):
+    data = None
+    with open(file_path, 'rb') as f:
+        data = cPickle.load(f)
+    return data
+
+def draw_cm(file_path, output=None):
+    cm = _unpickle(file_path)
+    freq = cm.sum(axis=0)
+    freq = freq * 1.0 / freq.sum()
+    cm = cm * 1.0 / cm.sum(axis=0)
+    n = cm.shape[0]
+    acc = sum(np.diag(cm) * freq)
+
+    plt.matshow(cm, cmap=plt.cm.Greys, aspect='auto')
+    axes = plt.gca()
+    for i in xrange(n):
+        for j in xrange(n):
+            v = int(cm[i, j] * 100)
+            if v == 0: continue
+            if v >= 50:
+                axes.text(j, i, '{}'.format(v), fontweight='bold',
+                          va='center', ha='center', color='#ffffff')
+            else:
+                axes.text(j, i, '{}'.format(v),
+                          va='center', ha='center', color='#111111')
+
+    # plt.title('Average Accuracy {:.2%}'.format(acc))
+    plt.xlabel('True Label', fontsize=8)
+    plt.ylabel('Weak Label', fontsize=8)
+    axes.set_xticks([i for i in xrange(n)])
+    axes.set_yticks([i for i in xrange(n)])
+    axes.set_yticklabels(_label_names, fontsize=7)
+
+    x_tl = []
+    for i, (name, freq) in enumerate(zip(_label_names, freq)):
+        if i % 2 == 0:
+            x_tl.append('{}\n\n{:.1%}'.format(name, freq))
+        else:
+            x_tl.append('\n{}\n{:.1%}'.format(name, freq))
+    axes.set_xticklabels(x_tl, fontsize=7)
+
+    if output is not None:
+        plt.savefig(output)
+    else:
+        plt.show()
+
+if __name__ == '__main__':
+    parser = ArgumentParser()
+    parser.add_argument('--cm-file', help="Pickled confusion matrix file")
[…]

### 2014-11-14 figure/make_pgm.py

@@ -1,0 +1,22 @@
+from matplotlib import rc
+rc('font', family='serif', size=12)
+rc('text', usetex=True)
+
+import daft
+
+pgm = daft.PGM([4, 3.25], origin=[-1.75, -1.75])
+pgm.add_node(daft.Node('x', r'$x_n$', 0, 0, observed=True))
+pgm.add_node(daft.Node('y', r'$y_n$', 1, 0))
+pgm.add_node(daft.Node('z', r'$z_n$', 0, -1))
+pgm.add_node(daft.Node('y_tilde', r'$\tilde{y}_n$', 1, -1, observed=True))
+pgm.add_node(daft.Node('theta_1', r'$\theta_1$', 1, 1))
+pgm.add_node(daft.Node('theta_2', r'$\theta_2$', -1, -1))
+pgm.add_plate(daft.Plate([-0.5, -1.5, 2, 2], label=r'$N$', label_offset=[100, 5]))
+pgm.add_edge('x', 'y')
+pgm.add_edge('x', 'z')
+pgm.add_edge('y', 'y_tilde')
+pgm.add_edge('z', 'y_tilde')
+pgm.add_edge('theta_1', 'y')
+pgm.add_edge('theta_2', 'z')
+pgm.render()
+pgm.figure.savefig('pgm.pdf')

### 2014-11-14 figure/make_zstat.py

@@ -1,0 +1,34 @@
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import cPickle
+from argparse import ArgumentParser
+
+def _unpickle(file_path):
+    data = None
+    with open(file_path, 'rb') as f:
+        data = cPickle.load(f)
+    return data
+
+def draw_zstat(file_path, output=None, topk=None):
+    rank_precision = _unpickle(file_path)
+    if topk is not None:
+        rank_precision = rank_precision[0:topk]
+
+    plt.plot(rank_precision, linewidth=2.0, color='#111111')
+    plt.xlabel('Rank', fontsize=12, fontweight='bold')
+    plt.ylabel('Precision', fontsize=12, fontweight='bold')
+    plt.ylim(0.0, 1.0)
+
+    if output is not None:
+        plt.savefig(output)
+    else:
+        plt.show()
+
+if __name__ == '__main__':
+    parser = ArgumentParser()
+    parser.add_argument('--topk', type=int)
+    args = parser.parse_args()
+
+    draw_zstat('../material/noise_prediction_rank_precision.pkl',
+               './noise_prediction_rank_precision.pdf', args.topk)

### 2014-11-14 paper.tex
Modify experiments and figures

@@
 \label{sec:label_noise_model}
-We target on the problem of learning a classifier from a set of weakly labeled image data.
-To be specific, we have a weakly labeled dataset $\mathcal{D}_w=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
-Based on previous analysis of the noise types, we describe how the weak label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
-Despite the observed image $\vec{x}$ and the weak label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively.
+We target on the problem of learning a classifier from a set of images with noisy labels.
+To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
+Based on previous analysis of the noise types, we describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
+Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively.
 Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.
@@
 \begin{enumerate}
-    \item The weak label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
-    \item The weak label suffers from a pointless noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
-    \item The weak label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
+    \item The label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
+    \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
+    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
 \end{enumerate}
 
-Following this assignment rule, we define the conditional probability of the weak label by
+Following this assignment rule, we define the conditional probability of the noisy label by
 \begin{equation} \label{eq:likelihood}
@@
 
-To illustrate the relations between weak label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
+To illustrate the relations between noisy label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
 \begin{equation}
@@
 \begin{multline} \label{eq:posterior}
-    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}} | \vec{y}, \vec{z}, \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
+    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
     = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
@@
 \textbf{M-Step} Since deep neural networks are exploited to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, we perform gradient ascent on $Q$:
-\begin{multline}
+\begin{multline} \label{eq:gradient}
     \frac{\partial Q}{\partial \theta} = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta} \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
-    = \sum_{\vec{y},\vec{z}} w(\vec{y},\vec{z}) \left\{\frac{\partial}{\partial \theta_1}\log p(\vec{y}|\vec{x};\theta_1) + \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2) \right\}
+    = \sum_{\vec{y}} p(\vec{y} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_1} \log p(\vec{y}|\vec{x};\theta_1) + \\
+      \sum_{\vec{z}} p(\vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2)
 \end{multline}
-where $w(\vec{y},\vec{z}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)})$ can be treated as the weights of each pair of latent variables.
 
@@
 
-\subsection{Confusion Estimation} % (fold)
+\subsection{Estimating the Matrix $\mat{C}$} % (fold)
 \label{sub:confusion_estimation}
@@
 
-We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_s = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both strong label and weak label.
+We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy label.
 As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
@@
 
-\section{Deep Learning From Weak Labels} % (fold)
+\section{Deep Learning from Noisy Labels} % (fold)
 \label{sec:weak_label_deep_learning}
@@
 Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively.
-A label noise model layer infers the ground truths according to CNNs' results and the observed weak label.
+A label noise model layer infers the ground truths according to CNNs' results and the observed noisy label.
 The ground truth is then used to supervise the CNNs.
@@
 As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
-Moreover, we append a weak-label-loss layer at the end, which takes as input the CNNs' prediction scores and the observed weak label.
-Stochastic Gradient Descent (SGD) with backpropagation technique is used to approximately optimize the whole network.
-In each forward pass, the weak-label-loss layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
-While in the backward pass, it computes the weighted sum of gradients with respect to $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$, thus the errors can be further propagated back.
-The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.
+Moreover, we append a label-noise-model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
+Stochastic Gradient Ascent (SGA) with backpropagation technique is used to approximately optimize the whole network.
+In each forward pass, the label-noise-model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
+While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.
 
-\begin{algorithm}
-    \SetKwData{Sum}{sum}
-    \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
-    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+% The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.
 
-    \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
-    \Input{Object class scores matrix $Y$ of size $N \times L$}
-    \Input{Noise type scores matrix $Z$ of size $N \times 3$}
-    \Output{Posterior probability matrix $P$ of size $L \times 3$}
-    \BlankLine
+% \begin{algorithm}
+%     \SetKwData{Sum}{sum}
+%     \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
+%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 
-    $P_y \leftarrow$ \Softmax{$Y$}\;
-    $P_z \leftarrow$ \Softmax{$Z$}\;
-    \BlankLine
+%     \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
+%     \Input{Object class scores matrix $Y$ of size $N \times L$}
+%     \Input{Noise type scores matrix $Z$ of size $N \times 3$}
+%     \Output{Posterior probability matrix $P$ of size $L \times 3$}
+%     \BlankLine
 
-    \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
-    \BlankLine
+%     $P_y \leftarrow$ \Softmax{$Y$}\;
+%     $P_z \leftarrow$ \Softmax{$Z$}\;
+%     \BlankLine
 
-    \For {$i \leftarrow 1$ \KwTo $N$} {
-        \Sum $\leftarrow 0$\;
-        \For {$j \leftarrow 1$ \KwTo $L$} {
-            \For {$k \leftarrow 1$ \KwTo $3$} {
-                $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
-                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-            }
-        }
-        $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
-    }
+%     \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
+%     \BlankLine
 
-    \caption{Forward pass}
-    \label{alg:forward}
-\end{algorithm}
-\begin{algorithm}
-    \SetKwData{Sum}{sum}
-    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+%     \For {$i \leftarrow 1$ \KwTo $N$} {
+%         \Sum $\leftarrow 0$\;
+%         \For {$j \leftarrow 1$ \KwTo $L$} {
+%             \For {$k \leftarrow 1$ \KwTo $3$} {
+%                 $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
+%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
+%             }
+%         }
+%         $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
+%     }
 
-    \Input{Object class scores matrix $Y$ of size $N \times L$}
-    \Input{Posterior probability matrix $P$ of size $L \times 3$}
-    \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
-    \BlankLine
+%     \caption{Forward pass}
+%     \label{alg:forward}
+% \end{algorithm}
+% \begin{algorithm}
+%     \SetKwData{Sum}{sum}
+%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 
-    \For {$i \leftarrow 1$ \KwTo $N$} {
-        \For {$j \leftarrow 1$ \KwTo $L$} {
-            \Sum $\leftarrow 0$\;
-            \For {$k \leftarrow 1$ \KwTo $3$} {
-                \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-            }
-            $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
-            $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
-        }
-    }
+%     \Input{Object class scores matrix $Y$ of size $N \times L$}
+%     \Input{Posterior probability matrix $P$ of size $L \times 3$}
+%     \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
+%     \BlankLine
 
-    \caption{Backward pass for computing gradient w.r.t. object class scores}
-    \label{alg:backward}
-\end{algorithm}
+%     \For {$i \leftarrow 1$ \KwTo $N$} {
+%         \For {$j \leftarrow 1$ \KwTo $L$} {
+%             \Sum $\leftarrow 0$\;
+%             \For {$k \leftarrow 1$ \KwTo $3$} {
+%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
+%             }
+%             $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
+%             $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
+%         }
+%     }
+
+%     \caption{Backward pass for computing gradient w.r.t. object class scores}
+%     \label{alg:backward}
+% \end{algorithm}
 
@@
 Gathering ground truth object classes is straight forward, since we can just manually label some images by expert.
-The resulting strongly labeled dataset $\mathcal{D}_s$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$.
-On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and weak labels.
+The resulting strongly labeled dataset $\mathcal{D}_c$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$.
+On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and noisy labels.
 For each sample, we choose as ground truth the $\vec{z}$ that maximizes the likelihood in Eq~\eqref{eq:likelihood}.
 
-After both the CNN components are properly pretrained, we can start training the whole network with massive weakly labeled data.
+After both the CNN components are properly pretrained, we can start training the whole network with massive noisy labeled data.
 However, some practical issues need to be further discussed.
-First, if we merely use weak data, we will lose precious knowledge that we have gained before and the model could be drifted.
+First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
 Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components.
 Then each CNN receives two kinds of gradients, one is from the strongly supervised data and the other is from the weakly supervised data.
-We denote them by $\Delta_s$ and $\Delta_w$, respectively.
-A potential problem is that $|\Delta_s| \ll |\Delta_w|$, because strongly labeled data is much less than the weak data.
-To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_s$ to half amount of the weak data $\mathcal{D}_w$.
+We denote them by $\Delta_c$ and $\Delta_n$, respectively.
+A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than the noisy data.
+To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$.
 This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.
 
-Our proposed model has the ability to figure out the ground truth label given the image and its weak label.
+Our proposed model has the ability to figure out the ground truth label given the image and its noisy label.
 From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself.
@@
 
-In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_s$), validation and testing sets.
-Meanwhile remaining data construct the weakly labeled training dataset $\mathcal{D}_w$.
-Notice that near duplicate images are removed from training datasets $\mathcal{D}_s$ and $\mathcal{D}_w$ to ensure that our testing protocol is reliable.
-The size of training datasets are $|\mathcal{D}_s| = 47570$ and $|\mathcal{D}_w| = 1.5M$, while for validation and testing set, there are 14,313 and 10,526 images respectively.
-The confusion matrix between strong and weak labels are presented in Figure~\ref{fig:cm_strong_weak}.
+In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and testing sets.
+Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$.
+A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our testing protocol.
+The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and testing set consist of 14,313 and 10,526 images respectively.
+The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}.
+We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding text are quite noisy.
 
@@
 \end{center}
-\caption{Confusion matrix between strong and weak labels.
-Grid numbers represent the percentage of confusion between true labels and weak labels.
-We ignore the elements whose values are less than $1\%$ for better demonstration.
-Frequency of each true label is listed at the top of each column.}
+\caption{\textbf{Confusion matrix between clean and noisy labels}.
+We hide extremely small grid numbers for better demonstration.
+Frequency of each true label is listed at the top of each column.
+The overall accuracy is $61.54\%$, which indicates that the noisy labels are not reliable.}
 \label{fig:cm_strong_weak}
@@
 We also implement the bottom up method introduced in~\cite{sukhbaatar2014learning}.
-Briefly speaking, they proposed a noise model with the assumption that a weak label is only related to its true label.
-The relation is modeled by a confusion matrix $Q$ whose true value can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
+Briefly speaking, they proposed a noise model with the assumption that a noisy label is only related to its true label.
+The relation is modeled by a confusion matrix $Q$ whose values can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
 
@@
 \hline\hline
-1 & AlexNet & $\mathcal{D}_1$ & random \\
+1 & AlexNet & $\mathcal{D}_c$ & random \\
 \hline
-2 & AlexNet & $\mathcal{D}_1$ & \texttt{ilsvrc2012} pretrained model \\
+2 & AlexNet & $\mathcal{D}_c$ & \texttt{ilsvrc2012} pretrained model \\
 \hline
-3 & AlexNet & $\mathcal{D}_1 \cup \mathcal{D}_2$ but treat weak labels in $\mathcal{D}_2$ as ground truth & random \\
+3 & AlexNet & $\mathcal{D}_c \cup \mathcal{D}_n$ but treat noisy labels in $\mathcal{D}_n$ as ground truth & random \\
 \hline
-4 & AlexNet & $\mathcal{D}_1 \cup \mathcal{D}_2$ but treat weak labels in $\mathcal{D}_2$ as ground truth & \texttt{ilsvrc2012} pretrained model \\
+4 & AlexNet & $\mathcal{D}_c \cup \mathcal{D}_n$ but treat noisy labels in $\mathcal{D}_n$ as ground truth & \texttt{ilsvrc2012} pretrained model \\
 \hline
-5 & Bottom Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_1 \cup \mathcal{D}_2$ & model \#2 \\
+5 & Bottom Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c \cup \mathcal{D}_n$ & model \#2 \\
 \hline
-6 & Ours & $\mathcal{D}_1 \cup \mathcal{D}_2$ & model \#2 \\
+6 & Ours & $\mathcal{D}_c \cup \mathcal{D}_n$ & model \#2 \\
 \hline
@@
 
-From the table we can see that when only a small amount of supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance.
+From row 1 we can see that when only a small amount of supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance.
 To cope with this problem, finetuning from a model pretrained on related but much larger dataset can significantly improve the accuracy, which is illustrated in the result of model \#2.
-However, this transfer learning scheme may still suffer from suboptimal model parameters if the two tasks are loosely related, just like the clothes vs.
-general object classification in our case.
-We see that sufficiently better performance can be achieved if we train the same model with random initialization on the massive weakly labeled data, but treat weak labels just as ground truth.
+This is a commonly used technique to train a deep model with limited data for specific task.
 
-Among all the methods listed above, our approach leads to the best performance.
-In order to understand the way our model handles weak labels, we demonstrate several examples in Figure~\ref{fig:model_output}.
-We can see that given a noisy label, our model could exploit its current knowledge to correct the noise by setting a large weight to the true label and use it as supervision instead of the noisy one.
-Another interesting observation is that if one of the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ goes wrong, the model can still figure out the correct label.
+However, this transfer learning scheme may still suffer from suboptimal model parameters if the datasets for pretraining and finetuning are loosely related, just like the clothes vs.
+general object in our case.
+We see from row 3 that better performance can be achieved when we train the same model with random initialization on massive data with label noise, but treat noisy labels just as ground truth.
+Model \#4 further improves the accuracy by initializing with ImageNet pretrained model.
+
+Row 5 and 6 show the effect of handling label noise.
+While model \#5 is only $0.4\% \sim 0.9\%$ better than the baseline model \#4, our proposed method gains improvement of $2.1\% \sim 2.9\%$.
+Since model \#5 assumes the noise only relates to true label, which may not be appropriate in our problem.
+On the contrary, our model predicts the noise type from the image itself.
+We will discuss about it in the following section.
+% subsection evaluation (end)
+
+\subsection{Effect of Noise Estimation} % (fold)
+\label{sub:effect_of_noise_estimation}
+In order to understand the way our model handles noisy labels, we demonstrate several examples in Figure~\ref{fig:model_output}.
+We can see that given a noisy label, our model could exploit its current prediction to correct the noise by setting a large weight to the true label, and then use it as supervision instead of the noisy one.
+Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong as shown in the top-right and bottom-left block respectively, the model can still figure out the correct label.
 
@@
 \includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{Examples of ground truth labels inferred by our model}
+\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
 \label{fig:model_output}
@@
 
-Next we explain the meaning of $p(\vec{z}|\vec{x})$ by taking a look at our model's prediction on samples drawn from the weak label class ``Windbreaker''.
-As shown in Figure~\ref{fig:noise_cluster}, images that have high probability of confusing noise often share similar visual patterns.
-This observation indicates that $p(\vec{z}|\vec{x})$ is a property of an image itself, which represents how the image tends to be confused.
+Next we explain the meaning of $p(\vec{z}|\vec{x})$ by taking a look at our model's prediction on samples drawn from the clean label class ``Coat''.
+As shown in Figure~\ref{fig:noise_cluster}, the noisy label is not simply related to the ground truth.
+On the contrary, images that have high probability of confusing noise tend to share similar visual patterns.
+This observation indicates that $p(\vec{z}|\vec{x})$ is a property of an image itself representing how confusing the image is.
 Our model is trained to capture these information and exploit them to clarify the noisy labels.
 Figure~\ref{fig:noise_prediction_rp} further shows the rank-precision curve of our model's noise prediction.
-We can see that nearly $80\%$ of the top-500 high confident ``confusing'' samples actually suffer from noise, which again verifies our feasibility of our proposed noise model.
+We can see that nearly $80\%$ of the top-500 high confident ``confusing'' samples actually suffer from noise, which again verifies the feasibility of our proposed noise model.
 
@@
 \caption{Images tend to suffer from confusing noise usually share similar visual patterns.
-After training, our model predicts high probability of ``noise free'' for the five images on the top, while predicting high probability of ``confusing noise'' for the bottom five.
-All the images share same the weak label ``Windbreaker'', but the ground truth of the bottom five images should be ``Jacket''.}
+Our model predicts high probability of ``noise free'' for the five images on the top, while predicting high probability of ``confusing noise'' for the bottoms.
+While all the images share the same clean label ``Coat'', the first three images at the bottom row have noisy label ``Windbreaker'' and the latter two have noisy label ``Jacket''.}
 \label{fig:noise_cluster}
@@
 \end{center}
-\caption{We first sort our model's ``confusing noise'' prediction on the validation set, and then check whether the weak label of the corresponding image mismatch its true label.
+\caption{We first sort our model's ``confusing noise'' prediction on the validation set, and then check whether the noisy label of the corresponding image mismatch its true label.
 The rank-precision curve is plotted.}
@@
 \end{figure}
-% subsection evaluation (end)
+% subsection effect_of_noise_estimation (end) 
 % section experiments (end)

### 2014-11-14 figure/make_cm.py

@@ -21,6 +21,7 @@ def draw_cm(file_path, output=None):
     cm = cm * 1.0 / cm.sum(axis=0)
     n = cm.shape[0]
     acc = sum(np.diag(cm) * freq)
+    print acc
 
     plt.matshow(cm, cmap=plt.cm.Greys, aspect='auto')
     axes = plt.gca()

### 2014-11-14 figure/make_zstat.py

@@ -16,9 +16,10 @@ def draw_zstat(file_path, output=None, topk=None):
         rank_precision = rank_precision[0:topk]
 
     plt.plot(rank_precision, linewidth=2.0, color='#111111')
-    plt.xlabel('Rank', fontsize=12, fontweight='bold')
-    plt.ylabel('Precision', fontsize=12, fontweight='bold')
+    plt.xlabel('Rank', fontsize=24)
+    plt.ylabel('Precision', fontsize=24)
     plt.ylim(0.0, 1.0)
+    plt.tick_params(labelsize='large')
 
     if output is not None:
         plt.savefig(output)

### 2014-11-14 paper.tex
Add intro

@@
 Large-scale strongly supervised datasets are crucial to train deep neural networks for various computer vision problems.
-Obtaining such well labeled data is usually expensive, but collecting weakly labeled data is much more effortless.
-In this paper we study how to train a deep neural network to classify objects with limited strong supervisions and massive weakly labeled data.
+Obtaining such well labeled data is usually expensive, but collecting web data with noisy labels is much more effortless.
+In this paper we study how to train a deep neural network to classify objects with a small set of clean annotations and massive noisy labeled data.
 A probabilistic model is proposed to describe the relationship between image data, noisy label and ground truth.
 We further integrate the model into a deep learning framework.
-Experiments are conducted on a collected large-scale weakly labeled dataset.
-The results show that weakly labeled data benefit the training of the deep model, and our approach can further improve the performance.
+Experiments are conducted on a collected large-scale web dataset.
+The results show that noisy labeled data benefit the training of deep neural networks, and exploiting our label noise model can further improve the performance.
 \end{abstract}
@@
 \label{sec:introduction}
-Visual classification, which aims at categorizing objects into predefined semantic groups, is a traditional yet fundamental problem in computer vision.
+
+Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, etc.
+While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods requires reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems and making it necessary to develop new efficient labeling and training frameworks for deep learning.
+
+One possible solution is to automatically collect large amount of annotations from the Internet web images (i.e.
+extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
+Unfortunately, these labels are extremely unreliable due to the various types of noise (i.e.
+labeling mistakes from annotators or computing errors from extraction algorithms).
+Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers [3, 13, 15].
+Various noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise.
+Other noise cleaning algorithms are developed [1, 3, ], but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
+
+Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset [5], and then finetuning on the smaller dataset of specific task.
+Such methods may better avoid overfitting and utilize the relationships between two datasets.
+However, we find that training a deep model directly with massive noisy data could achieve better performance than finetuning from a pretrained ImageNet model over a small subset, especially when the relations between the two datasets are weak.
+Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded [6].
+These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.9\linewidth]{figure/overview.pdf}
+\end{center}
+\caption{Overview of our method.
+Labels of web images often suffer from different types of noise.
+Our deep model infers true labels based on observed images and noisy labels.
+These true labels are then used to supervise the training of CNNs.}
+\label{fig:overview}
+\end{figure}
+
+Our goal here is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive amount of noisy labels more effectively.
+Figure~\ref{fig:overview} shows the general framework of our system.
+The major challenge of using noisy labeled data is to identify bad samples and keep them from drifting the model training.
+Intuitively, we have two types of evidence to help make decisions.
+One comes from the ground truth labels of other similar images, and the other comes from how confusing the input image itself.
+In this paper, we model these two types of information as latent variables and use them to bridge the semantic gap between our observed image and weak label.
+Additionally, we introduce two types of label noises explicitly, pure random noise and confusion noise to model the noise more directly.
+
+\begin{itemize}
+   \item \textbf{Pure random noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}.
+This kind of noise is often caused by either the mismatch between web image and surrounding texts, or false conversion from text to label.
+The noisy label in this case is not acceptable.
+   \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one.
+This kind of noise happens regularly in some sort of images.
+For example, the knitwear in the lower orange box of Figure~\ref{fig:overview} can be often misclassified as a sweater.
+However, in real applications, confusion among several related labels is generally acceptable to users.
+\end{itemize}
+
+We propose a novel probabilistic model to capture the relations among all these factors.
+We solve the problem by Expectation-Maximization (EM) algorithm and integrate it into a deep learning framework.
+To validate our approach, we collect a clothing classification dataset consisting of around $72,000$ clean labeled and one million noisy labeled data.
+Experiments on this dataset demonstrate that massive weakly labeled data can benefit the training of deep neural networks even further.
+
+Our work is inspired by [7], which also modifies the deep neural networks to train effectively with noisy labeled data.
+However, their modification is simply implemented by adding a linear layer on top of the softmax layer, which builds on the assumption that label noise is independent of input images.
+We generalize [7] to a new deep learning framework by allowing the noise is related with input images.
+We find that by modeling the noise more appropriately, the deep models can benefit even more from noisy labels.
+
+Our main contribution in this paper is a novel end-to-end deep learning framework that models the noisy web data generation on the Internet.
+The deep learning system is designed to learn to predict noise types, ground truth labels as well as noisy labels.
+The system is able to learn from a small set of clean annotations with a massive amount of noisy labels and find the best trade-off between using all the data.
+
+Our contribution comes from three aspects.
+First, we model label noise generation with a graphical model and further integrate it into the deep learning framework.
+Second, we study different noise types and model their relations with the images by a deep neural network.
+Finally, we collect a large scale clothing classification dataset with both noisy labels and clean labels.
+
+% Visual classification, which aims at categorizing objects into predefined semantic groups, is a traditional yet fundamental problem in computer vision.
 Starting from the pioneering work in~\cite{krizhevsky2012imagenet}, researchers have developed various deep learning approaches to solve object classification problem.
@@
 
-Without losing generality, we focus on the task of clothes recognition, \ie, determining whether an image is about a T-shirt, a sweater, or a dress, \etc.
+% Without losing generality, we focus on the task of clothes recognition, \ie, determining whether an image is about a T-shirt, a sweater, or a dress, \etc.
 This specific object classification problem draws much attention to many e-commerce companies, since it is a basic building block of products retrieval and recommendation systems.
@@
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.9\linewidth]{figure/overview.pdf}
-\end{center}
-\caption{Overview of our method.
-Weak labels often suffer from pointless (red) or confusing noise (orange).
-Our model infers true label (green) based on observed image and weak label, as well as CNN predictions about object class and noise type.}
-\label{fig:overview}
-\end{figure}
-
-To conquer this problem, we first study why a weak label goes wrong and conclude two types of label noise:
-\begin{itemize}
-   \item \textbf{Pointless noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}.
+% To conquer this problem, we first study why a weak label goes wrong and conclude two types of label noise:
+% \begin{itemize}
+%    \item \textbf{Pointless noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}.
 This kind of noise is often caused by either the mismatch between web image and surrounding text, or false conversion from text to label.
 The noisy label in this case is not acceptable.
-   \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one.
+%    \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one.
 This kind of noise happens regularly in some sort of images.
@@
 However, in real applications, confusion among several related labels is generally acceptable to users.
-\end{itemize}
+% \end{itemize}
 
-Our goal is to identify the ground truth label given an image as well as its weak label, and then use the ground truth label as supervision instead of the weak one.
+% Our goal is to identify the ground truth label given an image as well as its weak label, and then use the ground truth label as supervision instead of the weak one.
 Intuitively, we have two kinds of evidence to help us make decision.
@@
 
-Our contribution comes from two aspects.
+% Our contribution comes from two aspects.
 First, we investigate the cause of weak label in real-world data, and formulate the label noise in a probabilistic model.
@@
 \label{sec:related_work}
-Various methods have been proposed to handle label noise in different problem settings.
+
+\noindent
+\textbf{Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
+Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well labeled data to classify unlabeled samples.
+However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets.
+Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
+But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
+
+\noindent
+\textbf{Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
+However, the model parameters cannot be properly learned when training data is not enough.
+Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task~\cite{krizhevsky2012imagenet,oquab2013learning,azizpour2014generic}.
+Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
+In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.
+
+\noindent
+\textbf{Noise Modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning,sukhbaatar2014learning,vahdat2013handling}.
+~\cite{mnih2012learning} builds a simple noisy model for aerial images but only consider binary classification.
+[9] assumes label noise is independent from the true class label which is a simple and a specific case.
+[7] generalizes from [9 11] by considering multi-class classification and modeling class dependent noise, but they assume the noise is independent from source images, ignoring the hardness of labeling different images.
+
+% Various methods have been proposed to handle label noise in different problem settings.
 Our work is inspired by~\cite{sukhbaatar2014learning}, where they linearly map the probability distribution of the true label to that of the noisy label.
@@
 
-Other methods model noisy labels in different context, \eg, visual attributes annotation~\cite{vahdat2013handling}, or roads recognition in aerial images~\cite{mnih2012learning}.
+% Other methods model noisy labels in different context, \eg, visual attributes annotation~\cite{vahdat2013handling}, or roads recognition in aerial images~\cite{mnih2012learning}.
 It is non-trivial to generalize their approaches to solver our problem, \ie, multi-class object classification.
 
-Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
+% Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
 Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
@@
 
-The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
+% The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
 However, the model parameters cannot be properly learned when training data is not enough.
@@
 Based on previous analysis of the noise types, we describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
-Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively.
-Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.6\linewidth]{figure/pgm.pdf}
+\includegraphics[width=0.5\linewidth]{figure/pgm.pdf}
 \end{center}
@@
 \end{figure}
+
+Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively.
+Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.
 
@@
 \begin{equation}
-    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
+    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
 \end{equation}
@@
 \max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
-\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } K\times K \\
+\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L \\
                     & \vec{t} \in \{0,1\}^{N'}
@@
 
-Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+K^2)$ time complexity.
+Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+L^2)$ time complexity.
 Before we introduce the algorithm itself, some theorems need to be proved.
@@
 \begin{lemma}
-$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,K\}$
+$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,L\}$
 \end{lemma}
@@
 Theorem 1 further shows that samples with same pair of $(\tilde{\vec{y}},\vec{y})$ share a same noise type.
-Then what really matters is the frequency of each of the $K\times K$ pairs $(\tilde{\vec{y}},\vec{y})$.
+Then what really matters is the frequency of each of the $L\times L$ pairs $(\tilde{\vec{y}},\vec{y})$.
 Considering a particular column $\vec{c}$, suppose there are $M$ samples affecting this column.
-We can count the frequency of noisy label class 1 to $K$ as $m_1,\dots,m_K$ and might as well set $m_1\geq m_2\geq \cdots \geq m_K$.
+We can count the frequency of noisy label class 1 to $L$ as $m_1,\dots,m_L$ and might as well set $m_1\geq m_2\geq \cdots \geq m_L$.
 The problem is then converted to
@@
 \begin{aligned}
-\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{K} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right)\\
-\text{subject to} \quad & \vec{c} \in [0,1]^K, \sum_{k=1}^{K} \vec{c}_k = 1 \\
-                    & \vec{t} \in \{0,1\}^{K}
+\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{L} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right)\\
+\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{L} \vec{c}_k = 1 \\
+                    & \vec{t} \in \{0,1\}^{L}
 \end{aligned}
@@
 
-Due to the rearrangement inequality, we can prove that in the optimal solution,
-\begin{equation}
-    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_K)
-\end{equation}
-Then by using Theorem 2, there must exist a $k^* \in \{1,\dots,K\}$ such that
-\begin{equation} \label{eq:opt_t}
-\begin{aligned}
-    &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
-    &\vec{t}^*_i = 1, i = k^*+1,\dots,K
-\end{aligned}
-\end{equation}
-This also implies that only the first $k^*$ elements of $\vec{c}^*$ have nonzero values (greater than $\alpha$ actually).
-Furthermore, if $k^*$ is known, finding the optimal $\vec{c}^*$ is to solve the following problem:
-\begin{equation}
-\begin{aligned}
-\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k\\
-\text{subject to} \quad & \vec{c} \in [0,1]^K, \sum_{k=1}^{k^*} \vec{c}_k = 1
-\end{aligned}
-\end{equation}
-whose solution is
-\begin{equation} \label{eq:opt_c}
-\begin{aligned}
-    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^* \\
-    &\vec{c}^*_i = 0, i = k^*+1,\dots,K
-\end{aligned}
-\end{equation}
-
-The above analysis leads to a simple algorithm.
-We enumerate $k^*$ from 1 to $K$.
-For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively.
-Then we evaluate the objective function $E$ and record the best solution.
-
-% subsection confusion_estimation (end)
-
-% section label_noise_model (end)
-
-\section{Deep Learning from Noisy Labels} % (fold)
-\label{sec:weak_label_deep_learning}
 \begin{figure*}
@@
 \end{figure*}
+
+Due to the rearrangement inequality, we can prove that in the optimal solution,
+\begin{equation}
+    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_L)
+\end{equation}
+Then by using Theorem 2, there must exist a $k^* \in \{1,\dots,L\}$ such that
+\begin{equation} \label{eq:opt_t}
+\begin{aligned}
+    &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
+    &\vec{t}^*_i = 1, i = k^*+1,\dots,L
+\end{aligned}
+\end{equation}
+This also implies that only the first $k^*$ elements of $\vec{c}^*$ have nonzero values (greater than $\alpha$ actually).
+Furthermore, if $k^*$ is known, finding the optimal $\vec{c}^*$ is to solve the following problem:
+\begin{equation}
+\begin{aligned}
+\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k\\
+\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{k^*} \vec{c}_k = 1
+\end{aligned}
+\end{equation}
+whose solution is
+\begin{equation} \label{eq:opt_c}
+\begin{aligned}
+    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^* \\
+    &\vec{c}^*_i = 0, i = k^*+1,\dots,L
+\end{aligned}
+\end{equation}
+
+The above analysis leads to a simple algorithm.
+We enumerate $k^*$ from 1 to $L$.
+For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively.
+Then we evaluate the objective function $E$ and record the best solution.
+
+% subsection confusion_estimation (end)
+
+% section label_noise_model (end)
+
+\section{Deep Learning from Noisy Labels} % (fold)
+\label{sec:weak_label_deep_learning}
 
@@
 Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components.
-Then each CNN receives two kinds of gradients, one is from the strongly supervised data and the other is from the weakly supervised data.
+Then each CNN receives two kinds of gradients, one is from the clean labeled data and the other is from the noisy labeled data.
 We denote them by $\Delta_c$ and $\Delta_n$, respectively.
 A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than the noisy data.
-To deal with this problem, we bootstrap the strongly labeled data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$.
+To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$.
 This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.
 
-Our proposed model has the ability to figure out the ground truth label given the image and its noisy label.
+Our proposed method has the ability to figure out the ground truth label given the image and its noisy label.
 From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself.
@@
 \label{sub:dataset}
-We build a large-scale clothes dataset by crawling images and their surrounding text from some online shopping websites.
-The surrounding text is valuable, because it usually contains several keywords that can be further converted to visual tags.
+We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites.
+These surrounding texts are valuable, because they usually contain several keywords that can be further converted to visual tags.
 Specific to our task of clothes classification, we define $14$ classes: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Coat, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.
 
-In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and testing sets.
+In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets.
 Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$.
-A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our testing protocol.
-The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and testing set consist of 14,313 and 10,526 images respectively.
+A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our test protocol.
+The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and test set consist of 14,313 and 10,526 images respectively.
 The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}.
-We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding text are quite noisy.
+We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding texts are quite noisy.
 
@@
 Briefly speaking, they proposed a noise model with the assumption that a noisy label is only related to its true label.
-The relation is modeled by a confusion matrix $Q$ whose values can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
+The relation is built by a confusion matrix $Q$ whose values can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
 
@@
 For each method, we keep training the model until it converges.
-Classification accuracies on both the validation and testing set are presented in Table~\ref{tab:accuracy}.
+Classification accuracies on both the validation and test set are presented in Table~\ref{tab:accuracy}.
 
@@
 
+\begin{figure*}
+\begin{center}
+\end{center}
+\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
+\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
+\label{fig:model_output}
+\end{figure*}
+
+From row 1 we can see that when only a small amount of strongly supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance.
+To cope with this problem, finetuning from a model pretrained on related but much larger dataset can significantly improve the accuracy, which is illustrated in the result of model \#2.
+This is a commonly used technique to train a deep model with limited data for specific task.
+
+However, this transfer learning scheme may still suffer from suboptimal model parameters if the datasets for pretraining and finetuning are loosely related, just like the clothes vs.
+general objects in our case.
+We see from row 3 that better performance can be achieved when we train the same model with random initialization on massive data with label noise, but treat noisy labels just as ground truth.
+Model \#4 further improves the accuracy by initializing with ImageNet pretrained model.
+
 \begin{table}
@@
 \hline
-\# & Validation Accuracy & Testing Accuracy \\
+\# & Validation Accuracy & Test Accuracy \\
 \hline\hline
@@
 \end{center}
-\caption{Classification accuracies on validation and testing set}
+\caption{Classification accuracies on validation and test set}
 \label{tab:accuracy}
@@
 
-From row 1 we can see that when only a small amount of supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance.
-To cope with this problem, finetuning from a model pretrained on related but much larger dataset can significantly improve the accuracy, which is illustrated in the result of model \#2.
-This is a commonly used technique to train a deep model with limited data for specific task.
-
-However, this transfer learning scheme may still suffer from suboptimal model parameters if the datasets for pretraining and finetuning are loosely related, just like the clothes vs.
-general object in our case.
-We see from row 3 that better performance can be achieved when we train the same model with random initialization on massive data with label noise, but treat noisy labels just as ground truth.
-Model \#4 further improves the accuracy by initializing with ImageNet pretrained model.
-
 Row 5 and 6 show the effect of handling label noise.
 While model \#5 is only $0.4\% \sim 0.9\%$ better than the baseline model \#4, our proposed method gains improvement of $2.1\% \sim 2.9\%$.
-Since model \#5 assumes the noise only relates to true label, which may not be appropriate in our problem.
+Since model \#5 assumes that the noisy label only relates to the ground truth, which may not be appropriate in our problem.
 On the contrary, our model predicts the noise type from the image itself.
@@
 We can see that given a noisy label, our model could exploit its current prediction to correct the noise by setting a large weight to the true label, and then use it as supervision instead of the noisy one.
-Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong as shown in the top-right and bottom-left block respectively, the model can still figure out the correct label.
-
-\begin{figure*}
-\begin{center}
-\end{center}
-\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
-\label{fig:model_output}
-\end{figure*}
+Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong as shown in the top-right and bottom-left block respectively, our model can still figure out the correct label.
 
@@
 \label{sec:conclusion}
-In this paper, we raised the problem of training a deep neural network with limited strongly labeled data and massive weakly labeled data.
-By investigating the source of weak labels, a novel probabilistic model is proposed to describe how a noisy label is generated.
-Two latent variables --- ground truth and noise type -- are introduced to bridge the semantic gap between the observed image and its corresponding weak label.
-We exploit EM algorithm to learn the parameters and integrate it into a deep learning framework.
-Experiments on a large-scale clothes dataset show that learning from massive weakly labeled data is significantly better than using merely the limited strongly supervised data.
-Utilizing our proposed label noise model can further improve the performance.
+In this paper, we raised the problem of training a deep neural network with limited clean annotations and massive noisy labeled data.
+A novel end-to-end deep learning framework is proposed to handle label noise in training data.
+We exploit a novel probabilistic model to describe how a noisy label is generated.
+Two latent variables --- ground truth and noise type -- are introduced to bridge the semantic gap between the observed image and its corresponding noisy label.
+We solve the problem by EM algorithm and integrate it into the deep learning framework.
+Experiments on a large-scale clothes dataset show that massive noisy label data could benefit the training of deep models, and utilizing our noise handling method can further improve the performance.
 % section conclusion (end)

### 2014-11-14 paper.tex
Nearly final

@@
 %%%%%%%%% TITLE
-\title{Learning From Massive Weakly Labeled Data for Visual Classification}
+\title{Learning From Massive Noisy Labeled Data for Visual Classification}
 
@@
 Obtaining such well labeled data is usually expensive, but collecting web data with noisy labels is much more effortless.
-In this paper we study how to train a deep neural network to classify objects with a small set of clean annotations and massive noisy labeled data.
-A probabilistic model is proposed to describe the relationship between image data, noisy label and ground truth.
-We further integrate the model into a deep learning framework.
+In this paper we model label noise with a graphical model and further integrate it into a deep learning framework.
 Experiments are conducted on a collected large-scale web dataset.
@@
 Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, etc.
-While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods requires reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems and making it necessary to develop new efficient labeling and training frameworks for deep learning.
+While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
+Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.
 
-One possible solution is to automatically collect large amount of annotations from the Internet web images (i.e.
+One possible solution is to automatically collect large amount of annotations from the Internet web images~\cite{gong2014multiview} (i.e.
 extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
@@
 labeling mistakes from annotators or computing errors from extraction algorithms).
-Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers [3, 13, 15].
+Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
 Various noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise.
-Other noise cleaning algorithms are developed [1, 3, ], but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
+Other noise cleaning algorithms are developed~\cite{barandela2000decontamination,brodley2011identifying}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
 
 Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset [5], and then finetuning on the smaller dataset of specific task.
-Such methods may better avoid overfitting and utilize the relationships between two datasets.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetuning on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
+Such methods may better avoid overfitting and utilize the relationships between the two datasets.
 However, we find that training a deep model directly with massive noisy data could achieve better performance than finetuning from a pretrained ImageNet model over a small subset, especially when the relations between the two datasets are weak.
-Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded [6].
+Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
 These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
@@
 In this paper, we model these two types of information as latent variables and use them to bridge the semantic gap between our observed image and weak label.
-Additionally, we introduce two types of label noises explicitly, pure random noise and confusion noise to model the noise more directly.
-
+Additionally, we introduce two types of label noise:
 \begin{itemize}
-   \item \textbf{Pure random noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}.
+   \item \textbf{Pure random noise} occurs when a noisy label has no semantic relationship with its image, for example, the samples with ``$\times$'' in Figure~\ref{fig:overview}.
 This kind of noise is often caused by either the mismatch between web image and surrounding texts, or false conversion from text to label.
 The noisy label in this case is not acceptable.
-   \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one.
+   \item \textbf{Confusing noise} occurs when a noisy label is a reasonable object class for its image other than the ground truth one.
 This kind of noise happens regularly in some sort of images.
-For example, the knitwear in the lower orange box of Figure~\ref{fig:overview} can be often misclassified as a sweater.
+For example, the samples with ``?'' in Figure~\ref{fig:overview}.
 However, in real applications, confusion among several related labels is generally acceptable to users.
@@
 To validate our approach, we collect a clothing classification dataset consisting of around $72,000$ clean labeled and one million noisy labeled data.
-Experiments on this dataset demonstrate that massive weakly labeled data can benefit the training of deep neural networks even further.
+Experiments on this dataset demonstrate that massive noisy labeled data could benefit the training of deep neural networks.
 
-Our work is inspired by [7], which also modifies the deep neural networks to train effectively with noisy labeled data.
-However, their modification is simply implemented by adding a linear layer on top of the softmax layer, which builds on the assumption that label noise is independent of input images.
-We generalize [7] to a new deep learning framework by allowing the noise is related with input images.
+Our work is inspired by~\cite{sukhbaatar2014learning}, which also modifies the deep neural networks to train effectively with noisy labeled data.
+However, their modification is simply implemented by adding a linear layer on top of the softmax layer, which builds on the assumption that label noise is independent with input images.
+We generalize~\cite{sukhbaatar2014learning} to a new deep learning framework by relating the noise to the input image.
 We find that by modeling the noise more appropriately, the deep models can benefit even more from noisy labels.
-
-Our main contribution in this paper is a novel end-to-end deep learning framework that models the noisy web data generation on the Internet.
-The deep learning system is designed to learn to predict noise types, ground truth labels as well as noisy labels.
-The system is able to learn from a small set of clean annotations with a massive amount of noisy labels and find the best trade-off between using all the data.
 
@@
 
-% Visual classification, which aims at categorizing objects into predefined semantic groups, is a traditional yet fundamental problem in computer vision.
-Starting from the pioneering work in~\cite{krizhevsky2012imagenet}, researchers have developed various deep learning approaches to solve object classification problem.
-While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all the methods rely on large-scale strongly supervised training dataset~\cite{deng2009imagenet}, which consumes a lot of manpower to label millions of images.
-In many real-world applications, we can only get limited well labeled data.
-Training a deep neural network is thus difficult even if we finetune it from a pretrained ImageNet model.
-However, we can easily get substantial weakly supervised data by crawling images from the Internet and extracting keywords from their surrounding text.
-For example, product photos on \emph{Amazon} and \emph{Taobao} usually have relatively reasonable title and tags, which can be converted to weak object class and attributes.
-Thus it drives us to find some effective ways to do visual recognition by utilizing these massive information.
-
-% Without losing generality, we focus on the task of clothes recognition, \ie, determining whether an image is about a T-shirt, a sweater, or a dress, \etc.
-This specific object classification problem draws much attention to many e-commerce companies, since it is a basic building block of products retrieval and recommendation systems.
-The major challenge of using weakly labeled data in training classifier is to identify bad samples and keep them from drifting the model.
-Figure~\ref{fig:overview} shows some examples of label noise.
-Existing methods try to solve this problem from two aspects.
-One way is to model the relationship between true label and noisy label, but the model is too simple to fit in real-world applications.
-The other one exploits semi-supervised learning algorithms (such as label propagation), but their complexities are usually quadratic with the number of samples, thus cannot be applied on large-scale datasets.
-
-% To conquer this problem, we first study why a weak label goes wrong and conclude two types of label noise:
-% \begin{itemize}
-%    \item \textbf{Pointless noise} occurs when a weak label has no semantic relationship with its image, for example, the samples in the upper red box of Figure~\ref{fig:overview}.
-This kind of noise is often caused by either the mismatch between web image and surrounding text, or false conversion from text to label.
-The noisy label in this case is not acceptable.
-%    \item \textbf{Confusing noise} occurs when a weak label is a reasonable object class for its image other than the ground truth one.
-This kind of noise happens regularly in some sort of images.
-For example, the knitwear in the lower orange box of Figure~\ref{fig:overview} can be often misclassified as a sweater.
-However, in real applications, confusion among several related labels is generally acceptable to users.
-% \end{itemize}
-
-% Our goal is to identify the ground truth label given an image as well as its weak label, and then use the ground truth label as supervision instead of the weak one.
-Intuitively, we have two kinds of evidence to help us make decision.
-One comes from the ground truth labels of other similar images, and the other one comes from how confusing is the input image itself.
-In this paper, we model these two kinds of information as latent variables and use them to bridge the semantic gap between our observed image and weak label.
-A novel probabilistic model is proposed to build relations among all these factors.
-We solve the problem by Expectation-Maximization (EM) algorithm and integrate it into a deep learning framework.
-To validate our approach, we collected a clothes image dataset consisting of about $72,000$ strongly labeled and one million weakly labeled data.
-Experiments on this dataset show that massive weakly labeled data benefit the training of deep neural networks, and our approach can further improve the performance.
-
-% Our contribution comes from two aspects.
-First, we investigate the cause of weak label in real-world data, and formulate the label noise in a probabilistic model.
-Second, we integrate the proposed model into a deep learning framework to help it resist bad supervision in training with weakly labeled data.
-
 % section related_work (end)
@@
 \label{sec:related_work}
+For most of the related works including effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to \cite{frenay2013classification} for a comprehensive review.
 
-\noindent
-\textbf{Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
-Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets.
-Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
+{\bf Direct learning with noisy labels:} Among other consequences, many works have shown that noise can adversely impact the classification performances of induced classifiers \cite{zhu2004class}. 
+Experiments in the literature show that the performances of classifiers inferred by label noise-robust algo- rithms are still affected by label noise.
+Label noise-robust methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.
+
+{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
+Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
+However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on largescale datasets.
+Weston et al.
+\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural net- work, which benefits the learning of discriminative features.
 But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
 
-\noindent
-\textbf{Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
+{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task~\cite{krizhevsky2012imagenet,oquab2013learning,azizpour2014generic}.
+Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic}.
 Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.
+In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves bette performance compared with finetuning from a ImageNet pretrained model.
 
-\noindent
-\textbf{Noise Modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning,sukhbaatar2014learning,vahdat2013handling}.
-~\cite{mnih2012learning} builds a simple noisy model for aerial images but only consider binary classification.
-[9] assumes label noise is independent from the true class label which is a simple and a specific case.
-[7] generalizes from [9 11] by considering multi-class classification and modeling class dependent noise, but they assume the noise is independent from source images, ignoring the hardness of labeling different images.
-
-% Various methods have been proposed to handle label noise in different problem settings.
-Our work is inspired by~\cite{sukhbaatar2014learning}, where they linearly map the probability distribution of the true label to that of the noisy label.
-But their assumption --- noisy label and input image are conditionally independent given the true label --- is too strong.
-It cannot figure out whether an observed label is correct or not.
-Our proposed method overcomes this problem by first estimating how likely an image suffers from pointless or confusing noise.
-And then predicting the true label based on this information and our observed noisy label.
-
-% Other methods model noisy labels in different context, \eg, visual attributes annotation~\cite{vahdat2013handling}, or roads recognition in aerial images~\cite{mnih2012learning}.
-It is non-trivial to generalize their approaches to solver our problem, \ie, multi-class object classification.
-
-% Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
-Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets.
-Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
-But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
-
-% The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
-However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task~\cite{krizhevsky2012imagenet,oquab2013learning,azizpour2014generic}.
-Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.
-
+{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels \cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.
+\cite{mnih2012learning} builds a simple noisy model for aerial images but only consider binary classification.
+\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and a specific case.
+\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is independent from source images, ignoring the hardness of labeling different images.
 % section related_work (end)

### 2014-11-14 paper.tex
Final

@@
 \begin{abstract}
-Large-scale strongly supervised datasets are crucial to train deep neural networks for various computer vision problems.
-Obtaining such well labeled data is usually expensive, but collecting web data with noisy labels is much more effortless.
-In this paper we model label noise with a graphical model and further integrate it into a deep learning framework.
-Experiments are conducted on a collected large-scale web dataset.
-The results show that noisy labeled data benefit the training of deep neural networks, and exploiting our label noise model can further improve the performance.
+Large-scale supervised datasets are crucial to train deep neural networks for various computer vision problems.
+However, obtaining a massive amount of well labeled data is usually very expensive and time consuming.
+In this paper, we introduce a general framework to train deep nets with only limited number of clean labels and millions of easily obtained noisy labels.
+We model label noises with a graphical probabilistic framework and further integrate it into the deep learning system.
+To demonstrate the performance of our approach, we collect a large scale clothing classification dataset with both noisy and clean labels.
+We demonstrate the effectiveness of our approach on this dataset, showing the possibility of learning a strong deep model with only a small amount of clean labels.
 \end{abstract}
@@
 
-Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetuning on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
-Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a deep model directly with massive noisy data could achieve better performance than finetuning from a pretrained ImageNet model over a small subset, especially when the relations between the two datasets are weak.
-Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
-These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
-
 \begin{figure}[t]
@@
 \end{figure}
+
+Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetuning on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
+Such methods may better avoid overfitting and utilize the relationships between the two datasets.
+However, we find that training a deep model directly with massive noisy data could achieve better performance than finetuning from a pretrained ImageNet model over a small subset, especially when the relations between the two datasets are weak.
+Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
+These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
 
@@
 {\bf Direct learning with noisy labels:} Among other consequences, many works have shown that noise can adversely impact the classification performances of induced classifiers \cite{zhu2004class}. 
-Experiments in the literature show that the performances of classifiers inferred by label noise-robust algo- rithms are still affected by label noise.
+Experiments in the literature show that the performances of classifiers inferred by label noise-robust algorithms are still affected by label noise.
 Label noise-robust methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.
@@
 Weston et al.
-\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural net- work, which benefits the learning of discriminative features.
+\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
 But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
@@
 Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves bette performance compared with finetuning from a ImageNet pretrained model.
+In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.
 
@@
 \begin{equation}
-    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
+    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)})
 \end{equation}
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
-\end{center}
-\caption{System diagram of our proposed method.
-Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively.
-A label noise model layer infers the ground truths according to CNNs' results and the observed noisy label.
-The ground truth is then used to supervise the CNNs.
-A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
-\label{fig:framework}
-\end{figure*}
-
 Due to the rearrangement inequality, we can prove that in the optimal solution,
@@
 \label{sec:weak_label_deep_learning}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
+\end{center}
+\caption{System diagram of our proposed method.
+Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively.
+A label noise model layer infers the ground truths according to CNNs' results and the observed noisy label.
+The ground truth is then used to supervise the CNNs.
+A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
+\label{fig:framework}
+\end{figure*}
 

### 2015-03-25 paper.tex
Add authors and describe the effect of M-Step in another way

@@
 \usepackage{algorithm2e}
+\usepackage{authblk}
 
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 %%%%%%%%% TITLE
-\title{Learning From Massive Noisy Labeled Data for Visual Classification}
+\title{Learning From Massive Noisy Labeled Data for Image Classification}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author[1]{Tong Xiao}
+\author[2]{Tian Xia}
+\author[2]{Yi Yang}
+\author[2]{Chang Huang}
+\author[1]{Xiaogang Wang}
+
+\affil[1]{The Chinese University of Hong Kong}
+\affil[2]{Baidu Research}
+
+\renewcommand\Authands{ and }
+
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
 
@@
 
-The semantic meaning of this optimization process is straight forward.
-We enumerate all the possible true labels, and weight each of them by their posterior probability based on our observation of the image and corresponding noisy label.
-Then we use these weighted labels to supervise the training of our deep neural networks.
+The M-Step above is equivalent to minimize the cross entropy between the estimated ground truth distribution and the prediction of the classifier.
 % subsection learning_the_parameters (end)
@@
 
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+This work is supported by the National Basic Research Program of China (973 program No. 2014CB340505).
+
 {\small

### 2015-03-31 paper.tex
Rewrite the unclear content in the introduction

@@
 \end{center}
-\caption{Overview of our method.
+\caption{Overview of our approach.
 Labels of web images often suffer from different types of noise.
-Our deep model infers true labels based on observed images and noisy labels.
-These true labels are then used to supervise the training of CNNs.}
+A probabilistic model is proposed to detect and correct the wrong labels.
+The corrected labels are used to train underlying CNNs.}
 \label{fig:overview}
@@
 Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetuning on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a deep model directly with massive noisy data could achieve better performance than finetuning from a pretrained ImageNet model over a small subset, especially when the relations between the two datasets are weak.
-Other approaches address the classification problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
+However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning only on the clean labels.
+Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
 These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
+Therefore, it is inevitable to develop a better way of using huge amount of noisy labeled data.
 
-Our goal here is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive amount of noisy labels more effectively.
-Figure~\ref{fig:overview} shows the general framework of our system.
-The major challenge of using noisy labeled data is to identify bad samples and keep them from drifting the model training.
-Intuitively, we have two types of evidence to help make decisions.
-One comes from the ground truth labels of other similar images, and the other comes from how confusing the input image itself.
-In this paper, we model these two types of information as latent variables and use them to bridge the semantic gap between our observed image and weak label.
-Additionally, we introduce two types of label noise:
+Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively.
+Figure~\ref{fig:overview} shows the framework of our approach.
+We collect a million clothes images from E-commerce websites.
+Each image is automatically assigned a noisy label according to the keywords in its surrounding text.
+After that, we manually refine 72,000 image labels, which constitute a clean sub-dataset.
+All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.
+
+To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the ground truths and uses them to supervise the training of the network.
+Our work is inspired by~\cite{sukhbaatar2014learning}, which modifies a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
+However, they assume noisy labels are conditionally independent with input images given clean labels.
+By examining our collected dataset, we find that this assumption is too strong to fit the real-world data well.
+For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
+The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
+It shows that images tend to be mislabeled may share similar visual patterns.
+This is because different sellers have their own bias on different categories, thus they may provide wrong keywords for many similar clothes.
+Based on these observations, we introduce two types of label noise:
 \begin{itemize}
-   \item \textbf{Pure random noise} occurs when a noisy label has no semantic relationship with its image, for example, the samples with ``$\times$'' in Figure~\ref{fig:overview}.
-This kind of noise is often caused by either the mismatch between web image and surrounding texts, or false conversion from text to label.
-The noisy label in this case is not acceptable.
-   \item \textbf{Confusing noise} occurs when a noisy label is a reasonable object class for its image other than the ground truth one.
-This kind of noise happens regularly in some sort of images.
-For example, the samples with ``?'' in Figure~\ref{fig:overview}.
-However, in real applications, confusion among several related labels is generally acceptable to users.
+\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Figure~\ref{fig:overview}).
+\item \textbf{Pure random noise} makes the noisy label totally wrong.
+It is often caused by either the mismatch between an image and its surrounding text, or false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
 \end{itemize}
 
-We propose a novel probabilistic model to capture the relations among all these factors.
-We solve the problem by Expectation-Maximization (EM) algorithm and integrate it into a deep learning framework.
-To validate our approach, we collect a clothing classification dataset consisting of around $72,000$ clean labeled and one million noisy labeled data.
-Experiments on this dataset demonstrate that massive noisy labeled data could benefit the training of deep neural networks.
-
-Our work is inspired by~\cite{sukhbaatar2014learning}, which also modifies the deep neural networks to train effectively with noisy labeled data.
-However, their modification is simply implemented by adding a linear layer on top of the softmax layer, which builds on the assumption that label noise is independent with input images.
-We generalize~\cite{sukhbaatar2014learning} to a new deep learning framework by relating the noise to the input image.
-We find that by modeling the noise more appropriately, the deep models can benefit even more from noisy labels.
+The proposed probabilistic model will build the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
+We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
+Experiments on the collected dataset show that our model can better detect and correct the wrong labels.
 
 Our contribution comes from three aspects.
-First, we model label noise generation with a graphical model and further integrate it into the deep learning framework.
-Second, we study different noise types and model their relations with the images by a deep neural network.
-Finally, we collect a large scale clothing classification dataset with both noisy labels and clean labels.
+First, we study the causes of noisy labels in real-world data and describe all the variables with a novel probabilistic model.
+Second, we integrate the model into existing deep learning framework to help detect and correct wrong labels.
+Different training strategies are investigated to make the CNNs learn from better supervisions.
+Finally, a large-scale clothing dataset is collected with both noisy and clean labels, which will be released for academic use.
+
+% TODO: combine these two figures
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
+\end{center}
+\caption{The probability of an image suffering from different noise types depend on the image itself.
+Although all the images belong to class ``T-shirt'', the top two images can be easily recognized, while the bottom two tend to be confused with class ``Chiffon''.}
+\label{fig:compare_noise_level}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
+\end{center}
+\caption{Images tend to be mislabeled usually share similar visual patterns.}
+\label{fig:noise_cluster}
+\end{figure}
 
@@
 Specific to our clothes classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc.
-See Figure~\ref{fig:compare_noise_level} for some examples.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
-\end{center}
-\caption{The probability of an image suffering from different noise types depend on the image itself.
-Although all the images belong to class ``T-shirt'', the top two images can be easily recognized, while the bottom two tend to be confused with class ``Chiffon''.}
-\label{fig:compare_noise_level}
-\end{figure}
 
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
-\end{center}
-\caption{Images tend to suffer from confusing noise usually share similar visual patterns.
-Our model predicts high probability of ``noise free'' for the five images on the top, while predicting high probability of ``confusing noise'' for the bottoms.
-While all the images share the same clean label ``Coat'', the first three images at the bottom row have noisy label ``Windbreaker'' and the latter two have noisy label ``Jacket''.}
-\label{fig:noise_cluster}
-\end{figure}
-
-\begin{figure}[t]
-\begin{center}
 \includegraphics[width=0.8\linewidth]{figure/noise_prediction_rank_precision.pdf}

### 2015-04-01 paper.tex
Add missing references

@@
 Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic}.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
@@
 Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on largescale datasets.
-Weston et al.
-\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
+However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets.
+Chen \etal~\cite{chen2013fast} tackled this problem in the scenario of image tagging by a co-regularized duo classifier that can efficiently use both the image and incomplete tags.
+Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
 But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
@@
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic}.
+Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
 Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
@@
 The effectiveness of our model is validated based on a series of experiments.
-We exploit the AlexNet~\cite{krizhevsky2012imagenet} as our baseline model, which consists of five convolutional layers and three fully connected layers.
+We implement our method by using Caffe~\cite{jia2014caffe} and exploit the AlexNet~\cite{krizhevsky2012imagenet} as the baseline model, which consists of five convolutional layers and three fully connected layers.
 Although recent models may have better learning capability, we choose AlexNet since it is well studied and much easier to be reimplemented (see the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}}).

### 2015-04-01 paper.tex
Polish the section of related work

@@
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning only on the clean labels.
+However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
 Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
@@
 Experiments in the literature show that the performances of classifiers inferred by label noise-robust algorithms are still affected by label noise.
-Label noise-robust methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.
+These methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.
 
@@
 Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
-But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.
+But they need extra information about whether a pair of unlabeled images belong to the same class, which cannot be obtained in our problem.
 
@@
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
-Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.
+Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
+Nevertheless, this transfer learning scheme could be suboptimal when the two tasks are just loosely related.
+In our case of clothing classification, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it from an ImageNet pretrained model only on the clean labels.
 
 {\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels \cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.
-\cite{mnih2012learning} builds a simple noisy model for aerial images but only consider binary classification.
+\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.
 \cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and a specific case.
-\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is independent from source images, ignoring the hardness of labeling different images.
+\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
 % section related_work (end)

### 2015-04-01 paper.tex
Polish the section of label noise model

@@
 To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
-Based on previous analysis of the noise types, we describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
+We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
 
@@
 
-On the other hand, the latent variable $\vec{z}$ representing label noise type is also an 1-of-3 binary random variable. We assign three semantic meanings to each possible state of $\vec{z}$:
+On the other hand, the latent variable $\vec{z}$ representing label noise type is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
 \begin{enumerate}
@@
     \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
-    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are easily confused with $\vec{y}$
+    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are confusing with $\vec{y}$
 \end{enumerate}
 
-Following this assignment rule, we define the conditional probability of the noisy label by
+Following this assignment rule, we define the conditional probability of the noisy label as
 \begin{equation} \label{eq:likelihood}
@@
 
-While the object class probability distribution $p(\vec{y} | \vec{x})$ is comprehensible, the semantic meaning of $p(\vec{z} | \vec{x})$ needs extra clarification: it can be seen as a property of an image, which represents how confusing the image is.
-Specific to our clothes classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc.
+While the class label probability distribution $p(\vec{y} | \vec{x})$ is comprehensible, the semantic meaning of $p(\vec{z} | \vec{x})$ needs extra clarification: it represents how confusing the image content is.
+Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc.
 
-To illustrate the relations between noisy label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution} by
+To illustrate the relations between noisy label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution}
 \begin{equation}
@@
 \label{sub:learning_the_parameters}
-We exploit two deep neural networks to model $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ separately.
+We exploit two CNNs to model $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ separately.
 Denote the parameter set of each deep model by $\theta_1$ and $\theta_2$.
 Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
-Expectation-Maximization algorithm is used to solve this problem iteratively.
+The Expectation-Maximization algorithm is used to solve this problem iteratively.
 
@@
 \textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$.
-Therefore, in each iteration $t$ of the E-Step, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
+Therefore, in each iteration $t$, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
 \begin{multline} \label{eq:posterior}
@@
 
-We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy label.
+We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
 As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
@@
 
-Notice that if the true label of an image is class $i$ while the noisy label is class $j$, then it can only affect the value of $\mat{C}_{ij}$.
+Notice that if the true label is class $i$ while the noisy label is class $j$, then it can only affect the value of $\mat{C}_{ij}$.
 Thus each column of $\mat{C}$ can be optimized separately.

### 2015-04-06 paper.tex
Polish the section of deep learning

@@
 As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
-\begin{equation}
+\begin{equation} \label{eq:opt_all}
     \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)})
@@
 As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
-Moreover, we append a label-noise-model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
-Stochastic Gradient Ascent (SGA) with backpropagation technique is used to approximately optimize the whole network.
-In each forward pass, the label-noise-model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
+Moreover, we append a label noise model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
+Stochastic Gradient Ascent with backpropagation technique is used to approximately optimize the whole network.
+In each forward pass, the label noise model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
 While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.
@@
 Therefore, we need to pretrain each CNN component with strongly supervised data.
-Gathering ground truth object classes is straight forward, since we can just manually label some images by expert.
-The resulting strongly labeled dataset $\mathcal{D}_c$ can be directly used for training the network that predicts $p(\vec{y}|\vec{x})$.
-On the other hand, although off-the-shelf supervision for $p(\vec{z}|\vec{x})$ is not available, we can heuristically generate some data by utilizing the images having both strong and noisy labels.
-For each sample, we choose as ground truth the $\vec{z}$ that maximizes the likelihood in Eq~\eqref{eq:likelihood}.
+Images and their ground truth labels in the dataset $\mathcal{D}_c$ are used to train the CNN that predicts $p(\vec{y}|\vec{x})$.
+On the other hand, the optimal solutions of $\vec{z}^{(1)},\cdots,\vec{z}^{(N)}$ in Eq~\eqref{eq:opt_all} are used to train the CNN that predicts $p(\vec{z}|\vec{x})$.
 
-After both the CNN components are properly pretrained, we can start training the whole network with massive noisy labeled data.
+After both CNN components are properly pretrained, we can start training the whole network with massive noisy labeled data.
 However, some practical issues need to be further discussed.
 First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
-Therefore, we need to mix strongly label data together in to our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNN components.
+Therefore, we need to mix strongly label data into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
 Then each CNN receives two kinds of gradients, one is from the clean labeled data and the other is from the noisy labeled data.
@@
 
-Our proposed method has the ability to figure out the ground truth label given the image and its noisy label.
-From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how confusing is the input image itself.
+Our proposed method has the ability to figure out the true label given the image and its noisy label.
+From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how easily for the image to be mislabeled.
 Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model.
-Meanwhile, we exploit the second kind of information to bridge the semantic gap between the image and its possible noisy labels.
+On the other hand, the second kind of information correlates the image content with the label noise, which can help distinguish between hard samples and mislabeled ones.
 % section weak_label_deep_learning (end)

### 2015-04-06 paper.tex
Polish the subsection of dataset

@@
 
-Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, etc.
+Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, \etc.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
@@
 Each image is automatically assigned a noisy label according to the keywords in its surrounding text.
-After that, we manually refine 72,000 image labels, which constitute a clean sub-dataset.
+After that, we manually refine 72409 image labels, which constitute a clean sub-dataset.
 All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.
@@
 \label{sub:dataset}
-We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites.
+Since there is no publicly available dataset that has both clean and noisy labels, to test our method under real-world scenario, we build a large-scale clothing dataset by crawling images from some online shopping websites.
+More than a million images are collected together with their surrounding texts provided by the sellers.
+These surrounding texts usually contain rich information about the products, which can be further converted to visual tags.
+Specific to our task of clothing classification, we define $14$ class labels: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Hoodie, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.
+We assign an image a noisy label if we find its surrounding text contains only the keywords of that label, otherwise we discard the image to reduce ambiguity.
+
+After that we manually refine the noisy labels of a small portion of all the images and split them into training ($\mathcal{D}_c$), validation and test sets.
+On the other hand, the remaining data construct the noisy labeled training dataset ($\mathcal{D}_n$).
+A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with some image in the validation and test sets, which ensures the reliability of our test protocol.
+Finally, the size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have 14313 and 10526 images, respectively.
+
+The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}.
+We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater).
+This confusion matrix indicates that the noisy labels are not so reliable.
+
+% We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites.
 These surrounding texts are valuable, because they usually contain several keywords that can be further converted to visual tags.
@@
 
-In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets.
+% In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets.
 Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$.

### 2015-04-07 paper.tex
Modification by Yang Yi

@@
 Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
-Various noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise.
-Other noise cleaning algorithms are developed~\cite{barandela2000decontamination,brodley2011identifying}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
+Various label noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise~\cite{bartlett2006convexity,teng2001comparison}.
+Other data cleansing algorithms are proposed~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
 
@@
 
-Although annotating all the noisy data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific task~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
+Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels.
+Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
@@
 Figure~\ref{fig:overview} shows the framework of our approach.
-We collect a million clothes images from E-commerce websites.
-Each image is automatically assigned a noisy label according to the keywords in its surrounding text.
-After that, we manually refine 72409 image labels, which constitute a clean sub-dataset.
+We collect 1,000,000 clothing images from E-commerce websites.
+Each image is automatically assigned with a noisy label according to the keywords in its surrounding text.
+After that, we manually refine 72,409 image labels, which constitute a clean sub-dataset.
 All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.
@@
 Our work is inspired by~\cite{sukhbaatar2014learning}, which modifies a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
-However, they assume noisy labels are conditionally independent with input images given clean labels.
+However,~\cite{sukhbaatar2014learning} assumes noisy labels are conditionally independent with input images given clean labels.
 By examining our collected dataset, we find that this assumption is too strong to fit the real-world data well.
@@
 
-The proposed probabilistic model will build the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
+The proposed probabilistic model build the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
 We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
@@
 Our contribution comes from three aspects.
-First, we study the causes of noisy labels in real-world data and describe all the variables with a novel probabilistic model.
+First, we study the cause of noisy labels in real-world data and describe it with a novel probabilistic model.
 Second, we integrate the model into existing deep learning framework to help detect and correct wrong labels.
-Different training strategies are investigated to make the CNNs learn from better supervisions.
-Finally, a large-scale clothing dataset is collected with both noisy and clean labels, which will be released for academic use.
+We study different training strategies to make the CNNs learn from better supervisions.
+Finally, we collect a large-scale clothing dataset with both noisy and clean labels, which will be released for academic use.
 
@@
 \end{center}
-\caption{The probability of an image suffering from different noise types depend on the image itself.
+\caption{The probability of an image suffering from different noise types depends on the image itself.
 Although all the images belong to class ``T-shirt'', the top two images can be easily recognized, while the bottom two tend to be confused with class ``Chiffon''.}
@@
 \end{figure}
-
-% section related_work (end)
+% section introduction (end)
 
@@
 \label{sec:related_work}
-For most of the related works including effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to \cite{frenay2013classification} for a comprehensive review.
+For most of the related works including effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2013classification} for a comprehensive review.
 
-{\bf Direct learning with noisy labels:} Among other consequences, many works have shown that noise can adversely impact the classification performances of induced classifiers \cite{zhu2004class}.
-Experiments in the literature show that the performances of classifiers inferred by label noise-robust algorithms are still affected by label noise.
-These methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.
+{\bf Direct learning with noisy labels:} Many works have shown that label noise can adversely impact the classification accuracy of induced classifiers~\cite{zhu2004class}.
+To better handle label noise, some approaches rely on training classifiers with label noise-robust algorithms~\cite{beigman2009learning,manwani2013noise}.
+However,~\cite{bartlett2006convexity} proves that most of the loss functions are not completely robust to label noise.
+Experiments in~\cite{teng2001comparison} show that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
+These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2013classification}.
+On the other hand, some label noise cleansing methods are proposed to remove or correct mislabeled instances~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
+Thus they may remove too many instances and the overcleansing can reduce the performances of classifiers~\cite{matic1992computer}.
 
-{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
-Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on large-scale datasets.
+{\bf Semi-supervised learning:} Apart from directly learning with label noise, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
+Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
+However, it suffers from computing pairwise distance, which has quadratic complexity with the number of samples and cannot be applied on large-scale datasets.
 Chen \etal~\cite{chen2013fast} tackled this problem in the scenario of image tagging by a co-regularized duo classifier that can efficiently use both the image and incomplete tags.
@@
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
+Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
 Nevertheless, this transfer learning scheme could be suboptimal when the two tasks are just loosely related.
@@
 
-{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels \cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.
-\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.
-\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and a specific case.
-\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
+{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.~\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.~\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and a specific case.~\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
+Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent noise but also input dependent noise.
 % section related_work (end)
@@
 A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with some image in the validation and test sets, which ensures the reliability of our test protocol.
-Finally, the size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have 14313 and 10526 images, respectively.
+Finally, the size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have 14,313 and 10,526 images, respectively.
 

### 2015-04-07 paper.tex
Polish the last two sections

@@
 Figure~\ref{fig:overview} shows the framework of our approach.
-We collect 1,000,000 clothing images from E-commerce websites.
+We collect $1,000,000$ clothing images from E-commerce websites.
 Each image is automatically assigned with a noisy label according to the keywords in its surrounding text.
-After that, we manually refine 72,409 image labels, which constitute a clean sub-dataset.
+After that, we manually refine $72,409$ image labels, which constitute a clean sub-dataset.
 All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.
@@
 \section{Deep Learning from Noisy Labels} % (fold)
-\label{sec:weak_label_deep_learning}
+\label{sec:deep_learning_from_noisy_labels}
 
@@
 On the other hand, the second kind of information correlates the image content with the label noise, which can help distinguish between hard samples and mislabeled ones.
-% section weak_label_deep_learning (end)
+% section deep_learning_from_noisy_labels (end)
 
@@
 A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with some image in the validation and test sets, which ensures the reliability of our test protocol.
-Finally, the size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have 14,313 and 10,526 images, respectively.
+Finally, the size of training datasets are $|\mathcal{D}_c| = 47,570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have $14,313$ and $10,526$ images, respectively.
 
 The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}.
-We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater).
-This confusion matrix indicates that the noisy labels are not so reliable.
-
-% We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites.
-These surrounding texts are valuable, because they usually contain several keywords that can be further converted to visual tags.
-Specific to our task of clothes classification, we define $14$ classes: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Coat, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.
-
-% In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets.
-Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$.
-A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our test protocol.
-The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and test set consist of 14,313 and 10,526 images respectively.
-The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}.
-We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding texts are quite noisy.
+We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater), which means that the noisy labels are not so reliable.
 
@@
 \end{figure}
-
 % subsection dataset (end)
 
-\subsection{Evaluation} % (fold)
+\subsection{Evaluation on the Collected Dataset} % (fold)
 \label{sub:evaluation}
-The effectiveness of our model is validated based on a series of experiments.
-We implement our method by using Caffe~\cite{jia2014caffe} and exploit the AlexNet~\cite{krizhevsky2012imagenet} as the baseline model, which consists of five convolutional layers and three fully connected layers.
-Although recent models may have better learning capability, we choose AlexNet since it is well studied and much easier to be reimplemented (see the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}}).
+We validate our method through a series of experiments conducted on the collected dataset.
+Our implementation is based on Caffe~\cite{jia2014caffe}, and the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}} is chosen as the baseline model, which approximates AlexNet~\cite{krizhevsky2012imagenet}.
+Besides, we reimplement two other approaches.
+One is a semi-supervised learning method called Pseudo-Label~\cite{lee2013pseudo}, which exploits classifier's prediction as ground truth for unlabeled data.
+The other one is the Bottom-Up method introduced in~\cite{sukhbaatar2014learning}, where the relation between noisy labels and clean labels are built by a confusion matrix $Q$.
+In the experiments, we directly use the true $Q$ as shown in Figure~\ref{fig:cm_strong_weak} instead of estimating its values.
 
-We also implement the bottom up method introduced in~\cite{sukhbaatar2014learning}.
-Briefly speaking, they proposed a noise model with the assumption that a noisy label is only related to its true label.
-The relation is built by a confusion matrix $Q$ whose values can be easily obtained as Figure~\ref{fig:cm_strong_weak} in our problem.
+We list all the experiment settings in Table~\ref{tab:models}.
+Different methods require different training data.
+We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions.
+On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
+Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as ground truths for AlexNet, and are discarded for Pseudo-Label.
 
-We list all the models and training strategies to be compared in Table~\ref{tab:models}.
-In general, we set the initial learning rate to be $0.001$ and is multiplied by $0.1$ every $50000$ iterations.
-For each method, we keep training the model until it converges.
+In general, we use a mini-batch size of $256$.
+The learning rate is initialized to be $0.001$ and is divided by $10$ after every $50,000$ iterations.
+We keep training each model until convergence.
 Classification accuracies on both the validation and test set are presented in Table~\ref{tab:accuracy}.
@@
 \begin{center}
-\begin{tabular}{c|p{3.5em}|p{8em}|p{6em}}
+\begin{tabular}{c|p{3.5em}|p{9em}|p{5em}}
 \hline
-\# & Method & Data & Initialization \\
+\# & Method & Training Data & Initialization \\
 \hline\hline
@@
 \hline
-2 & AlexNet & $\mathcal{D}_c$ & \texttt{ilsvrc2012} pretrained model \\
+2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained \\
 \hline
-3 & AlexNet & $\mathcal{D}_c \cup \mathcal{D}_n$ but treat noisy labels in $\mathcal{D}_n$ as ground truth & random \\
+3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random \\
 \hline
-4 & AlexNet & $\mathcal{D}_c \cup \mathcal{D}_n$ but treat noisy labels in $\mathcal{D}_n$ as ground truth & \texttt{ilsvrc2012} pretrained model \\
+4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained \\
 \hline
-5 & Bottom Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c \cup \mathcal{D}_n$ & model \#2 \\
+5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 \\
 \hline
-6 & Ours & $\mathcal{D}_c \cup \mathcal{D}_n$ & model \#2 \\
+6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 \\
+\hline
+7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
+\hline
+8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
 \hline
@@
 \end{center}
-\caption{Models and corresponding training strategies used in our experiments}
+\caption{Experiment settings}
 \label{tab:models}
 \end{table}
-
-\begin{figure*}
-\begin{center}
-\end{center}
-\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
-\label{fig:model_output}
-\end{figure*}
-
-From row 1 we can see that when only a small amount of strongly supervised data is provided to train the deep neural network, the parameters cannot be learned properly and thus results in a bad performance.
-To cope with this problem, finetuning from a model pretrained on related but much larger dataset can significantly improve the accuracy, which is illustrated in the result of model \#2.
-This is a commonly used technique to train a deep model with limited data for specific task.
-
-However, this transfer learning scheme may still suffer from suboptimal model parameters if the datasets for pretraining and finetuning are loosely related, just like the clothes vs.
-general objects in our case.
-We see from row 3 that better performance can be achieved when we train the same model with random initialization on massive data with label noise, but treat noisy labels just as ground truth.
-Model \#4 further improves the accuracy by initializing with ImageNet pretrained model.
 
@@
 \hline
-4 & 75.57\% & 75.30\% \\
+4 & 75.06\% & 75.13\% \\
 \hline
-5 & 75.97\% & 76.22\% \\
+5 & 75.57\% & 75.30\% \\
 \hline
-6 & 77.65\% & 78.24\% \\
+6 & 73.10\% & 73.04\% \\
+\hline
+7 & 75.97\% & 76.22\% \\
+\hline
+8 & \textbf{77.65\%} & \textbf{78.24\%} \\
 \hline
@@
 
-Row 5 and 6 show the effect of handling label noise.
-While model \#5 is only $0.4\% \sim 0.9\%$ better than the baseline model \#4, our proposed method gains improvement of $2.1\% \sim 2.9\%$.
-Since model \#5 assumes that the noisy label only relates to the ground truth, which may not be appropriate in our problem.
-On the contrary, our model predicts the noise type from the image itself.
-We will discuss about it in the following section.
-% subsection evaluation (end)
+\begin{figure*}
+\begin{center}
+\end{center}
+\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
+\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
+\label{fig:model_output}
+\end{figure*}
+
+We first study the effect of transfer learning and massive noisy labeled data.
+From row \#1 we can see that training a CNN from scratch with only small amount of clean data can result in bad performance.
+To deal with this problem, finetuning from an ImageNet pretrained model can significantly improve the accuracy, as shown in row \#2.
+However, by comparing row \#2 and \#3, we find that training with random initialization on additional massive noisy labeled data is better than finetuning only on the clean data, which demonstrates the power of using large-scale yet easily obtained noisy labeled data.
+The accuracy can be further improved if we finetune the model either from an ImageNet pretrained one or model \#2.
+The latter one has slightly better performance thus is used to initialize the remaining methods.
+
+Next, from row \#6 we can see that semi-supervised learning methods may not be a good choice when massive noisy labeled data are available.
+Although model \#6 achieves marginally better result than its base model, it is significantly inferior to model \#5, which indicates that simply discarding all the noisy labels cannot make the full use of these information.
+
+Finally, row \#7 and \#8 show the effect of modeling the label noise.
+Model \#7 is only $0.4\% \sim 0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.1\% \sim 2.9\%$.
+This result does credit to our image dependent label noise model, which fits better to the noisy labeled data crawled from the Internet.
+
+\subsection{Evaluation on Synthetic Dataset} % (fold)
+\label{sub:evaluation_on_synthetic_dataset}
+We also conduct synthetic experiments on CIFAR-10 following the settings of~\cite{sukhbaatar2014learning}.
+We first randomly generate a confusion matrix $Q$ between clean labels and noisy labels, and then corrupt the training labels according to it.
+We use Caffe's CIFAR10-quick as the base model and compare our method with~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) under different noise levels.
+The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c|c|c|c}
+\hline
+Noise Level & Base Model & \cite{sukhbaatar2014learning} & Ours \\
+\hline\hline
+30\% & 65.57\% & 69.73\% & 69.81\% \\
+\hline
+40\% & 62.38\% & 66.66\% & 66.76\% \\
+\hline
+50\% & 57.36\% & 63.39\% & 63.00\% \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Classification accuracies on CIFAR-10 with synthetic label noise}
+\label{tab:accuracy_synthetic}
+\end{table}
+
+It should be noticed that~\cite{sukhbaatar2014learning} assumed distribution of noisy labels only depends on classes, while we assume it also depends on image content.
+This kind of synthetic label noise exactly matches their assumption but is unfavored to our model.
+Thus the noise type prediction in our model could be less informative.
+Nevertheless, our model achieved comparable results with~\cite{sukhbaatar2014learning}.
+% subsection evaluation_on_synthetic_dataset (end)
 
@@
 \label{sub:effect_of_noise_estimation}
-In order to understand the way our model handles noisy labels, we demonstrate several examples in Figure~\ref{fig:model_output}.
-We can see that given a noisy label, our model could exploit its current prediction to correct the noise by setting a large weight to the true label, and then use it as supervision instead of the noisy one.
+In order to understand how does our model handle noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
+We can see that given a noisy label, our model could exploit its current knowledge to estimate the probability distribution of the true label, and then use it as supervision instead of the noisy one.
 Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong as shown in the top-right and bottom-left block respectively, our model can still figure out the correct label.
 
-Next we explain the meaning of $p(\vec{z}|\vec{x})$ by taking a look at our model's prediction on samples drawn from the clean label class ``Coat''.
-As shown in Figure~\ref{fig:noise_cluster}, the noisy label is not simply related to the ground truth.
-On the contrary, images that have high probability of confusing noise tend to share similar visual patterns.
-This observation indicates that $p(\vec{z}|\vec{x})$ is a property of an image itself representing how confusing the image is.
-Our model is trained to capture these information and exploit them to clarify the noisy labels.
-Figure~\ref{fig:noise_prediction_rp} further shows the rank-precision curve of our model's noise prediction.
-We can see that nearly $80\%$ of the top-500 high confident ``confusing'' samples actually suffer from noise, which again verifies the feasibility of our proposed noise model.
+Next we demonstrate the effect of learning to predict the label noise type.
+We estimate $p(\vec{z}_2=1|\vec{x})+p(\vec{z}_3=1|\vec{x})$ on the validation set and sort the images accordingly in descending order.
+Then for each image, we check whether its noisy label mismatches its clean label.
+The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
+It shows that the intuitive observation --- images tend to be mislabeled often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to help handle noisy labels.
 
@@
 \end{center}
-\caption{We first sort our model's ``confusing noise'' prediction on the validation set, and then check whether the noisy label of the corresponding image mismatch its true label.
-The rank-precision curve is plotted.}
+\caption{Rank-precision curve of label noise prediction}
 \label{fig:noise_prediction_rp}
@@
 \label{sec:conclusion}
-In this paper, we raised the problem of training a deep neural network with limited clean annotations and massive noisy labeled data.
-A novel end-to-end deep learning framework is proposed to handle label noise in training data.
-We exploit a novel probabilistic model to describe how a noisy label is generated.
-Two latent variables --- ground truth and noise type -- are introduced to bridge the semantic gap between the observed image and its corresponding noisy label.
-We solve the problem by EM algorithm and integrate it into the deep learning framework.
-Experiments on a large-scale clothes dataset show that massive noisy label data could benefit the training of deep models, and utilizing our noise handling method can further improve the performance.
+In this paper, we raised the problem of training a classifier with limited clean annotations and massive noisy labeled data.
+We proposed a novel probabilistic model to describe how a noisy label is generated.
+Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between the observed image and its noisy label.
+We solved the problem by EM algorithm and integrated it into existing deep learning framework.
+Experiments on a collected large-scale clothing dataset showed that massive noisy label data could benefit the training of deep models, and utilizing our method could further improve the performance.
 % section conclusion (end)

### 2015-04-08 paper.tex
Merge tables

@@
 
-We list all the experiment settings in Table~\ref{tab:models}.
+We list all the experiment settings in Table~\ref{tab:exp}.
 Different methods require different training data.
@@
 We keep training each model until convergence.
-Classification accuracies on both the validation and test set are presented in Table~\ref{tab:accuracy}.
+Classification accuracies on the test set are presented in Table~\ref{tab:exp}.
 
-\begin{table}
+\begin{table*}[t]
 \begin{center}
-\begin{tabular}{c|p{3.5em}|p{9em}|p{5em}}
+\begin{tabular}{c|c|c|c|c}
 \hline
-\# & Method & Training Data & Initialization \\
+\# & Method & Training Data & Initialization & Test Accuracy\\
 \hline\hline
-1 & AlexNet & $\mathcal{D}_c$ & random \\
-\hline
-2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained \\
-\hline
-3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random \\
-\hline
-4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained \\
-\hline
-5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 \\
-\hline
-6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 \\
-\hline
-7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
-\hline
-8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
+1 & AlexNet & $\mathcal{D}_c$ & random & 64.54\% \\
+2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained & 72.63\% \\
+3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random & 74.03\% \\
+4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained & 75.13\% \\
+5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 & 75.30\% \\
+6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 & 73.04\% \\
+7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & 76.22\% \\
+8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & \textbf{78.24\%} \\
 \hline
@@
 \end{center}
-\caption{Experiment settings}
-\label{tab:models}
-\end{table}
+\caption{Experiment results on the collected dataset}
+\label{tab:exp}
+\end{table*}
 
-\begin{table}
-\begin{center}
-\begin{tabular}{c|c|c}
-\hline
-\# & Validation Accuracy & Test Accuracy \\
-\hline\hline
-1 & 64.28\% & 64.54\% \\
-\hline
-2 & 72.21\% & 72.63\% \\
-\hline
-3 & 73.76\% & 74.03\% \\
-\hline
-4 & 75.06\% & 75.13\% \\
-\hline
-5 & 75.57\% & 75.30\% \\
-\hline
-6 & 73.10\% & 73.04\% \\
-\hline
-7 & 75.97\% & 76.22\% \\
-\hline
-8 & \textbf{77.65\%} & \textbf{78.24\%} \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Classification accuracies on validation and test set}
-\label{tab:accuracy}
-\end{table}
+% \begin{table}
+% \begin{center}
+% \begin{tabular}{c|c|c}
+% \hline
+% \# & Validation Accuracy & Test Accuracy \\
+% \hline\hline
+% 1 & 64.28\% & 64.54\% \\
+% \hline
+% 2 & 72.21\% & 72.63\% \\
+% \hline
+% 3 & 73.76\% & 74.03\% \\
+% \hline
+% 4 & 75.06\% & 75.13\% \\
+% \hline
+% 5 & 75.57\% & 75.30\% \\
+% \hline
+% 6 & 73.10\% & 73.04\% \\
+% \hline
+% 7 & 75.97\% & 76.22\% \\
+% \hline
+% 8 & \textbf{77.65\%} & \textbf{78.24\%} \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{Classification accuracies on validation and test set}
+% \label{tab:accuracy}
+% \end{table}
 
@@
 Finally, row \#7 and \#8 show the effect of modeling the label noise.
-Model \#7 is only $0.4\% \sim 0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.1\% \sim 2.9\%$.
+Model \#7 is only $0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.9\%$.
 This result does credit to our image dependent label noise model, which fits better to the noisy labeled data crawled from the Internet.

### 2015-04-08 paper.tex
Update all the figures

@@
 \begin{center}
-\includegraphics[width=0.9\linewidth]{figure/overview.pdf}
+\includegraphics[width=0.95\linewidth]{figure/overview.pdf}
 \end{center}
@@
 Labels of web images often suffer from different types of noise.
-A probabilistic model is proposed to detect and correct the wrong labels.
-The corrected labels are used to train underlying CNNs.}
+A label noise model is proposed to detect and correct the wrong labels.
+The corrected labels are used to train the underlying CNNs.}
 \label{fig:overview}
@@
 Figure~\ref{fig:overview} shows the framework of our approach.
-We collect $1,000,000$ clothing images from E-commerce websites.
+We collect $1,000,000$ clothing images from some online shopping websites.
 Each image is automatically assigned with a noisy label according to the keywords in its surrounding text.
@@
 
-% TODO: combine these two figures
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
-\end{center}
-\caption{The probability of an image suffering from different noise types depends on the image itself.
-Although all the images belong to class ``T-shirt'', the top two images can be easily recognized, while the bottom two tend to be confused with class ``Chiffon''.}
-\label{fig:compare_noise_level}
-\end{figure}
-
 \begin{figure}[t]
@@
 \end{center}
-\caption{Images tend to be mislabeled usually share similar visual patterns.}
+\caption{Images tend to be mislabeled often share similar visual patterns.}
 \label{fig:noise_cluster}
@@
 Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc.
+We show some examples in Figure~\ref{fig:compare_noise_level}.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
+\end{center}
+\caption{Predicting noise types of four different ``T-shirt'' images.
+The top two can be recognized with little ambiguity, while the bottom two are easily confusing with the class ``Chiffon''.
+Image content can affect the possibility of it to be mislabeled.}
+\label{fig:compare_noise_level}
+\end{figure}
 
@@
 \end{center}
-\caption{System diagram of our proposed method.
-Two CNNs are exploited to predict object class $p(\vec{y}|\vec{x})$ and noise type $p(\vec{z}|\vec{x})$ respectively.
-A label noise model layer infers the ground truths according to CNNs' results and the observed noisy label.
-The ground truth is then used to supervise the CNNs.
-A separate strongly labeled dataset is also utilized to prevent the model from drifting away.}
+\caption{System diagram of our method.
+Two CNNs are used to predict the class label $p(\vec{y}|\vec{x})$ and the noise type $p(\vec{z}|\vec{x})$, respectively.
+The label noise model layer infers the true label according to the predictions and the noisy label, which is then used to supervise the training of CNNs.
+Data with clean labels are also mixed in to prevent the models from drifting away.}
 \label{fig:framework}
@@
 First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
-Therefore, we need to mix strongly label data into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
+Therefore, we need to mix the data with clean labels into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
 Then each CNN receives two kinds of gradients, one is from the clean labeled data and the other is from the noisy labeled data.
@@
 \end{center}
-\caption{\textbf{Confusion matrix between clean and noisy labels}.
+\caption{Confusion matrix between clean and noisy labels.
 We hide extremely small grid numbers for better demonstration.
@@
 \includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{\textbf{Examples of model predictions}. The information layout in each block is illustrated in the top-left one.}
+\caption{Examples of handling noisy labels. The information layout in each block is illustrated in the top-left one.}
 \label{fig:model_output}
@@
 \end{center}
-\caption{Classification accuracies on CIFAR-10 with synthetic label noise}
+\caption{Accuracies on CIFAR-10 with synthetic label noise}
 \label{tab:accuracy_synthetic}
@@
 Thus the noise type prediction in our model could be less informative.
-Nevertheless, our model achieved comparable results with~\cite{sukhbaatar2014learning}.
+Nevertheless, our model achieves comparable results with~\cite{sukhbaatar2014learning}.
 % subsection evaluation_on_synthetic_dataset (end)
@@
 In order to understand how does our model handle noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
-We can see that given a noisy label, our model could exploit its current knowledge to estimate the probability distribution of the true label, and then use it as supervision instead of the noisy one.
-Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong as shown in the top-right and bottom-left block respectively, our model can still figure out the correct label.
+We can see that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label, and then use it as supervision instead of the noisy one.
+Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong, our model can still figure out the correct label.
 
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{figure/noise_prediction_rank_precision.pdf}
+\includegraphics[width=1.0\linewidth]{figure/noise_prediction_rank_precision.pdf}
 \end{center}

### 2015-04-08 figure/make_cm.py

@@ -5,7 +5,7 @@ import cPickle
 from argparse import ArgumentParser
 
 _label_names = [
-    'T-Shirt', 'Shirt', 'Knitwear', 'Chiffon', 'Sweater', 'Coat', 'Windbreaker',
+    'T-Shirt', 'Shirt', 'Knitwear', 'Chiffon', 'Sweater', 'Hoodie', 'Windbreaker',
     'Jacket', 'Down Coat', 'Suit', 'Shawl', 'Dress', 'Vest', 'Underwear']
 
 def _unpickle(file_path):
@@ -37,19 +37,22 @@ def draw_cm(file_path, output=None):
                           va='center', ha='center', color='#111111')
 
     # plt.title('Average Accuracy {:.2%}'.format(acc))
-    plt.xlabel('True Label', fontsize=8)
-    plt.ylabel('Weak Label', fontsize=8)
+    plt.xlabel('True Label', fontsize=12, fontweight='bold')
+    plt.ylabel('Noisy Label', fontsize=12, fontweight='bold')
     axes.set_xticks([i for i in xrange(n)])
     axes.set_yticks([i for i in xrange(n)])
     axes.set_yticklabels(_label_names, fontsize=7)
 
     x_tl = []
     for i, (name, freq) in enumerate(zip(_label_names, freq)):
-        if i % 2 == 0:
-            x_tl.append('{}\n\n{:.1%}'.format(name, freq))
+        if i % 3 == 0:
+            x_tl.append('{}\n\n\n{:.1%}'.format(name, freq))
+        elif i % 3 == 1:
+            x_tl.append('\n{}\n\n{:.1%}'.format(name, freq))
         else:
-            x_tl.append('\n{}\n{:.1%}'.format(name, freq))
-    axes.set_xticklabels(x_tl, fontsize=7)
+            x_tl.append('\n\n{}\n{:.1%}'.format(name, freq))
+    axes.set_xticklabels(x_tl, fontsize=8)
+    axes.tick_params(width=0)
 
     if output is not None:
         plt.savefig(output)

### 2015-04-08 figure/make_zstat.py

@@ -15,11 +15,15 @@ def draw_zstat(file_path, output=None, topk=None):
     if topk is not None:
         rank_precision = rank_precision[0:topk]
 
-    plt.plot(rank_precision, linewidth=2.0, color='#111111')
-    plt.xlabel('Rank', fontsize=24)
-    plt.ylabel('Precision', fontsize=24)
+    plt.plot(rank_precision, linewidth=2.5, color='#111111')
+    plt.xlabel('Rank', fontsize=24, fontweight='bold')
+    plt.ylabel('Precision', fontsize=24, fontweight='bold')
     plt.ylim(0.0, 1.0)
     plt.tick_params(labelsize='large')
+
+    fig = plt.gcf()
+    fig.set_figheight(6)
+    fig.set_figwidth(12)
 
     if output is not None:
         plt.savefig(output)

### 2015-04-08 paper.tex
Update the abstract

@@
 \begin{abstract}
-Large-scale supervised datasets are crucial to train deep neural networks for various computer vision problems.
+Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems.
 However, obtaining a massive amount of well labeled data is usually very expensive and time consuming.
-In this paper, we introduce a general framework to train deep nets with only limited number of clean labels and millions of easily obtained noisy labels.
-We model label noises with a graphical probabilistic framework and further integrate it into the deep learning system.
-To demonstrate the performance of our approach, we collect a large scale clothing classification dataset with both noisy and clean labels.
-We demonstrate the effectiveness of our approach on this dataset, showing the possibility of learning a strong deep model with only a small amount of clean labels.
+In this paper, we introduce a general framework to train CNNs with only limited number of clean labels and millions of easily obtained noisy labels.
+We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system.
+To demonstrate the effectiveness of our approach, we collect a large-scale clothing classification dataset with both noisy and clean labels.
+Experiments on this dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
 \end{abstract}
@@
 A label noise model is proposed to detect and correct the wrong labels.
-The corrected labels are used to train the underlying CNNs.}
+The corrected labels are used to train underlying CNNs.}
 \label{fig:overview}

### 2015-04-09 paper.tex
Polish the whole paper

@@
 
-\renewcommand\Authands{ and }
+\renewcommand\Authands{, and }
 
@@
 
-Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, \etc.
+Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, \etc.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
@@
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a Convolutional Neural Network (CNN) from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
+However, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
 Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
@@
 
-To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the ground truths and uses them to supervise the training of the network.
+To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the true labels and uses them to supervise the training of the network.
 Our work is inspired by~\cite{sukhbaatar2014learning}, which modifies a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
@@
 
-The proposed probabilistic model build the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
+The proposed probabilistic model builds the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
 We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
@@
 First, we study the cause of noisy labels in real-world data and describe it with a novel probabilistic model.
-Second, we integrate the model into existing deep learning framework to help detect and correct wrong labels.
+Second, we integrate the model into a deep learning framework to help detect and correct wrong labels.
 We study different training strategies to make the CNNs learn from better supervisions.
@@
 {\bf Semi-supervised learning:} Apart from directly learning with label noise, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
-Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of samples and cannot be applied on large-scale datasets.
+Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well labeled data to classify unlabeled samples.
+However, it suffers from computing pairwise distance, which has quadratic complexity with the number of samples thus cannot be applied on large-scale datasets.
 Chen \etal~\cite{chen2013fast} tackled this problem in the scenario of image tagging by a co-regularized duo classifier that can efficiently use both the image and incomplete tags.
@@
 
-{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features.
+{\bf Transfer learning:} The success of CNNs lies in their capability of learning rich and hierarchical image features.
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
+Researchers proposed to conquer this problem by first initializing CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
 Nevertheless, this transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothing classification, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it from an ImageNet pretrained model only on the clean labels.
+In our case of clothing classification, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
 
-{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.~\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.~\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and a specific case.~\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
+{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.~\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.~\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and special case.~\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
 Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent noise but also input dependent noise.
@@
 \label{sec:label_noise_model}
-We target on the problem of learning a classifier from a set of images with noisy labels.
-To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
+We target on learning a classifier from a set of images with noisy labels.
+To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with the $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
 We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
@@
 
-Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the ground truth and the type of label noise, respectively.
+Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the true label and the label noise type, respectively.
 Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.
 
-On the other hand, the latent variable $\vec{z}$ representing label noise type is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
+On the other hand, the label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
 \begin{enumerate}
@@
     p(\tilde{\vec{y}}|\vec{y},\vec{z}) = \begin{cases}
-        \mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
-        \frac{1}{L-1}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
-        \mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
+        \tilde{\vec{y}}^{T}\mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
+        \frac{1}{L-1}\tilde{\vec{y}}^{T}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
+        \tilde{\vec{y}}^{T}\mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
     \end{cases}
@@
 Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
-The Expectation-Maximization algorithm is used to solve this problem iteratively.
+The Expectation-Maximization algorithm is used to iteratively solve this problem.
 
-For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood by
+For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood
 \begin{equation}
@@
 \end{equation}
-\textbf{M-Step} Since deep neural networks are exploited to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, we perform gradient ascent on $Q$:
+\textbf{M-Step} We exploit two CNNs to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, respectively.
+Thus the gradient of $Q$ \wrt $\theta$ can be decoupled into two parts:
 \begin{multline} \label{eq:gradient}
@@
 Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process.
-Because without other regularizations, learning all the three parts could lead to trivial solutions.
+Because without other regularizations, learning all the three parts in Eq~\eqref{eq:joint_distribution} could lead to trivial solutions.
 For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$.
-To avoid this degeneration, we choose to give $\mat{C}$ a good estimation while let the deep model learn to predict $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ for each input image.
-
-We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
+To avoid this degeneration, we estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
 As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
@@
 Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal.
-So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
+So that we discard those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
 \begin{equation}
@@
 
-Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+L^2)$ time complexity.
-Before we introduce the algorithm itself, some theorems need to be proved.
-Denote the optimal solution by $\mat{C}^*$ and $\vec{t}^*$
-\begin{lemma}
+Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+L^2)$ time complexity. Denote the optimal solution by $\mat{C}^*$ and $\vec{t}^*$
+\begin{theorem}
 $\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,L\}$
-\end{lemma}
+\end{theorem}
 \begin{proof}
@@
 Second, for all the samples $n$ where $\tilde{\vec{y}}^{(n)}_i=1$ and $\vec{y}^{(n)}_j=1$, we set $\vec{t}_n$ to 1.
-The resulting $E$ is always greater than the original one, which leads to a contradiction.
+The resulting $E$ will get increased, which leads to a contradiction.
 \end{proof}
@@
 Suppose $\tilde{\vec{y}}^{(i)}_k=\tilde{\vec{y}}^{(j)}_k=1$ and $\vec{y}^{(i)}_l=\vec{y}^{(j)}_l=1$ but $\vec{t}^*_i \neq \vec{t}^*_j$.
-From Lemma 1 we know that elements in $\mat{C}^*$ is either 0 or greater than $\alpha$.
+From Theorem 1 we know that elements in $\mat{C}^*$ is either 0 or greater than $\alpha$.
 If $\mat{C}^*_{kl}=0$, we can set $\vec{t}^*_i=\vec{t}^*_j=1$, otherwise we can set $\vec{t}^*_i=\vec{t}^*_j=0$.
-In either case the objective function $E$ is greater than the original one, which draws a contradiction.
+In either case the resulting $E$ will get increased, which leads to a contradiction.
 \end{proof}
@@
 For the second part, $\vec{t}^*_i=1$ implies $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} \leq \alpha$.
-By using Lemma 1 we know that $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0$.
+By using Theorem 1 we know that $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0$.
 \end{proof}
@@
 Theorem 1 further shows that samples with same pair of $(\tilde{\vec{y}},\vec{y})$ share a same noise type.
-Then what really matters is the frequency of each of the $L\times L$ pairs $(\tilde{\vec{y}},\vec{y})$.
+Then what really matters is the frequencies of all the $L\times L$ pairs of $(\tilde{\vec{y}},\vec{y})$.
 Considering a particular column $\vec{c}$, suppose there are $M$ samples affecting this column.
-We can count the frequency of noisy label class 1 to $L$ as $m_1,\dots,m_L$ and might as well set $m_1\geq m_2\geq \cdots \geq m_L$.
+We can count the frequencies of noisy label class 1 to $L$ as $m_1,\dots,m_L$ and might as well assume $m_1\geq m_2\geq \cdots \geq m_L$.
 The problem is then converted to
@@
 \end{equation}
-Then by using Theorem 2, there must exist a $k^* \in \{1,\dots,L\}$ such that
+Then by using Theorem 3, there must exist a $k^* \in \{1,\dots,L\}$ such that
 \begin{equation} \label{eq:opt_t}
@@
 Therefore, we need to mix the data with clean labels into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
-Then each CNN receives two kinds of gradients, one is from the clean labeled data and the other is from the noisy labeled data.
+Then each CNN receives two kinds of gradients, one is from the clean labels and the other is from the noisy labels.
 We denote them by $\Delta_c$ and $\Delta_n$, respectively.
-A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than the noisy data.
+A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than noisy data.
 To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$.
@@
 \label{sub:dataset}
-Since there is no publicly available dataset that has both clean and noisy labels, to test our method under real-world scenario, we build a large-scale clothing dataset by crawling images from some online shopping websites.
+Since there is no publicly available dataset that has both clean and noisy labels, to test our method under real-world scenario, we build a large-scale clothing dataset by crawling images from several online shopping websites.
 More than a million images are collected together with their surrounding texts provided by the sellers.
@@
 After that we manually refine the noisy labels of a small portion of all the images and split them into training ($\mathcal{D}_c$), validation and test sets.
-On the other hand, the remaining data construct the noisy labeled training dataset ($\mathcal{D}_n$).
-A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with some image in the validation and test sets, which ensures the reliability of our test protocol.
+On the other hand, the remaining samples construct the noisy labeled training dataset ($\mathcal{D}_n$).
+A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with any image in the validation or test set, which ensures the reliability of our test protocol.
 Finally, the size of training datasets are $|\mathcal{D}_c| = 47,570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have $14,313$ and $10,526$ images, respectively.
@@
 On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
-Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as ground truths for AlexNet, and are discarded for Pseudo-Label.
+Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
 
@@
 We first randomly generate a confusion matrix $Q$ between clean labels and noisy labels, and then corrupt the training labels according to it.
-We use Caffe's CIFAR10-quick as the base model and compare our method with~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) under different noise levels.
+Based on Caffe's CIFAR10-quick model, we compare~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
 The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
@@
 
-It should be noticed that~\cite{sukhbaatar2014learning} assumed distribution of noisy labels only depends on classes, while we assume it also depends on image content.
+It should be noticed that~\cite{sukhbaatar2014learning} assumes distribution of noisy labels only depends on classes, while we assume it also depends on image content.
 This kind of synthetic label noise exactly matches their assumption but is unfavored to our model.
-Thus the noise type prediction in our model could be less informative.
+Thus the noise type predictions in our model could be less informative.
 Nevertheless, our model achieves comparable results with~\cite{sukhbaatar2014learning}.
@@
 \end{center}
-\caption{Rank-precision curve of label noise prediction}
+\caption{Rank-precision curve of label noise predictions}
 \label{fig:noise_prediction_rp}
@@
 Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between the observed image and its noisy label.
-We solved the problem by EM algorithm and integrated it into existing deep learning framework.
+We solved the problem by the EM algorithm and integrated it into a deep learning framework.
 Experiments on a collected large-scale clothing dataset showed that massive noisy label data could benefit the training of deep models, and utilizing our method could further improve the performance.

### 2015-04-09 paper.tex
Polish by xgwang

@@
 However, obtaining a massive amount of well labeled data is usually very expensive and time consuming.
-In this paper, we introduce a general framework to train CNNs with only limited number of clean labels and millions of easily obtained noisy labels.
+In this paper, we introduce a general framework to train CNNs with only a limited number of clean labels and millions of easily obtained noisy labels.
 We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system.
@@
 
-Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, \etc.
+Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, and scene classification~\cite{farabet2013learning}.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
@@
 extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
-Unfortunately, these labels are extremely unreliable due to the various types of noise (i.e.
+Unfortunately, these labels are extremely unreliable due to various types of noise (i.e.
 labeling mistakes from annotators or computing errors from extraction algorithms).
@@
 Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people first initialize the parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
+Based on the observation of transferability of deep neural networks, people initialize parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
+However, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on clean labels.
 Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
@@
 Figure~\ref{fig:overview} shows the framework of our approach.
-We collect $1,000,000$ clothing images from some online shopping websites.
+We collect $1,000,000$ clothing images from online shopping websites.
 Each image is automatically assigned with a noisy label according to the keywords in its surrounding text.
-After that, we manually refine $72,409$ image labels, which constitute a clean sub-dataset.
-All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.
+We manually refine $72,409$ image labels, which constitute a clean sub-dataset.
+All the data are then used to train CNNs, while the major challenge is to identify and correct wrong labels during the training process.
 
 To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the true labels and uses them to supervise the training of the network.
-Our work is inspired by~\cite{sukhbaatar2014learning}, which modifies a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
-However,~\cite{sukhbaatar2014learning} assumes noisy labels are conditionally independent with input images given clean labels.
-By examining our collected dataset, we find that this assumption is too strong to fit the real-world data well.
+Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
+However,~\cite{sukhbaatar2014learning} assumed noisy labels were conditionally independent with input images given clean labels.
+By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
 For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
@@
 
-The proposed probabilistic model builds the relations among the image, noisy label, ground truth label, and the noise type, where the latter two are treated as latent variables.
+The proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
 We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
@@
 \label{sec:related_work}
-For most of the related works including effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2013classification} for a comprehensive review.
+For most of the related works including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2013classification} for a comprehensive review.
 
@@
 To better handle label noise, some approaches rely on training classifiers with label noise-robust algorithms~\cite{beigman2009learning,manwani2013noise}.
-However,~\cite{bartlett2006convexity} proves that most of the loss functions are not completely robust to label noise.
-Experiments in~\cite{teng2001comparison} show that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
+However, Bartlett \etal~\cite{bartlett2006convexity} proved that most of the loss functions are not completely robust to label noise.
+Experiments in~\cite{teng2001comparison} showed that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
 These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2013classification}.
-On the other hand, some label noise cleansing methods are proposed to remove or correct mislabeled instances~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
-Thus they may remove too many instances and the overcleansing can reduce the performances of classifiers~\cite{matic1992computer}.
+On the other hand, some label noise cleansing methods were proposed to remove or correct mislabeled instances~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches were difficult in distinguishing informative hard examples from harmful mislabeled ones.
+Thus they might remove too many instances and the overcleansing could reduce the performances of classifiers~\cite{matic1992computer}.
 
-{\bf Semi-supervised learning:} Apart from directly learning with label noise, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data.
-Label Propagation method~\cite{zhu2002learning} explicitly uses ground truths of well labeled data to classify unlabeled samples.
-However, it suffers from computing pairwise distance, which has quadratic complexity with the number of samples thus cannot be applied on large-scale datasets.
-Chen \etal~\cite{chen2013fast} tackled this problem in the scenario of image tagging by a co-regularized duo classifier that can efficiently use both the image and incomplete tags.
+{\bf Semi-supervised learning:} Apart from direct learning with label noise, some semi-supervised learning algorithms were developed to utilize weakly labeled or even unlabeled data.
+The Label Propagation method~\cite{zhu2002learning} explicitly used ground truths of well labeled data to classify unlabeled samples.
+However, it suffered from computing pairwise distance, which has quadratic complexity with the number of samples thus cannot be applied on large-scale datasets.
 Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
-But they need extra information about whether a pair of unlabeled images belong to the same class, which cannot be obtained in our problem.
+But they needed extra information about whether a pair of unlabeled images belong to the same class, which cannot be obtained in our problem.
 
@@
 
-{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.~\cite{mnih2012learning} builds a simple noise model for aerial images but only considers binary classification.~\cite{larsen1998design} assumes label noise is independent from the true class label which is a simple and special case.~\cite{sukhbaatar2014learning} generalizes from them by considering multi-class classification and modeling class dependent noise, but they assume the noise is conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
+{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.
+Mnih and Hinton~\cite{mnih2012learning} built a simple noise model for aerial images but only considered binary classification.
+Larsen \etal~\cite{larsen1998design} assumed label noises are independent from true class labels which is a simple and special case.
+Sukhbaatar \etal~\cite{sukhbaatar2014learning} generalized from them by considering multi-class classification and modeling class dependent noise, but they assumed the noise was conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
 Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent noise but also input dependent noise.
@@
 We target on learning a classifier from a set of images with noisy labels.
-To be specific, we have a noisy labeled dataset $\mathcal{D}_n=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with the $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
+To be specific, we have a noisy labeled dataset $\mathcal{D}_{\eta}=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
 We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
@@
 
-On the other hand, the label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
+The label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
 \begin{enumerate}
@@
 \end{equation}
-where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are one), and $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denoting the confusion probability between class $i$ and $j$.
+where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are ones), $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denotes the confusion probability between classes $i$ and $j$.
 Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
@@
 While the class label probability distribution $p(\vec{y} | \vec{x})$ is comprehensible, the semantic meaning of $p(\vec{z} | \vec{x})$ needs extra clarification: it represents how confusing the image content is.
-Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes, \etc.
-We show some examples in Figure~\ref{fig:compare_noise_level}.
+Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes.
+Some examples are shown in Figure~\ref{fig:compare_noise_level}.
 
@@
 
-To illustrate the relations between noisy label and ground truth, we can derive their conditional probability from Eq~\ref{eq:joint_distribution}
+To illustrate the relations between noisy and true labels, we derive their conditional probability from Eq~\ref{eq:joint_distribution}
 \begin{equation}
@@
 We exploit two CNNs to model $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ separately.
-Denote the parameter set of each deep model by $\theta_1$ and $\theta_2$.
+Denote the parameter set of each CNN by $\theta_1$ and $\theta_2$.
 Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
-The Expectation-Maximization algorithm is used to iteratively solve this problem.
+The EM algorithm is used to iteratively solve this problem.
 
-For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood
+For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood,
 \begin{equation}
@@
 \textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$.
-Therefore, in each iteration $t$, we first compute the posterior of latent variables using current parameters $\theta^{(t)}$:
+Therefore, in each iteration $t$, we first compute the posterior of latent variables using the current parameters $\theta^{(t)}$:
 \begin{multline} \label{eq:posterior}
@@
 
-The M-Step above is equivalent to minimize the cross entropy between the estimated ground truth distribution and the prediction of the classifier.
+The M-Step above is equivalent to minimizing the cross entropy between the estimated ground truth distribution and the prediction of the classifier.
 % subsection learning_the_parameters (end)
 
-\subsection{Estimating the Matrix $\mat{C}$} % (fold)
+\subsection{Estimating Matrix $\mat{C}$} % (fold)
 \label{sub:confusion_estimation}
@@
 For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$.
-To avoid this degeneration, we estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
-As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
+To avoid such degeneration, we estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
+As prior information about $\vec{z}$ is not available, we solve the following optimization problem:
 \begin{equation} \label{eq:opt_all}
@@
 Suppose there exists some $i,j$ such that $0 < \mat{C}^*_{ij} \leq \alpha$.
-Then we conduct following operations.
+Then we conduct the following operations.
 First, we set $\mat{C}^*_{ij}=0$ while adding its original value to other elements in column $j$.
@@
 \begin{proof}
-The first part is straight forward.
+The first part is straightforward.
 For the second part, $\vec{t}^*_i=1$ implies $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} \leq \alpha$.
@@
 \begin{aligned}
-\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{L} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right)\\
-\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{L} \vec{c}_k = 1 \\
-                    & \vec{t} \in \{0,1\}^{L}
+\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{L} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right),\\
+\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{L} \vec{c}_k = 1,\\
+                    & \vec{t} \in \{0,1\}^{L}.
 \end{aligned}
@@
 \begin{equation}
-    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_L)
+    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_L).
 \end{equation}
@@
     &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
-    &\vec{t}^*_i = 1, i = k^*+1,\dots,L
+    &\vec{t}^*_i = 1, i = k^*+1,\dots,L.
 \end{aligned}
@@
 \begin{aligned}
-\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k\\
-\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{k^*} \vec{c}_k = 1
+\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k,\\
+\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{k^*} \vec{c}_k = 1,
 \end{aligned}
@@
 \begin{aligned}
-    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^* \\
-    &\vec{c}^*_i = 0, i = k^*+1,\dots,L
+    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^*,\\
+    &\vec{c}^*_i = 0, i = k^*+1,\dots,L.
 \end{aligned}
@@
 
-After both CNN components are properly pretrained, we can start training the whole network with massive noisy labeled data.
+After both CNN components are properly pretrained, we can start to train the whole network with massive noisy labeled data.
 However, some practical issues need to be further discussed.
@@
 A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than noisy data.
-To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_n$.
+To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_{\eta}$.
 This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.
@@
 After that we manually refine the noisy labels of a small portion of all the images and split them into training ($\mathcal{D}_c$), validation and test sets.
-On the other hand, the remaining samples construct the noisy labeled training dataset ($\mathcal{D}_n$).
-A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with any image in the validation or test set, which ensures the reliability of our test protocol.
-Finally, the size of training datasets are $|\mathcal{D}_c| = 47,570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have $14,313$ and $10,526$ images, respectively.
+On the other hand, the remaining samples construct the noisy labeled training dataset ($\mathcal{D}_{\eta}$).
+A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ the images that are near duplicate with any image in the validation or test set, which ensures the reliability of our test protocol.
+Finally, the size of training datasets are $|\mathcal{D}_c| = 47,570$ and $|\mathcal{D}_{\eta}| = 10^6$, while validation and test set have $14,313$ and $10,526$ images, respectively.
 
@@
 On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
-Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
+Meanwhile, the noisy labels of $\mathcal{D}_{\eta}$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
 
@@
 2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained & 72.63\% \\
-3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random & 74.03\% \\
-4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained & 75.13\% \\
-5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 & 75.30\% \\
-6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 & 73.04\% \\
-7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & 76.22\% \\
-8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & \textbf{78.24\%} \\
+3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & random & 74.03\% \\
+4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & ImaegNet pretrained & 75.13\% \\
+5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & model \#2 & 75.30\% \\
+6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as unlabeled & model \#2 & 73.04\% \\
+7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & 76.22\% \\
+8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & \textbf{78.24\%} \\
 \hline
@@
 
-It should be noticed that~\cite{sukhbaatar2014learning} assumes distribution of noisy labels only depends on classes, while we assume it also depends on image content.
+It should be noticed that~\cite{sukhbaatar2014learning} assumed the distribution of noisy labels only depends on classes, while we assume it also depends on image content.
 This kind of synthetic label noise exactly matches their assumption but is unfavored to our model.
@@
 \label{sec:acknowledgements}
-This work is supported by the National Basic Research Program of China (973 program No. 2014CB340505).
+This work is supported by the General Research Fund sponsored by the Research Grants Council of Hong Kong (Project Nos.
+CUHK14206114 and CUHK14207814) and the National Basic Research Program of China (973 program No.
+2014CB340505).
 

### 2015-04-09 paper.tex
Fix the bibs

@@
 
-Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, and scene classification~\cite{farabet2013learning}.
+Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
@@
 Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people initialize parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2013learning,azizpour2014generic,donahue2013decaf}.
+Based on the observation of transferability of deep neural networks, people initialize parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2014learning,azizpour2014generic,donahue2013decaf}.
 Such methods may better avoid overfitting and utilize the relationships between the two datasets.
@@
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
-It shows that images tend to be mislabeled may share similar visual patterns.
-This is because different sellers have their own bias on different categories, thus they may provide wrong keywords for many similar clothes.
-Based on these observations, we introduce two types of label noise:
+This is because different sellers have their own bias on different categories, thus they may provide wrong keywords for similar clothes.
+We can capture these visual patterns to estimate how likely an image is mislabeled.
+Based on these observations, we further introduce two types of label noise:
 \begin{itemize}
@@
 \end{center}
-\caption{Images tend to be mislabeled often share similar visual patterns.}
+\caption{Mislabeled images often share similar visual patterns.}
 \label{fig:noise_cluster}
@@
 \label{sec:related_work}
-For most of the related works including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2013classification} for a comprehensive review.
+For most of the related works including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2014classification} for a comprehensive review.
 
@@
 Experiments in~\cite{teng2001comparison} showed that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
-These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2013classification}.
+These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2014classification}.
 On the other hand, some label noise cleansing methods were proposed to remove or correct mislabeled instances~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches were difficult in distinguishing informative hard examples from harmful mislabeled ones.
@@
 However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic,donahue2013decaf}.
+Researchers proposed to conquer this problem by first initializing CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2014learning, azizpour2014generic,donahue2013decaf}.
 Nevertheless, this transfer learning scheme could be suboptimal when the two tasks are just loosely related.
@@
 The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
-It shows that the intuitive observation --- images tend to be mislabeled often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to help handle noisy labels.
+It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to help handle noisy labels.
 

### 2015-04-10 ext.tex
Add extended abstract

--- 2015-04-09 paper.tex
@@
-%!TEX program = xelatex
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% Use class option [extendedabs] to prepare the 1-page extended abstract.
+\documentclass[extendedabs]{bmvc2k}
+\usepackage[colorlinks = true,
+            linkcolor = blue,
+            urlcolor  = blue,
+            citecolor = blue,
+            anchorcolor = blue]{hyperref}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{tabularx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{algorithm2e}
-\usepackage{authblk}
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-\usepackage{fontspec}
-
-\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{407} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\def\vec{\mathbf}
-\def\mat{\mathbf}
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}{Proposition}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+% Document starts here
 \begin{document}
 
-\RestyleAlgo{boxruled}
-
-%%%%%%%%% TITLE
 \title{Learning From Massive Noisy Labeled Data for Image Classification}
-
-\author[1]{Tong Xiao}
-\author[2]{Tian Xia}
-\author[2]{Yi Yang}
-\author[2]{Chang Huang}
-\author[1]{Xiaogang Wang}
-
-\affil[1]{The Chinese University of Hong Kong}
-\affil[2]{Baidu Research}
-
-\renewcommand\Authands{, and }
-
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
+\addauthor{
+Tong Xiao$^1$, 
+Tian Xia$^2$,
+Yi Yang$^2$,
+Chang Huang$^2$,
+and Xiaogang Wang$^1$
+}{}{1}
+\addinstitution{
+$^1$The Chinese University of Hong Kong.
+$^2$Baidu Research.
+}
 
 \maketitle
-%\thispagestyle{empty}
+\let\thefootnote\relax\footnote{This is an extended abstract. The full paper is available at the \href{http://www.cv-foundation.org/openaccess/CVPR2015.py}{Computer Vision Foundation webpage}. }
+\vspace{-0.2in}
 
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems.
-However, obtaining a massive amount of well labeled data is usually very expensive and time consuming.
-In this paper, we introduce a general framework to train CNNs with only a limited number of clean labels and millions of easily obtained noisy labels.
-We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system.
-To demonstrate the effectiveness of our approach, we collect a large-scale clothing classification dataset with both noisy and clean labels.
-Experiments on this dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction} % (fold)
-\label{sec:introduction}
-
-Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
-While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
+\noindent
+Deep learning with large-scale supervised training data has shown very impressive improvement on image classification challenge~\cite{krizhevsky2012imagenet}.
+However, it requires reliable annotations from millions of images which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
 Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.
 
-One possible solution is to automatically collect large amount of annotations from the Internet web images~\cite{gong2014multiview} (i.e.
-extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
-Unfortunately, these labels are extremely unreliable due to various types of noise (i.e.
-labeling mistakes from annotators or computing errors from extraction algorithms).
-Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
-Various label noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise~\cite{bartlett2006convexity,teng2001comparison}.
-Other data cleansing algorithms are proposed~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches are difficult in distinguishing informative hard examples from harmful mislabeled ones.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.95\linewidth]{figure/overview.pdf}
-\end{center}
-\caption{Overview of our approach.
-Labels of web images often suffer from different types of noise.
-A label noise model is proposed to detect and correct the wrong labels.
-The corrected labels are used to train underlying CNNs.}
-\label{fig:overview}
-\end{figure}
+One possible solution is to automatically collect annotations from the Internet web images (\emph{i.e.} extracting tags from the surrounding texts) and directly use them as ground truth to train deep models.
+Unfortunately, these labels are extremely unreliable due to various types of noise (\emph{e.g.} labeling mistakes from annotators or computing errors from extraction algorithms).
+Many works have shown that noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{nettleton2010study}.
+Various label noise-robust algorithms~\cite{manwani2013noise} and data cleansing algorithms~\cite{brodley2011identifying} are developed but experiments show that performances are still affected by label noise~\cite{bartlett2006convexity}.
 
 Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels.
-Based on the observation of transferability of deep neural networks, people initialize parameters with a model pretrained on a larger yet related dataset~\cite{krizhevsky2012imagenet}, and then finetune on the smaller dataset of specific tasks~\cite{oquab2014learning,azizpour2014generic,donahue2013decaf}.
-Such methods may better avoid overfitting and utilize the relationships between the two datasets.
-However, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on clean labels.
-Other approaches address the problem as semi-supervised learning where noisy labels are discarded~\cite{zhu2002learning}.
-These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
-Therefore, it is inevitable to develop a better way of using huge amount of noisy labeled data.
+Semi-supervised learning methods~\cite{lee2013pseudo} can also be employed by simply discarding all the noisy labels.
+Researchers have also studied the transferability of Convolutional Neural Networks (CNNs) by finetuning an ImageNet pretrained model on smaller datasets of specific tasks~\cite{oquab2014learning}.
+However, these methods cannot fully utilize the massive noisy labeled data, which may lead to suboptimal results.
 
@@
 Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
-However,~\cite{sukhbaatar2014learning} assumed noisy labels were conditionally independent with input images given clean labels.
-By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
+However,~\cite{sukhbaatar2014learning} assumed noisy labels are conditionally independent with input images given clean labels.
+By examining the collected dataset, we find that this assumption is too strong to fit real-world data well.
 For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
-This is because different sellers have their own bias on different categories, thus they may provide wrong keywords for similar clothes.
+Since different sellers have their own bias on different categories, they may provide wrong keywords for similar clothes.
 We can capture these visual patterns to estimate how likely an image is mislabeled.
@@
 \begin{itemize}
-\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Figure~\ref{fig:overview}).
+\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\emph{e.g}, the samples with ``?'' in Figure~\ref{fig:overview}).
 \item \textbf{Pure random noise} makes the noisy label totally wrong.
-It is often caused by either the mismatch between an image and its surrounding text, or false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
+It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\emph{e.g.}, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
 \end{itemize}
 
-The proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
+Our proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
 We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
-Experiments on the collected dataset show that our model can better detect and correct the wrong labels.
-
-Our contribution comes from three aspects.
-First, we study the cause of noisy labels in real-world data and describe it with a novel probabilistic model.
-Second, we integrate the model into a deep learning framework to help detect and correct wrong labels.
-We study different training strategies to make the CNNs learn from better supervisions.
-Finally, we collect a large-scale clothing dataset with both noisy and clean labels, which will be released for academic use.
+Experiments on the collected dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
 
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
+\includegraphics[width=0.8\linewidth]{figure/overview.pdf}
+\end{center}
+\caption{Overview of our approach.
+Labels of web images often suffer from different types of noise.
+A label noise model is proposed to detect and correct the wrong labels.
+The corrected labels are used to train underlying CNNs.}
+\label{fig:overview}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.8\linewidth]{figure/noise_cluster.pdf}
 \end{center}
@@
 \end{figure}
-% section introduction (end)
 
-\section{Related Work} % (fold)
-\label{sec:related_work}
-For most of the related works including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2014classification} for a comprehensive review.
-
-{\bf Direct learning with noisy labels:} Many works have shown that label noise can adversely impact the classification accuracy of induced classifiers~\cite{zhu2004class}.
-To better handle label noise, some approaches rely on training classifiers with label noise-robust algorithms~\cite{beigman2009learning,manwani2013noise}.
-However, Bartlett \etal~\cite{bartlett2006convexity} proved that most of the loss functions are not completely robust to label noise.
-Experiments in~\cite{teng2001comparison} showed that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
-These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2014classification}.
-On the other hand, some label noise cleansing methods were proposed to remove or correct mislabeled instances~\cite{barandela2000decontamination,brodley2011identifying,miranda2009use}, but these approaches were difficult in distinguishing informative hard examples from harmful mislabeled ones.
-Thus they might remove too many instances and the overcleansing could reduce the performances of classifiers~\cite{matic1992computer}.
-
-{\bf Semi-supervised learning:} Apart from direct learning with label noise, some semi-supervised learning algorithms were developed to utilize weakly labeled or even unlabeled data.
-The Label Propagation method~\cite{zhu2002learning} explicitly used ground truths of well labeled data to classify unlabeled samples.
-However, it suffered from computing pairwise distance, which has quadratic complexity with the number of samples thus cannot be applied on large-scale datasets.
-Weston \etal~\cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features.
-But they needed extra information about whether a pair of unlabeled images belong to the same class, which cannot be obtained in our problem.
-
-{\bf Transfer learning:} The success of CNNs lies in their capability of learning rich and hierarchical image features.
-However, the model parameters cannot be properly learned when training data is not enough.
-Researchers proposed to conquer this problem by first initializing CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning it on the smaller dataset of specific task~\cite{krizhevsky2012imagenet, oquab2014learning, azizpour2014generic,donahue2013decaf}.
-Nevertheless, this transfer learning scheme could be suboptimal when the two tasks are just loosely related.
-In our case of clothing classification, we find that training a CNN from scratch with limited clean labels and massive noisy labels is better than finetuning it only on the clean labels.
-
-{\bf Noise modeling with deep learning:} Various methods have been proposed to handle label noise in different problem settings, but there are very few works about deep learning from noisy labels~\cite{mnih2012learning, larsen1998design, sukhbaatar2014learning}.
-Mnih and Hinton~\cite{mnih2012learning} built a simple noise model for aerial images but only considered binary classification.
-Larsen \etal~\cite{larsen1998design} assumed label noises are independent from true class labels which is a simple and special case.
-Sukhbaatar \etal~\cite{sukhbaatar2014learning} generalized from them by considering multi-class classification and modeling class dependent noise, but they assumed the noise was conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
-Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent noise but also input dependent noise.
-% section related_work (end)
-
-\section{Label Noise Model} % (fold)
-\label{sec:label_noise_model}
-We target on learning a classifier from a set of images with noisy labels.
-To be specific, we have a noisy labeled dataset $\mathcal{D}_{\eta}=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
-We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\linewidth]{figure/pgm.pdf}
-\end{center}
-\caption{Probabilistic graphical model of label noise}
-\label{fig:noise_pgm}
-\end{figure}
-
-Despite the observed image $\vec{x}$ and the noisy label $\tilde{\vec{y}}$, we exploit two discrete latent variables --- $\vec{y}$ and $\vec{z}$ --- to represent the true label and the label noise type, respectively.
-Both $\tilde{\vec{y}}$ and $\vec{y}$ are $L$-dimensional binary random variables in 1-of-$L$ fashion, \ie, only one element is equal to 1 while others are all 0.
-
-The label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
-\begin{enumerate}
-    \item The label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
-    \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
-    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are confusing with $\vec{y}$
-\end{enumerate}
-
-Following this assignment rule, we define the conditional probability of the noisy label as
-\begin{equation} \label{eq:likelihood}
-    p(\tilde{\vec{y}}|\vec{y},\vec{z}) = \begin{cases}
-        \tilde{\vec{y}}^{T}\mat{I}\vec{y} & \text{if } \vec{z}_1 = 1 \\
-        \frac{1}{L-1}\tilde{\vec{y}}^{T}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
-        \tilde{\vec{y}}^{T}\mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
-    \end{cases}
-\end{equation}
-where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are ones), $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denotes the confusion probability between classes $i$ and $j$.
-Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
-\begin{equation} \label{eq:joint_distribution}
-  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x})
-\end{equation}
-
-While the class label probability distribution $p(\vec{y} | \vec{x})$ is comprehensible, the semantic meaning of $p(\vec{z} | \vec{x})$ needs extra clarification: it represents how confusing the image content is.
-Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes.
-Some examples are shown in Figure~\ref{fig:compare_noise_level}.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_level.pdf}
-\end{center}
-\caption{Predicting noise types of four different ``T-shirt'' images.
-The top two can be recognized with little ambiguity, while the bottom two are easily confusing with the class ``Chiffon''.
-Image content can affect the possibility of it to be mislabeled.}
-\label{fig:compare_noise_level}
-\end{figure}
-
-To illustrate the relations between noisy and true labels, we derive their conditional probability from Eq~\ref{eq:joint_distribution}
-\begin{equation}
-    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x})
-\end{equation}
-which can be interpreted as a mixture model.
-Given an input image $\vec{x}$, the conditional probability $p(\vec{z} | \vec{x})$ can be seen as the prior of each mixture component.
-This makes a key difference between our work and~\cite{sukhbaatar2014learning}, where they assume $\tilde{\vec{y}}$ is conditionally independent with $\vec{x}$ if $\vec{y}$ is given.
-All the images share a same noise model in~\cite{sukhbaatar2014learning}, while in our approach each data sample has its own.
-
-\subsection{Learning the Parameters} % (fold)
-\label{sub:learning_the_parameters}
-We exploit two CNNs to model $p(\vec{y} | \vec{x})$ and $p(\vec{z} | \vec{x})$ separately.
-Denote the parameter set of each CNN by $\theta_1$ and $\theta_2$.
-Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
-The EM algorithm is used to iteratively solve this problem.
-
-For any probability distribution $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})$, we can derive a lower bound of the incomplete log-likelihood,
-\begin{equation}
-\begin{aligned}
-    \log p(\tilde{\vec{y}} | \vec{x}; \theta) &= \log \sum_{\vec{y},\vec{z}} p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
-    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}
-\end{aligned}
-\end{equation}
-\textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$.
-Therefore, in each iteration $t$, we first compute the posterior of latent variables using the current parameters $\theta^{(t)}$:
-\begin{multline} \label{eq:posterior}
-    p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
-    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
-\end{multline}
-Then the expected complete log-likelihood can be written as
-\begin{equation}
-    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)
-\end{equation}
-\textbf{M-Step} We exploit two CNNs to model the probability $p(\vec{y}|\vec{x};\theta_1)$ and $p(\vec{z}|\vec{x};\theta_2)$, respectively.
-Thus the gradient of $Q$ \wrt $\theta$ can be decoupled into two parts:
-\begin{multline} \label{eq:gradient}
-    \frac{\partial Q}{\partial \theta} = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta} \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
-    = \sum_{\vec{y}} p(\vec{y} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_1} \log p(\vec{y}|\vec{x};\theta_1) + \\
-      \sum_{\vec{z}} p(\vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2)
-\end{multline}
-
-The M-Step above is equivalent to minimizing the cross entropy between the estimated ground truth distribution and the prediction of the classifier.
-% subsection learning_the_parameters (end)
-
-\subsection{Estimating Matrix $\mat{C}$} % (fold)
-\label{sub:confusion_estimation}
-Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process.
-Because without other regularizations, learning all the three parts in Eq~\eqref{eq:joint_distribution} could lead to trivial solutions.
-For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$.
-To avoid such degeneration, we estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy labels.
-As prior information about $\vec{z}$ is not available, we solve the following optimization problem:
-\begin{equation} \label{eq:opt_all}
-    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)})
-\end{equation}
-Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal.
-So that we discard those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
-\begin{equation}
-\begin{aligned}
-\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
-\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L \\
-                    & \vec{t} \in \{0,1\}^{N'}
-\end{aligned}
-\end{equation}
-where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples.
-The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.
-
-Next, we will show that the problem can be solved by a simple yet efficient algorithm in $O(N'+L^2)$ time complexity. Denote the optimal solution by $\mat{C}^*$ and $\vec{t}^*$
-\begin{theorem}
-$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,L\}$
-\end{theorem}
-\begin{proof}
-Suppose there exists some $i,j$ such that $0 < \mat{C}^*_{ij} \leq \alpha$.
-Then we conduct the following operations.
-First, we set $\mat{C}^*_{ij}=0$ while adding its original value to other elements in column $j$.
-Second, for all the samples $n$ where $\tilde{\vec{y}}^{(n)}_i=1$ and $\vec{y}^{(n)}_j=1$, we set $\vec{t}_n$ to 1.
-The resulting $E$ will get increased, which leads to a contradiction.
-\end{proof}
-\begin{theorem}
-$(\tilde{\vec{y}}^{(i)},\vec{y}^{(i)})=(\tilde{\vec{y}}^{(j)},\vec{y}^{(j)}) \Rightarrow \vec{t}^*_i=\vec{t}^*_j, \forall i,j \in \{1,\dots,N'\}$
-\end{theorem}
-\begin{proof}
-Suppose $\tilde{\vec{y}}^{(i)}_k=\tilde{\vec{y}}^{(j)}_k=1$ and $\vec{y}^{(i)}_l=\vec{y}^{(j)}_l=1$ but $\vec{t}^*_i \neq \vec{t}^*_j$.
-From Theorem 1 we know that elements in $\mat{C}^*$ is either 0 or greater than $\alpha$.
-If $\mat{C}^*_{kl}=0$, we can set $\vec{t}^*_i=\vec{t}^*_j=1$, otherwise we can set $\vec{t}^*_i=\vec{t}^*_j=0$.
-In either case the resulting $E$ will get increased, which leads to a contradiction.
-\end{proof}
-\begin{theorem}
-$\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} > \alpha \Leftrightarrow \vec{t}^*_i=0$ and $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0 \Leftrightarrow \vec{t}^*_i=1, \forall i \in \{1,\dots,N'\}$
-\end{theorem}
-\begin{proof}
-The first part is straightforward.
-For the second part, $\vec{t}^*_i=1$ implies $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} \leq \alpha$.
-By using Theorem 1 we know that $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0$.
-\end{proof}
-
-Notice that if the true label is class $i$ while the noisy label is class $j$, then it can only affect the value of $\mat{C}_{ij}$.
-Thus each column of $\mat{C}$ can be optimized separately.
-Theorem 1 further shows that samples with same pair of $(\tilde{\vec{y}},\vec{y})$ share a same noise type.
-Then what really matters is the frequencies of all the $L\times L$ pairs of $(\tilde{\vec{y}},\vec{y})$.
-Considering a particular column $\vec{c}$, suppose there are $M$ samples affecting this column.
-We can count the frequencies of noisy label class 1 to $L$ as $m_1,\dots,m_L$ and might as well assume $m_1\geq m_2\geq \cdots \geq m_L$.
-The problem is then converted to
-\begin{equation}
-\begin{aligned}
-\max_{\vec{c},\vec{t}} \quad & E=\sum_{k=1}^{L} m_k \left(\log \alpha^{\vec{t}_k} + \log \mat{c}_k^{1-\vec{t}_k}\right),\\
-\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{L} \vec{c}_k = 1,\\
-                    & \vec{t} \in \{0,1\}^{L}.
-\end{aligned}
-\end{equation}
-
-Due to the rearrangement inequality, we can prove that in the optimal solution,
-\begin{equation}
-    \max(\alpha,\vec{c}^*_1) \geq \max(\alpha,\vec{c}^*_2) \geq \cdots \geq \max(\alpha,\vec{c}^*_L).
-\end{equation}
-Then by using Theorem 3, there must exist a $k^* \in \{1,\dots,L\}$ such that
-\begin{equation} \label{eq:opt_t}
-\begin{aligned}
-    &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
-    &\vec{t}^*_i = 1, i = k^*+1,\dots,L.
-\end{aligned}
-\end{equation}
-This also implies that only the first $k^*$ elements of $\vec{c}^*$ have nonzero values (greater than $\alpha$ actually).
-Furthermore, if $k^*$ is known, finding the optimal $\vec{c}^*$ is to solve the following problem:
-\begin{equation}
-\begin{aligned}
-\max_{\vec{c}} \quad & E=\sum_{k=1}^{k^*} m_k \log \mat{c}_k,\\
-\text{subject to} \quad & \vec{c} \in [0,1]^L, \sum_{k=1}^{k^*} \vec{c}_k = 1,
-\end{aligned}
-\end{equation}
-whose solution is
-\begin{equation} \label{eq:opt_c}
-\begin{aligned}
-    &\vec{c}^*_i = \frac{m_i}{\sum_{k=1}^{k^*}{m_k}}, i = 1,\dots,k^*,\\
-    &\vec{c}^*_i = 0, i = k^*+1,\dots,L.
-\end{aligned}
-\end{equation}
-
-The above analysis leads to a simple algorithm.
-We enumerate $k^*$ from 1 to $L$.
-For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively.
-Then we evaluate the objective function $E$ and record the best solution.
-
-% subsection confusion_estimation (end)
-
-% section label_noise_model (end)
-
-\section{Deep Learning from Noisy Labels} % (fold)
-\label{sec:deep_learning_from_noisy_labels}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
-\end{center}
-\caption{System diagram of our method.
-Two CNNs are used to predict the class label $p(\vec{y}|\vec{x})$ and the noise type $p(\vec{z}|\vec{x})$, respectively.
-The label noise model layer infers the true label according to the predictions and the noisy label, which is then used to supervise the training of CNNs.
-Data with clean labels are also mixed in to prevent the models from drifting away.}
-\label{fig:framework}
-\end{figure*}
-
-We integrate the proposed label noise model into a deep learning framework.
-As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
-Moreover, we append a label noise model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
-Stochastic Gradient Ascent with backpropagation technique is used to approximately optimize the whole network.
-In each forward pass, the label noise model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
-While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.
-
-% The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.
-
-% \begin{algorithm}
-%     \SetKwData{Sum}{sum}
-%     \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
-%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-
-%     \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
-%     \Input{Object class scores matrix $Y$ of size $N \times L$}
-%     \Input{Noise type scores matrix $Z$ of size $N \times 3$}
-%     \Output{Posterior probability matrix $P$ of size $L \times 3$}
-%     \BlankLine
-
-%     $P_y \leftarrow$ \Softmax{$Y$}\;
-%     $P_z \leftarrow$ \Softmax{$Z$}\;
-%     \BlankLine
-
-%     \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
-%     \BlankLine
-
-%     \For {$i \leftarrow 1$ \KwTo $N$} {
-%         \Sum $\leftarrow 0$\;
-%         \For {$j \leftarrow 1$ \KwTo $L$} {
-%             \For {$k \leftarrow 1$ \KwTo $3$} {
-%                 $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
-%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-%             }
-%         }
-%         $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
-%     }
-
-%     \caption{Forward pass}
-%     \label{alg:forward}
-% \end{algorithm}
-% \begin{algorithm}
-%     \SetKwData{Sum}{sum}
-%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-
-%     \Input{Object class scores matrix $Y$ of size $N \times L$}
-%     \Input{Posterior probability matrix $P$ of size $L \times 3$}
-%     \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
-%     \BlankLine
-
-%     \For {$i \leftarrow 1$ \KwTo $N$} {
-%         \For {$j \leftarrow 1$ \KwTo $L$} {
-%             \Sum $\leftarrow 0$\;
-%             \For {$k \leftarrow 1$ \KwTo $3$} {
-%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-%             }
-%             $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
-%             $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
-%         }
-%     }
-
-%     \caption{Backward pass for computing gradient w.r.t. object class scores}
-%     \label{alg:backward}
-% \end{algorithm}
-
-Directly training the whole network with random initialization is impractical, because the posterior computation could be totally wrong.
-Therefore, we need to pretrain each CNN component with strongly supervised data.
-Images and their ground truth labels in the dataset $\mathcal{D}_c$ are used to train the CNN that predicts $p(\vec{y}|\vec{x})$.
-On the other hand, the optimal solutions of $\vec{z}^{(1)},\cdots,\vec{z}^{(N)}$ in Eq~\eqref{eq:opt_all} are used to train the CNN that predicts $p(\vec{z}|\vec{x})$.
-
-After both CNN components are properly pretrained, we can start to train the whole network with massive noisy labeled data.
-However, some practical issues need to be further discussed.
-First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
-Therefore, we need to mix the data with clean labels into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
-Then each CNN receives two kinds of gradients, one is from the clean labels and the other is from the noisy labels.
-We denote them by $\Delta_c$ and $\Delta_n$, respectively.
-A potential problem is that $|\Delta_c| \ll |\Delta_n|$, because clean data is much less than noisy data.
-To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_{\eta}$.
-This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.
-
-Our proposed method has the ability to figure out the true label given the image and its noisy label.
-From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how easily for the image to be mislabeled.
-Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model.
-On the other hand, the second kind of information correlates the image content with the label noise, which can help distinguish between hard samples and mislabeled ones.
-% section deep_learning_from_noisy_labels (end)
-
-\section{Experiments} % (fold)
-\label{sec:experiments}
-
-\subsection{Dataset} % (fold)
-\label{sub:dataset}
-Since there is no publicly available dataset that has both clean and noisy labels, to test our method under real-world scenario, we build a large-scale clothing dataset by crawling images from several online shopping websites.
-More than a million images are collected together with their surrounding texts provided by the sellers.
-These surrounding texts usually contain rich information about the products, which can be further converted to visual tags.
-Specific to our task of clothing classification, we define $14$ class labels: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Hoodie, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.
-We assign an image a noisy label if we find its surrounding text contains only the keywords of that label, otherwise we discard the image to reduce ambiguity.
-
-After that we manually refine the noisy labels of a small portion of all the images and split them into training ($\mathcal{D}_c$), validation and test sets.
-On the other hand, the remaining samples construct the noisy labeled training dataset ($\mathcal{D}_{\eta}$).
-A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ the images that are near duplicate with any image in the validation or test set, which ensures the reliability of our test protocol.
-Finally, the size of training datasets are $|\mathcal{D}_c| = 47,570$ and $|\mathcal{D}_{\eta}| = 10^6$, while validation and test set have $14,313$ and $10,526$ images, respectively.
-
-The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}.
-We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater), which means that the noisy labels are not so reliable.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{figure/cm_strong_weak_labels.pdf}
-\end{center}
-\caption{Confusion matrix between clean and noisy labels.
-We hide extremely small grid numbers for better demonstration.
-Frequency of each true label is listed at the top of each column.
-The overall accuracy is $61.54\%$, which indicates that the noisy labels are not reliable.}
-\label{fig:cm_strong_weak}
-\end{figure}
-% subsection dataset (end)
-
-\subsection{Evaluation on the Collected Dataset} % (fold)
-\label{sub:evaluation}
-We validate our method through a series of experiments conducted on the collected dataset.
-Our implementation is based on Caffe~\cite{jia2014caffe}, and the \texttt{bvlc\_reference\_caffenet}\footnote{\url{http://caffe.berkeleyvision.org/model_zoo.html}} is chosen as the baseline model, which approximates AlexNet~\cite{krizhevsky2012imagenet}.
-Besides, we reimplement two other approaches.
-One is a semi-supervised learning method called Pseudo-Label~\cite{lee2013pseudo}, which exploits classifier's prediction as ground truth for unlabeled data.
-The other one is the Bottom-Up method introduced in~\cite{sukhbaatar2014learning}, where the relation between noisy labels and clean labels are built by a confusion matrix $Q$.
-In the experiments, we directly use the true $Q$ as shown in Figure~\ref{fig:cm_strong_weak} instead of estimating its values.
-
-We list all the experiment settings in Table~\ref{tab:exp}.
-Different methods require different training data.
-We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions.
-On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
-Meanwhile, the noisy labels of $\mathcal{D}_{\eta}$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
-
-In general, we use a mini-batch size of $256$.
-The learning rate is initialized to be $0.001$ and is divided by $10$ after every $50,000$ iterations.
-We keep training each model until convergence.
-Classification accuracies on the test set are presented in Table~\ref{tab:exp}.
-
-\begin{table*}[t]
-\begin{center}
-\begin{tabular}{c|c|c|c|c}
-\hline
-\# & Method & Training Data & Initialization & Test Accuracy\\
-\hline\hline
-1 & AlexNet & $\mathcal{D}_c$ & random & 64.54\% \\
-2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained & 72.63\% \\
-3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & random & 74.03\% \\
-4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & ImaegNet pretrained & 75.13\% \\
-5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as ground truths & model \#2 & 75.30\% \\
-6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as unlabeled & model \#2 & 73.04\% \\
-7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & 76.22\% \\
-8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & \textbf{78.24\%} \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Experiment results on the collected dataset}
-\label{tab:exp}
-\end{table*}
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{c|c|c}
-% \hline
-% \# & Validation Accuracy & Test Accuracy \\
-% \hline\hline
-% 1 & 64.28\% & 64.54\% \\
-% \hline
-% 2 & 72.21\% & 72.63\% \\
-% \hline
-% 3 & 73.76\% & 74.03\% \\
-% \hline
-% 4 & 75.06\% & 75.13\% \\
-% \hline
-% 5 & 75.57\% & 75.30\% \\
-% \hline
-% 6 & 73.10\% & 73.04\% \\
-% \hline
-% 7 & 75.97\% & 76.22\% \\
-% \hline
-% 8 & \textbf{77.65\%} & \textbf{78.24\%} \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Classification accuracies on validation and test set}
-% \label{tab:accuracy}
-% \end{table}
-
-\begin{figure*}
-\begin{center}
-\end{center}
-\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{Examples of handling noisy labels. The information layout in each block is illustrated in the top-left one.}
-\label{fig:model_output}
-\end{figure*}
-
-We first study the effect of transfer learning and massive noisy labeled data.
-From row \#1 we can see that training a CNN from scratch with only small amount of clean data can result in bad performance.
-To deal with this problem, finetuning from an ImageNet pretrained model can significantly improve the accuracy, as shown in row \#2.
-However, by comparing row \#2 and \#3, we find that training with random initialization on additional massive noisy labeled data is better than finetuning only on the clean data, which demonstrates the power of using large-scale yet easily obtained noisy labeled data.
-The accuracy can be further improved if we finetune the model either from an ImageNet pretrained one or model \#2.
-The latter one has slightly better performance thus is used to initialize the remaining methods.
-
-Next, from row \#6 we can see that semi-supervised learning methods may not be a good choice when massive noisy labeled data are available.
-Although model \#6 achieves marginally better result than its base model, it is significantly inferior to model \#5, which indicates that simply discarding all the noisy labels cannot make the full use of these information.
-
-Finally, row \#7 and \#8 show the effect of modeling the label noise.
-Model \#7 is only $0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.9\%$.
-This result does credit to our image dependent label noise model, which fits better to the noisy labeled data crawled from the Internet.
-
-\subsection{Evaluation on Synthetic Dataset} % (fold)
-\label{sub:evaluation_on_synthetic_dataset}
-We also conduct synthetic experiments on CIFAR-10 following the settings of~\cite{sukhbaatar2014learning}.
-We first randomly generate a confusion matrix $Q$ between clean labels and noisy labels, and then corrupt the training labels according to it.
-Based on Caffe's CIFAR10-quick model, we compare~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
-The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c|c|c|c}
-\hline
-Noise Level & Base Model & \cite{sukhbaatar2014learning} & Ours \\
-\hline\hline
-30\% & 65.57\% & 69.73\% & 69.81\% \\
-\hline
-40\% & 62.38\% & 66.66\% & 66.76\% \\
-\hline
-50\% & 57.36\% & 63.39\% & 63.00\% \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Accuracies on CIFAR-10 with synthetic label noise}
-\label{tab:accuracy_synthetic}
-\end{table}
-
-It should be noticed that~\cite{sukhbaatar2014learning} assumed the distribution of noisy labels only depends on classes, while we assume it also depends on image content.
-This kind of synthetic label noise exactly matches their assumption but is unfavored to our model.
-Thus the noise type predictions in our model could be less informative.
-Nevertheless, our model achieves comparable results with~\cite{sukhbaatar2014learning}.
-% subsection evaluation_on_synthetic_dataset (end)
-
-\subsection{Effect of Noise Estimation} % (fold)
-\label{sub:effect_of_noise_estimation}
-In order to understand how does our model handle noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
-We can see that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label, and then use it as supervision instead of the noisy one.
-Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong, our model can still figure out the correct label.
-
-Next we demonstrate the effect of learning to predict the label noise type.
-We estimate $p(\vec{z}_2=1|\vec{x})+p(\vec{z}_3=1|\vec{x})$ on the validation set and sort the images accordingly in descending order.
-Then for each image, we check whether its noisy label mismatches its clean label.
-The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
-It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to help handle noisy labels.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_prediction_rank_precision.pdf}
-\end{center}
-\caption{Rank-precision curve of label noise predictions}
-\label{fig:noise_prediction_rp}
-\end{figure}
-% subsection effect_of_noise_estimation (end) 
-% section experiments (end)
-
-\section{Conclusion} % (fold)
-\label{sec:conclusion}
-In this paper, we raised the problem of training a classifier with limited clean annotations and massive noisy labeled data.
-We proposed a novel probabilistic model to describe how a noisy label is generated.
-Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between the observed image and its noisy label.
-We solved the problem by the EM algorithm and integrated it into a deep learning framework.
-Experiments on a collected large-scale clothing dataset showed that massive noisy label data could benefit the training of deep models, and utilizing our method could further improve the performance.
-% section conclusion (end)
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-This work is supported by the General Research Fund sponsored by the Research Grants Council of Hong Kong (Project Nos.
-CUHK14206114 and CUHK14207814) and the National Basic Research Program of China (973 program No.
-2014CB340505).
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{references}
-}
+\bibliography{extbib}
 

### 2015-04-10 paper.tex
Reduce the paper length

@@
 Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
-While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
+While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain, preventing deep models from being quickly trained on new image recognition problems.
 Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.
 
-One possible solution is to automatically collect large amount of annotations from the Internet web images~\cite{gong2014multiview} (i.e.
-extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
-Unfortunately, these labels are extremely unreliable due to various types of noise (i.e.
-labeling mistakes from annotators or computing errors from extraction algorithms).
+One possible solution is to automatically collect large amount of annotations from the Internet web images~\cite{gong2014multiview} (\ie extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
+Unfortunately, these labels are extremely unreliable due to various types of noise (\eg labeling mistakes from annotators or computing errors from extraction algorithms).
 Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
@@
 \begin{center}
-\includegraphics[width=0.95\linewidth]{figure/overview.pdf}
+\includegraphics[width=0.85\linewidth]{figure/overview.pdf}
 \end{center}
@@
 Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
-However,~\cite{sukhbaatar2014learning} assumed noisy labels were conditionally independent with input images given clean labels.
+However,~\cite{sukhbaatar2014learning} assumed noisy labels are conditionally independent with input images given clean labels.
 By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
@@
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
-This is because different sellers have their own bias on different categories, thus they may provide wrong keywords for similar clothes.
+Since different sellers have their own bias on different categories, they may provide wrong keywords for similar clothes.
 We can capture these visual patterns to estimate how likely an image is mislabeled.
@@
 \item \textbf{Pure random noise} makes the noisy label totally wrong.
-It is often caused by either the mismatch between an image and its surrounding text, or false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
+It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
 \end{itemize}
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
+\includegraphics[width=0.9\linewidth]{figure/noise_cluster.pdf}
 \end{center}
@@
 Two CNNs are used to predict the class label $p(\vec{y}|\vec{x})$ and the noise type $p(\vec{z}|\vec{x})$, respectively.
-The label noise model layer infers the true label according to the predictions and the noisy label, which is then used to supervise the training of CNNs.
+The label noise model layer uses both these predictions and the given noisy label to estimate a posterior distribution of the true label, which is then used to supervise the training of CNNs.
 Data with clean labels are also mixed in to prevent the models from drifting away.}
@@
 \begin{center}
-\end{center}
 \includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
@@
 \label{fig:model_output}
+\end{center}
 \end{figure*}

### 2015-04-10 paper.tex
Polish the paper again

@@
 
-Deep learning with a massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
+Deep learning from large-scale supervised training dataset has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain, preventing deep models from being quickly trained on new image recognition problems.
@@
 Sukhbaatar \etal~\cite{sukhbaatar2014learning} generalized from them by considering multi-class classification and modeling class dependent noise, but they assumed the noise was conditionally independent with the image content, ignoring the hardness of labeling images of different confusing levels.
-Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent noise but also input dependent noise.
+Our work can be viewed as a generalization of~\cite{sukhbaatar2014learning,natarajan2013learning} and our model is flexible enough to not only class dependent but also image dependent noise.
 % section related_work (end)
@@
 Denote the parameter set of each CNN by $\theta_1$ and $\theta_2$.
-Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximize the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
+Our goal is to find the optimal $\theta = \theta_1 \cup \theta_2$ that maximizes the incomplete log-likelihood $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$.
 The EM algorithm is used to iteratively solve this problem.
@@
 After both CNN components are properly pretrained, we can start to train the whole network with massive noisy labeled data.
-However, some practical issues need to be further discussed.
+However, some practical issues need further discussion.
 First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
@@
 To deal with this problem, we bootstrap the clean data $\mathcal{D}_c$ to half amount of the noisy data $\mathcal{D}_{\eta}$.
-This upsampling process brings another advantage --- the gradients we calculated in each mini-batch are much more stable.
+In our experiments, we find that the performance of the classifier drops significantly without upsampling, but it is not sensitive with the upsampling ratio as long as the number of clean and noisy samples are in the same order.
 
 Our proposed method has the ability to figure out the true label given the image and its noisy label.
-From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how easily for the image to be mislabeled.
-Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model.
+From the perspective of information, our model predicts from two kinds of clues: what are the true labels for other similar images; and how likely the image is mislabeled.
+The Label Propagation method~\cite{zhu2002learning} explicitly uses the first kind of information, while we implicitly capture it with a discriminative deep model.
 On the other hand, the second kind of information correlates the image content with the label noise, which can help distinguish between hard samples and mislabeled ones.
@@
 6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ as unlabeled & model \#2 & 73.04\% \\
-7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & 76.22\% \\
-8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & \textbf{78.24\%} \\
+7 & Bottom-Up~\cite{sukhbaatar2014learning} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & 76.22\% \\
+8 & Ours & upsampled $\mathcal{D}_c$ and $\mathcal{D}_{\eta}$ & model \#2 & \textbf{78.24\%} \\
 \hline
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
+\includegraphics[width=0.9\linewidth]{figure/model_output.pdf}
 \caption{Examples of handling noisy labels. The information layout in each block is illustrated in the top-left one.}
@@
 Next, from row \#6 we can see that semi-supervised learning methods may not be a good choice when massive noisy labeled data are available.
-Although model \#6 achieves marginally better result than its base model, it is significantly inferior to model \#5, which indicates that simply discarding all the noisy labels cannot make the full use of these information.
+Although model \#6 achieves marginally better result than its base model, it is significantly inferior to model \#5, which indicates that simply discarding all the noisy labels cannot fully utilize these information.
 
@@
 Next we demonstrate the effect of learning to predict the label noise type.
-We estimate $p(\vec{z}_2=1|\vec{x})+p(\vec{z}_3=1|\vec{x})$ on the validation set and sort the images accordingly in descending order.
+We first estimate $p(\vec{z}_2=1|\vec{x})+p(\vec{z}_3=1|\vec{x})$ on the validation set and sort the images accordingly in descending order.
 Then for each image, we check whether its noisy label mismatches its clean label.
@@
 We proposed a novel probabilistic model to describe how a noisy label is generated.
-Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between the observed image and its noisy label.
+Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between an observed image and its noisy label.
 We solved the problem by the EM algorithm and integrated it into a deep learning framework.

### 2015-04-10 ext.tex
Polish the extended abstract

@@
 \noindent
-Deep learning with large-scale supervised training data has shown very impressive improvement on image classification challenge~\cite{krizhevsky2012imagenet}.
+Deep learning from large-scale supervised training dataset has shown very impressive improvement on image classification challenge~\cite{krizhevsky2012imagenet}.
 However, it requires reliable annotations from millions of images which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems.
@@
 Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels.
-Semi-supervised learning methods~\cite{lee2013pseudo} can also be employed by simply discarding all the noisy labels.
+Semi-supervised learning methods~\cite{lee2013pseudo} can be employed by simply discarding all the noisy labels.
 Researchers have also studied the transferability of Convolutional Neural Networks (CNNs) by finetuning an ImageNet pretrained model on smaller datasets of specific tasks~\cite{oquab2014learning}.
@@
 Our proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
-We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
+We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the deep learning framework.
 Experiments on the collected dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.

### 2015-04-11 paper.tex
Remove unused packages. Polish the exp and conclusion sections

@@
 \usepackage{amsthm}
-\usepackage{algorithm2e}
 \usepackage{authblk}
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-\usepackage{fontspec}
 
@@
 
-\RestyleAlgo{boxruled}
-
 %%%%%%%%% TITLE
 \title{Learning From Massive Noisy Labeled Data for Image Classification}
-
 \author[1]{Tong Xiao}
@@
 \author[1]{Xiaogang Wang}
-
 \affil[1]{The Chinese University of Hong Kong}
 \affil[2]{Baidu Research}
-
 \renewcommand\Authands{, and }
@@
 \maketitle
-%\thispagestyle{empty}
+\thispagestyle{empty}
 
@@
 \begin{center}
-\includegraphics[width=0.85\linewidth]{figure/overview.pdf}
+\includegraphics[width=1.0\linewidth]{figure/overview.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\linewidth]{figure/noise_cluster.pdf}
+\includegraphics[width=1.0\linewidth]{figure/noise_cluster.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{figure/pgm.pdf}
+\includegraphics[width=0.6\linewidth]{figure/pgm.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\linewidth]{figure/diagram.pdf}
+\includegraphics[width=1.0\linewidth]{figure/diagram.pdf}
 \end{center}
@@
 While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.
-
-% The forward procedure is summarized in Algorithm~\ref{alg:forward}, and the backward pass for computing gradient with respect to $p(\vec{y}|\vec{x})$ is illustrated in Algorithm~\ref{alg:backward}.
-
-% \begin{algorithm}
-%     \SetKwData{Sum}{sum}
-%     \SetKwFunction{Softmax}{Softmax}\SetKwFunction{Q}{Q}
-%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-
-%     \Input{Observed weak label vector $\tilde{\vec{y}}$ of size $N$}
-%     \Input{Object class scores matrix $Y$ of size $N \times L$}
-%     \Input{Noise type scores matrix $Z$ of size $N \times 3$}
-%     \Output{Posterior probability matrix $P$ of size $L \times 3$}
-%     \BlankLine
-
-%     $P_y \leftarrow$ \Softmax{$Y$}\;
-%     $P_z \leftarrow$ \Softmax{$Z$}\;
-%     \BlankLine
-
-%     \emph{\Q is the function that implements Eq~\eqref{eq:likelihood}}\;
-%     \BlankLine
-
-%     \For {$i \leftarrow 1$ \KwTo $N$} {
-%         \Sum $\leftarrow 0$\;
-%         \For {$j \leftarrow 1$ \KwTo $L$} {
-%             \For {$k \leftarrow 1$ \KwTo $3$} {
-%                 $P[i,j,k] \leftarrow P_y[i,j] \times P_z[i,k] \times$ \Q{$\tilde{\vec{y}}$,j,k}\;
-%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-%             }
-%         }
-%         $P[i,:,:] \leftarrow P[i,:,:] /$ \Sum\;
-%     }
-
-%     \caption{Forward pass}
-%     \label{alg:forward}
-% \end{algorithm}
-% \begin{algorithm}
-%     \SetKwData{Sum}{sum}
-%     \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-
-%     \Input{Object class scores matrix $Y$ of size $N \times L$}
-%     \Input{Posterior probability matrix $P$ of size $L \times 3$}
-%     \Output{Gradient matrix $\Delta_Y$ of size $N \times L$}
-%     \BlankLine
-
-%     \For {$i \leftarrow 1$ \KwTo $N$} {
-%         \For {$j \leftarrow 1$ \KwTo $L$} {
-%             \Sum $\leftarrow 0$\;
-%             \For {$k \leftarrow 1$ \KwTo $3$} {
-%                 \Sum $\leftarrow$ \Sum$+ P[i,j,k]$\;
-%             }
-%             $\Delta_Y[i,:] \leftarrow \Delta_Y[i,:] + $ \Sum $\times Y[i,:]$\;
-%             $\Delta_Y[i,j] \leftarrow \Delta_Y[i,j] - $ \Sum\;
-%         }
-%     }
-
-%     \caption{Backward pass for computing gradient w.r.t. object class scores}
-%     \label{alg:backward}
-% \end{algorithm}
 
@@
 
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{c|c|c}
-% \hline
-% \# & Validation Accuracy & Test Accuracy \\
-% \hline\hline
-% 1 & 64.28\% & 64.54\% \\
-% \hline
-% 2 & 72.21\% & 72.63\% \\
-% \hline
-% 3 & 73.76\% & 74.03\% \\
-% \hline
-% 4 & 75.06\% & 75.13\% \\
-% \hline
-% 5 & 75.57\% & 75.30\% \\
-% \hline
-% 6 & 73.10\% & 73.04\% \\
-% \hline
-% 7 & 75.97\% & 76.22\% \\
-% \hline
-% 8 & \textbf{77.65\%} & \textbf{78.24\%} \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Classification accuracies on validation and test set}
-% \label{tab:accuracy}
-% \end{table}
-
 \begin{figure*}
 \begin{center}
-\includegraphics[width=0.9\linewidth]{figure/model_output.pdf}
+\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
 \caption{Examples of handling noisy labels. The information layout in each block is illustrated in the top-left one.}
@@
 
-\subsection{Evaluation on Synthetic Dataset} % (fold)
+\subsection{Evaluation on CIFAR-10 with Synthetic Noises} % (fold)
 \label{sub:evaluation_on_synthetic_dataset}
@@
 We first randomly generate a confusion matrix $Q$ between clean labels and noisy labels, and then corrupt the training labels according to it.
-Based on Caffe's CIFAR10-quick model, we compare~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
+Based on Caffe's CIFAR10-quick model, we compare the~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
 The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
@@
 It should be noticed that~\cite{sukhbaatar2014learning} assumed the distribution of noisy labels only depends on classes, while we assume it also depends on image content.
-This kind of synthetic label noise exactly matches their assumption but is unfavored to our model.
+Label noises generated in the synthetic experiments exactly match their assumption but are unfavored to our model.
 Thus the noise type predictions in our model could be less informative.
-Nevertheless, our model achieves comparable results with~\cite{sukhbaatar2014learning}.
+Nevertheless, our model achieves comparable performances with~\cite{sukhbaatar2014learning}.
 % subsection evaluation_on_synthetic_dataset (end)
@@
 \label{sub:effect_of_noise_estimation}
-In order to understand how does our model handle noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
-We can see that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label, and then use it as supervision instead of the noisy one.
-Another interesting observation is that if $p(\vec{y}|\vec{x})$ or $p(\vec{z}|\vec{x})$ goes wrong, our model can still figure out the correct label.
+In order to understand how our model handles noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
+We find that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label and then replaces the noisy one with it as supervision.
+Another interesting observation is that our model can still figure out the correct label if the prediction of the class label $p(\vec{y}|\vec{x})$ or the noise type $p(\vec{z}|\vec{x})$ goes wrong.
+These two latent variables compensate with each other to help the system distinguish between hard samples and noisy labeled ones.
 
-Next we demonstrate the effect of learning to predict the label noise type.
-We first estimate $p(\vec{z}_2=1|\vec{x})+p(\vec{z}_3=1|\vec{x})$ on the validation set and sort the images accordingly in descending order.
+Next we demonstrate the effectiveness of learning to predict the label noise type.
+Notice that if an image has low probability of ``noise free'' (\ie, $p(\vec{z}_1=1|\vec{x})$ is small), then our model will believe it is likely to be mislabeled.
+In order to check the reliability of these predictions, we first estimate $p(\vec{z}_1=1|\vec{x})$ on the validation set and sort the images accordingly in ascending order.
 Then for each image, we check whether its noisy label mismatches its clean label.
 The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
-It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to help handle noisy labels.
+It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to identify potentially mislabeled images.
 
@@
 \label{sec:conclusion}
-In this paper, we raised the problem of training a classifier with limited clean annotations and massive noisy labeled data.
-We proposed a novel probabilistic model to describe how a noisy label is generated.
-Two latent variables --- true label and noise type --- were introduced to bridge the semantic gap between an observed image and its noisy label.
-We solved the problem by the EM algorithm and integrated it into a deep learning framework.
-Experiments on a collected large-scale clothing dataset showed that massive noisy label data could benefit the training of deep models, and utilizing our method could further improve the performance.
+In this paper, we address the problem of training a deep learning classifier with massive amount of noisy labeled training data and a small amount of clean annotations which are generally easy to collect.
+To utilize both limited clean labels and massive noisy labels, we propose a novel probabilistic framework to describe how noisy labels are produced.
+We introduce two latent variables, the true label and the noise type, to bridge the gap between an input image and its noisy label.
+We observe that the label noises not only depend on the ambiguity between classes, but could follow similar visual patterns as well.
+We build the dependency of the noise type \wrt Images, and infer the ground truth label with EM algorithm.
+We integrate the probabilistic model into a deep learning framework and demonstrate the effectiveness of our method on a large-scale real-world clothing classification dataset.
 % section conclusion (end)

### 2015-04-11 ext.tex
Polish punctuations

@@
 
-\title{Learning From Massive Noisy Labeled Data for Image Classification}
+\title{Learning from Massive Noisy Labeled Data for Image Classification}
 \addauthor{
@@
 Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively.
-Figure~\ref{fig:overview} shows the framework of our approach.
+Fig.~\ref{fig:overview} shows the framework of our approach.
 We collect $1,000,000$ clothing images from online shopping websites.
@@
 By examining the collected dataset, we find that this assumption is too strong to fit real-world data well.
-For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
+For example, in Fig.~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
@@
 \begin{itemize}
-\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\emph{e.g}, the samples with ``?'' in Figure~\ref{fig:overview}).
+\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\emph{e.g}, the samples with ``?'' in Fig.~\ref{fig:overview}).
 \item \textbf{Pure random noise} makes the noisy label totally wrong.
-It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\emph{e.g.}, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
+It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\emph{e.g.}, the samples with ``$\times$'' in Fig.~\ref{fig:overview}).
 \end{itemize}

### 2015-04-11 paper.tex
Polish punctuations

@@
 \usepackage{authblk}
+\usepackage[nocompress]{cite}
 
@@
 %%%%%%%%% TITLE
-\title{Learning From Massive Noisy Labeled Data for Image Classification}
+\title{Learning from Massive Noisy Labeled Data for Image Classification}
 \author[1]{Tong Xiao}
@@
 By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
-For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
+For example, in Fig.~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
@@
 \begin{itemize}
-\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Figure~\ref{fig:overview}).
+\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Fig.~\ref{fig:overview}).
 \item \textbf{Pure random noise} makes the noisy label totally wrong.
-It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
+It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\eg, the samples with ``$\times$'' in Fig.~\ref{fig:overview}).
 \end{itemize}
@@
 To be specific, we have a noisy labeled dataset $\mathcal{D}_{\eta}=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
-We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
+We describe how the noisy label is generated by using a probabilistic graphical model shown in Fig.~\ref{fig:noise_pgm}.
 
@@
 \begin{enumerate}
-    \item The label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$
-    \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$
-    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are confusing with $\vec{y}$
+    \item The label is noise free, \ie, $\tilde{\vec{y}}$ should be equal to $\vec{y}$.
+    \item The label suffers from a pure random noise, \ie, $\tilde{\vec{y}}$ can take any possible value other than $\vec{y}$.
+    \item The label suffers from a confusing noise, \ie, $\tilde{\vec{y}}$ can take several values that are confusing with $\vec{y}$.
 \end{enumerate}
@@
         \frac{1}{L-1}\tilde{\vec{y}}^{T}(\mat{U} - \mat{I})\vec{y} & \text{if } \vec{z}_2 = 1 \\
-        \tilde{\vec{y}}^{T}\mat{C}\vec{y} & \text{if } \vec{z}_3 = 1
+        \tilde{\vec{y}}^{T}\mat{C}\vec{y} & \text{if } \vec{z}_3 = 1,
     \end{cases}
@@
 where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are ones), $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denotes the confusion probability between classes $i$ and $j$.
-Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$:
+Then we can derive from Fig.~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$,
 \begin{equation} \label{eq:joint_distribution}
-  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x})
+  p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}) = p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{y} | \vec{x}) p(\vec{z} | \vec{x}).
 \end{equation}
@@
 Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes.
-Some examples are shown in Figure~\ref{fig:compare_noise_level}.
+Some examples are shown in Fig.~\ref{fig:compare_noise_level}.
 
@@
 
-To illustrate the relations between noisy and true labels, we derive their conditional probability from Eq~\ref{eq:joint_distribution}
+To illustrate the relations between noisy and true labels, we derive their conditional probability from Eq.~\ref{eq:joint_distribution},
 \begin{equation}
-    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x})
+    p(\tilde{\vec{y}} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}}, \vec{z} | \vec{y}, \vec{x}) = \sum_{\vec{z}} p(\tilde{\vec{y}} | \vec{y}, \vec{z}) p(\vec{z} | \vec{x}),
 \end{equation}
@@
     \log p(\tilde{\vec{y}} | \vec{x}; \theta) &= \log \sum_{\vec{y},\vec{z}} p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta) \\
-    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}
+    &\geq \sum_{\vec{y},\vec{z}} q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) \log \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)}{q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x})}.
 \end{aligned}
@@
 \textbf{E-Step} The difference between $\log p(\tilde{\vec{y}} | \vec{x}; \theta)$ and its lower bound is the Kullback-Leibler divergence $\mathrm{KL}\left(q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) || p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)\right)$, which is equal to zero if and only if $q(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}) = p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta)$.
-Therefore, in each iteration $t$, we first compute the posterior of latent variables using the current parameters $\theta^{(t)}$:
+Therefore, in each iteration $t$, we first compute the posterior of latent variables using the current parameters $\theta^{(t)}$,
 \begin{multline} \label{eq:posterior}
     p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) = \frac{p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta^{(t)})}{p(\tilde{\vec{y}} | \vec{x}; \theta^{(t)})} \\
-    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}
+    = \frac{p(\tilde{\vec{y}}|\vec{y},\vec{z};\theta^{(t)}) p(\vec{y}|\vec{x};\theta^{(t)}) p(\vec{z}|\vec{x};\theta^{(t)})}{\sum_{\vec{y}',\vec{z}'} p(\tilde{\vec{y}}|\vec{y}',\vec{z}';\theta^{(t)}) p(\vec{y}'|\vec{x};\theta^{(t)}) p(\vec{z}'|\vec{x};\theta^{(t)})}.
 \end{multline}
@@
 \begin{equation}
-    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta)
+    Q(\theta; \theta^{(t)}) = \sum_{\vec{y},\vec{z}} p(\vec{y}, \vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \log p(\tilde{\vec{y}}, \vec{y}, \vec{z} | \vec{x}; \theta).
 \end{equation}
@@
     = \sum_{\vec{y}} p(\vec{y} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_1} \log p(\vec{y}|\vec{x};\theta_1) + \\
-      \sum_{\vec{z}} p(\vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2)
+      \sum_{\vec{z}} p(\vec{z} | \tilde{\vec{y}}, \vec{x}; \theta^{(t)}) \frac{\partial}{\partial \theta_2} \log p(\vec{z}|\vec{x};\theta_2).
 \end{multline}
@@
 \label{sub:confusion_estimation}
-Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq~\eqref{eq:likelihood} and keep it unchanged during the learning process.
-Because without other regularizations, learning all the three parts in Eq~\eqref{eq:joint_distribution} could lead to trivial solutions.
+Notice that we do not set parameters to the conditional probability $p(\tilde{\vec{y}}|\vec{y},\vec{z})$ in Eq.~\eqref{eq:likelihood} and keep it unchanged during the learning process.
+Because without other regularizations, learning all the three parts in Eq.~\eqref{eq:joint_distribution} could lead to trivial solutions.
 For example, the network will always predict $\vec{y}_1 = 1$, $\vec{z}_3 = 1$, and the matrix $\mat{C}$ is learned to make $\mat{C}_{1i} = 1$ for all $i$.
@@
 \begin{equation} \label{eq:opt_all}
-    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)})
+    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)}).
 \end{equation}
 Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal.
-So that we discard those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
+So that we discard those samples and reinterpret the problem in another form by exploiting Eq.~\eqref{eq:likelihood}:
 \begin{equation}
 \begin{aligned}
-\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
-\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L \\
-                    & \vec{t} \in \{0,1\}^{N'}
+\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i},\\
+\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L, \\
+                    & \vec{t} \in \{0,1\}^{N'},
 \end{aligned}
@@
 \begin{theorem}
-$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,L\}$
+$\mat{C}^*_{ij} \neq 0 \Rightarrow \mat{C}^*_{ij} > \alpha, \forall i,j \in \{1,\dots,L\}$.
 \end{theorem}
@@
 \begin{theorem}
-$(\tilde{\vec{y}}^{(i)},\vec{y}^{(i)})=(\tilde{\vec{y}}^{(j)},\vec{y}^{(j)}) \Rightarrow \vec{t}^*_i=\vec{t}^*_j, \forall i,j \in \{1,\dots,N'\}$
+$(\tilde{\vec{y}}^{(i)},\vec{y}^{(i)})=(\tilde{\vec{y}}^{(j)},\vec{y}^{(j)}) \Rightarrow \vec{t}^*_i=\vec{t}^*_j, \forall i,j \in \{1,\dots,N'\}$.
 \end{theorem}
@@
 \begin{theorem}
-$\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} > \alpha \Leftrightarrow \vec{t}^*_i=0$ and $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0 \Leftrightarrow \vec{t}^*_i=1, \forall i \in \{1,\dots,N'\}$
+$\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} > \alpha \Leftrightarrow \vec{t}^*_i=0$ and $\tilde{\vec{y}}^{(i)T} \mat{C}^* \vec{y}^{(i)} = 0 \Leftrightarrow \vec{t}^*_i=1, \forall i \in \{1,\dots,N'\}$.
 \end{theorem}
@@
 \begin{aligned}
-    &\vec{t}^*_i = 0, i = 1,\dots,k^* \\
+    &\vec{t}^*_i = 0, i = 1,\dots,k^*, \\
     &\vec{t}^*_i = 1, i = k^*+1,\dots,L.
@@
 We enumerate $k^*$ from 1 to $L$.
-For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively.
+For each $k^*$, $\vec{t}^*$ and $\vec{c}^*$ are computed by using Eq.~\eqref{eq:opt_t} and~\eqref{eq:opt_c}, respectively.
 Then we evaluate the objective function $E$ and record the best solution.
@@
 We integrate the proposed label noise model into a deep learning framework.
-As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
+As demonstrated in Fig.~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
 Moreover, we append a label noise model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
 Stochastic Gradient Ascent with backpropagation technique is used to approximately optimize the whole network.
-In each forward pass, the label noise model layer computes the posterior of latent variables according to Eq~\eqref{eq:posterior}.
-While in the backward pass, it computes the gradients according to Eq~\eqref{eq:gradient}.
+In each forward pass, the label noise model layer computes the posterior of latent variables according to Eq.~\eqref{eq:posterior}.
+While in the backward pass, it computes the gradients according to Eq.~\eqref{eq:gradient}.
 
@@
 Images and their ground truth labels in the dataset $\mathcal{D}_c$ are used to train the CNN that predicts $p(\vec{y}|\vec{x})$.
-On the other hand, the optimal solutions of $\vec{z}^{(1)},\cdots,\vec{z}^{(N)}$ in Eq~\eqref{eq:opt_all} are used to train the CNN that predicts $p(\vec{z}|\vec{x})$.
+On the other hand, the optimal solutions of $\vec{z}^{(1)},\cdots,\vec{z}^{(N)}$ in Eq.~\eqref{eq:opt_all} are used to train the CNN that predicts $p(\vec{z}|\vec{x})$.
 
@@
 First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
-Therefore, we need to mix the data with clean labels into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
+Therefore, we need to mix the data with clean labels into our training set, which is depicted in Fig.~\ref{fig:framework} as the extra supervisions for the two CNNs.
 Then each CNN receives two kinds of gradients, one is from the clean labels and the other is from the noisy labels.
@@
 
-The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}.
+The confusion matrix between clean and noisy labels is presented in Fig.~\ref{fig:cm_strong_weak}.
 We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater), which means that the noisy labels are not so reliable.
@@
 The other one is the Bottom-Up method introduced in~\cite{sukhbaatar2014learning}, where the relation between noisy labels and clean labels are built by a confusion matrix $Q$.
-In the experiments, we directly use the true $Q$ as shown in Figure~\ref{fig:cm_strong_weak} instead of estimating its values.
+In the experiments, we directly use the true $Q$ as shown in Fig.~\ref{fig:cm_strong_weak} instead of estimating its values.
 
-We list all the experiment settings in Table~\ref{tab:exp}.
+We list all the experiment settings in Tab.~\ref{tab:exp}.
 Different methods require different training data.
 We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions.
-On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
+On the other hand, when all the data are used, we upsample the clean data as discussed in Sec.~\ref{sec:deep_learning_from_noisy_labels}.
 Meanwhile, the noisy labels of $\mathcal{D}_{\eta}$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
@@
 We keep training each model until convergence.
-Classification accuracies on the test set are presented in Table~\ref{tab:exp}.
+Classification accuracies on the test set are presented in Tab.~\ref{tab:exp}.
 
@@
 Based on Caffe's CIFAR10-quick model, we compare the~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
-The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
+The test accuracies are reported in Tab.~\ref{tab:accuracy_synthetic}.
 
@@
 \label{sub:effect_of_noise_estimation}
-In order to understand how our model handles noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
+In order to understand how our model handles noisy labels, we first show several examples in Fig.~\ref{fig:model_output}.
 We find that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label and then replaces the noisy one with it as supervision.
@@
 Then for each image, we check whether its noisy label mismatches its clean label.
-The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
+The rank-precision curve is plotted in Fig.~\ref{fig:noise_prediction_rp}.
 It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to identify potentially mislabeled images.

### 2015-04-13 paper.tex
Update exp and conclusion

@@
 Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively.
-Fig.~\ref{fig:overview} shows the framework of our approach.
+Figure~\ref{fig:overview} shows the framework of our approach.
 We collect $1,000,000$ clothing images from online shopping websites.
@@
 By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
-For example, in Fig.~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
+For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
 The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''.
@@
 \begin{itemize}
-\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Fig.~\ref{fig:overview}).
+\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\eg, the samples with ``?'' in Figure~\ref{fig:overview}).
 \item \textbf{Pure random noise} makes the noisy label totally wrong.
-It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\eg, the samples with ``$\times$'' in Fig.~\ref{fig:overview}).
+It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\eg, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
 \end{itemize}
@@
 To be specific, we have a noisy labeled dataset $\mathcal{D}_{\eta}=\left\{\left(\vec{x}^{(1)}, \tilde{y}^{(1)}\right), \dots, \left(\vec{x}^{(N)}, \tilde{y}^{(N)}\right)\right\}$ with $n$-th image $\vec{x}^{(n)}$ and its corresponding noisy label $\tilde{y}^{(n)} \in \{1,\dots,L\}$, where $L$ is the number of classes.
-We describe how the noisy label is generated by using a probabilistic graphical model shown in Fig.~\ref{fig:noise_pgm}.
+We describe how the noisy label is generated by using a probabilistic graphical model shown in Figure~\ref{fig:noise_pgm}.
 
@@
 where $\mat{I}$ is the identity matrix, $\mat{U}$ is the unit matrix (all the elements are ones), $\mat{C}$ is a sparse stochastic matrix with $\mathrm{tr}(\mat{C})=0$ and $\mat{C}_{ij}$ denotes the confusion probability between classes $i$ and $j$.
-Then we can derive from Fig.~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$,
+Then we can derive from Figure~\ref{fig:noise_pgm} the joint distribution of $\tilde{\vec{y}}, \vec{y}$ and $\vec{z}$ conditioning on $\vec{x}$,
 \begin{equation} \label{eq:joint_distribution}
@@
 Specific to our clothing classification problem, $p(\vec{z} | \vec{x})$ can be affected by different factors, including background clutter, image resolution, the style and material of the clothes.
-Some examples are shown in Fig.~\ref{fig:compare_noise_level}.
+Some examples are shown in Figure~\ref{fig:compare_noise_level}.
 
@@
 We integrate the proposed label noise model into a deep learning framework.
-As demonstrated in Fig.~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
+As demonstrated in Figure~\ref{fig:framework}, we predict the probability $p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ by using two independent CNNs.
 Moreover, we append a label noise model layer at the end, which takes as input the CNNs' prediction scores and the observed noisy label.
@@
 First, if we merely use noisy labels, we will lose precious knowledge that we have gained before and the model could be drifted.
-Therefore, we need to mix the data with clean labels into our training set, which is depicted in Fig.~\ref{fig:framework} as the extra supervisions for the two CNNs.
+Therefore, we need to mix the data with clean labels into our training set, which is depicted in Figure~\ref{fig:framework} as the extra supervisions for the two CNNs.
 Then each CNN receives two kinds of gradients, one is from the clean labels and the other is from the noisy labels.
@@
 
-The confusion matrix between clean and noisy labels is presented in Fig.~\ref{fig:cm_strong_weak}.
+The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}.
 We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater), which means that the noisy labels are not so reliable.
@@
 The other one is the Bottom-Up method introduced in~\cite{sukhbaatar2014learning}, where the relation between noisy labels and clean labels are built by a confusion matrix $Q$.
-In the experiments, we directly use the true $Q$ as shown in Fig.~\ref{fig:cm_strong_weak} instead of estimating its values.
+In the experiments, we directly use the true $Q$ as shown in Figure~\ref{fig:cm_strong_weak} instead of estimating its values.
 
-We list all the experiment settings in Tab.~\ref{tab:exp}.
+We list all the experiment settings in Table~\ref{tab:exp}.
 Different methods require different training data.
 We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions.
-On the other hand, when all the data are used, we upsample the clean data as discussed in Sec.~\ref{sec:deep_learning_from_noisy_labels}.
+On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}.
 Meanwhile, the noisy labels of $\mathcal{D}_{\eta}$ are treated as true labels for AlexNet, and are discarded for Pseudo-Label.
@@
 We keep training each model until convergence.
-Classification accuracies on the test set are presented in Tab.~\ref{tab:exp}.
+Classification accuracies on the test set are presented in Table~\ref{tab:exp}.
 
@@
 Based on Caffe's CIFAR10-quick model, we compare the~\cite{sukhbaatar2014learning} (Bottom Up with true $Q$) with our model under different noise levels.
-The test accuracies are reported in Tab.~\ref{tab:accuracy_synthetic}.
+The test accuracies are reported in Table~\ref{tab:accuracy_synthetic}.
 
@@
 \label{sub:effect_of_noise_estimation}
-In order to understand how our model handles noisy labels, we first show several examples in Fig.~\ref{fig:model_output}.
+In order to understand how our model handles noisy labels, we first show several examples in Figure~\ref{fig:model_output}.
 We find that given a noisy label, our model exploits its current knowledge to estimate the probability distribution of the true label and then replaces the noisy one with it as supervision.
@@
 Then for each image, we check whether its noisy label mismatches its clean label.
-The rank-precision curve is plotted in Fig.~\ref{fig:noise_prediction_rp}.
-It shows that the intuitive observation --- mislabeled images often share similar patterns --- is reasonable, and our model is trained to recognize such patterns to identify potentially mislabeled images.
+The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
+It shows that our model can identify mislabeled samples quite well based on their image content, which verifies the observation that mislabeled images often share similar visual patterns.
 
@@
 \label{sec:conclusion}
-In this paper, we address the problem of training a deep learning classifier with massive amount of noisy labeled training data and a small amount of clean annotations which are generally easy to collect.
+In this paper, we address the problem of training a deep learning classifier with a massive amount of noisy labeled training data and a small amount of clean annotations which are generally easy to collect.
 To utilize both limited clean labels and massive noisy labels, we propose a novel probabilistic framework to describe how noisy labels are produced.
@@
 We observe that the label noises not only depend on the ambiguity between classes, but could follow similar visual patterns as well.
-We build the dependency of the noise type \wrt Images, and infer the ground truth label with EM algorithm.
+We build the dependency of the noise type \wrt images, and infer the ground truth label with the EM algorithm.
 We integrate the probabilistic model into a deep learning framework and demonstrate the effectiveness of our method on a large-scale real-world clothing classification dataset.

### 2015-04-13 paper.tex
Update paper.tex
Update abstract

@@
 Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems.
-However, obtaining a massive amount of well labeled data is usually very expensive and time consuming.
+However, obtaining a massive amount of well-labeled data is usually very expensive and time consuming.
 In this paper, we introduce a general framework to train CNNs with only a limited number of clean labels and millions of easily obtained noisy labels.
-We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system.
-To demonstrate the effectiveness of our approach, we collect a large-scale clothing classification dataset with both noisy and clean labels.
-Experiments on this dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
+We model the relationships between images, class labels and label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system.
+To demonstrate the effectiveness of our approach, we collect a large-scale real-world clothing classification dataset with both noisy and clean labels.
+Experiments on this dataset indicate that our approach can better correct the noisy labels and improves the performance of trained CNNs.
 \end{abstract}

### 2015-04-13 paper.tex
Update paper.tex
Modify the introduction and related work

@@
 
-Deep learning from large-scale supervised training dataset has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
+Deep learning with large-scale supervised training dataset has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2014panda}, and scene classification~\cite{farabet2013learning}.
 While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain, preventing deep models from being quickly trained on new image recognition problems.
@@
 
-One possible solution is to automatically collect large amount of annotations from the Internet web images~\cite{gong2014multiview} (\ie extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
+One possible solution is to automatically collect a large amount of annotations from the Internet web images~\cite{gong2014multiview} (\ie extracting tags from the surrounding texts or keywords from search engines) and directly use them as ground truth to train deep models.
 Unfortunately, these labels are extremely unreliable due to various types of noise (\eg labeling mistakes from annotators or computing errors from extraction algorithms).
-Many works have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
+Many studies have shown that these noisy labels could adversely impact the classification accuracy of the induced classifiers~\cite{zhu2004class,nettleton2010study,pechenizkiy2006class}.
 Various label noise-robust algorithms are developed but experiments show that performances of classifiers inferred by robust algorithms are still affected by label noise~\cite{bartlett2006convexity,teng2001comparison}.
@@
 These algorithms usually suffer from model complexity thus cannot be applied on large-scale datasets.
-Therefore, it is inevitable to develop a better way of using huge amount of noisy labeled data.
+Therefore, it is inevitable to develop a better way of using the huge amount of noisy labeled data.
 
@@
 To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the true labels and uses them to supervise the training of the network.
-Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
-However,~\cite{sukhbaatar2014learning} assumed noisy labels are conditionally independent with input images given clean labels.
-By examining our collected dataset, we find that this assumption is too strong to fit real-world data well.
+Our work is inspired by~\cite{sukhbaatar2014learning}, which modifies a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels.
+However,~\cite{sukhbaatar2014learning} assumes noisy labels are conditionally independent of input images given clean labels.
+However, when examining our collected dataset, we find that this assumption is too strong to fit the real-world data well.
 For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''.
@@
 Since different sellers have their own bias on different categories, they may provide wrong keywords for similar clothes.
-We can capture these visual patterns to estimate how likely an image is mislabeled.
+We observe these visual patterns and hypothesize that they are important to estimate how likely an image is mislabeled.
 Based on these observations, we further introduce two types of label noise:
@@
 
-The proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
+Our proposed probabilistic model captures the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables.
 We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs.
-Experiments on the collected dataset show that our model can better detect and correct the wrong labels.
+Experiments on our real-world clothing dataset indicate that our model can better detect and correct the noisy labels.
 
-Our contribution comes from three aspects.
+Our contributions fall in three aspects.
 First, we study the cause of noisy labels in real-world data and describe it with a novel probabilistic model.
-Second, we integrate the model into a deep learning framework to help detect and correct wrong labels.
-We study different training strategies to make the CNNs learn from better supervisions.
+Second, we integrate the model into a deep learning framework and explore different training strategies to make the CNNs learn from better supervisions.
 Finally, we collect a large-scale clothing dataset with both noisy and clean labels, which will be released for academic use.
@@
 \label{sec:related_work}
-For most of the related works including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2014classification} for a comprehensive review.
+Learning with noisy labeled training data has been extensively studied in the machine learning and computer vision literature.
+For most of the related work including the effect of label noises, taxonomy of label noises, robust algorithms and noise cleaning algorithms for learning with noisy data, we refer to~\cite{frenay2014classification} for a comprehensive review.
 
-{\bf Direct learning with noisy labels:} Many works have shown that label noise can adversely impact the classification accuracy of induced classifiers~\cite{zhu2004class}.
+{\bf Direct learning with noisy labels:} Many studies have shown that label noises can adversely impact the classification accuracy of induced classifiers~\cite{zhu2004class}.
 To better handle label noise, some approaches rely on training classifiers with label noise-robust algorithms~\cite{beigman2009learning,manwani2013noise}.
-However, Bartlett \etal~\cite{bartlett2006convexity} proved that most of the loss functions are not completely robust to label noise.
-Experiments in~\cite{teng2001comparison} showed that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
+However, Bartlett \etal~\cite{bartlett2006convexity} prove that most of the loss functions are not completely robust to label noise.
+Experiments in~\cite{teng2001comparison} show that the classifiers inferred by label noise-robust algorithms are still affected by label noise.
 These methods seem to be adequate only when label noise can be safely managed by overfitting avoidance~\cite{frenay2014classification}.

### 2015-04-14 paper.tex
Final version for camera ready

@@
 \begin{center}
-\includegraphics[width=0.6\linewidth]{figure/pgm.pdf}
+\includegraphics[width=0.5\linewidth]{figure/pgm.pdf}
 \end{center}
@@
 
-The label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three different semantic meanings:
+The label noise type $\vec{z}$ is an 1-of-3 binary random variable. It is associated with three semantic meanings:
 \begin{enumerate}
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/diagram.pdf}
+\includegraphics[width=0.85\linewidth]{figure/diagram.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/cm_strong_weak_labels.pdf}
+\includegraphics[width=0.9\linewidth]{figure/cm_strong_weak_labels.pdf}
 \end{center}
@@
 \end{center}
-\caption{Experiment results on the collected dataset}
+\caption{Experimental results on the clothing classification dataset. $\mathcal{D}_c$ contains $47,570$ clean labels while $\mathcal{D}_{\eta}$ contains $10^6$ noisy labels.}
 \label{tab:exp}
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{figure/model_output.pdf}
-\caption{Examples of handling noisy labels. The information layout in each block is illustrated in the top-left one.}
+\includegraphics[width=0.95\linewidth]{figure/model_output.pdf}
+\caption{Examples of handling noisy labels.
+The information layout for each block is illustrated on the top-left.
+$p(\vec{y}|\vec{x})$ and $p(\vec{z}|\vec{x})$ are predictions of the true label and noise type based on image content.
+After observing the noisy label, our model infers the posterior distributions $p(\vec{y}|\vec{\tilde{y}},\vec{x})$ and $p(\vec{z}|\vec{\tilde{y}},\vec{x})$, then replaces the $\vec{y}$ and $\vec{z}$ with them as supervisions to the CNNs.}
 \label{fig:model_output}
@@
 \hline
-Noise Level & Base Model & \cite{sukhbaatar2014learning} & Ours \\
+Noise Level & CIFAR10-quick & \cite{sukhbaatar2014learning} & Ours \\
 \hline\hline
@@
 \end{center}
-\caption{Accuracies on CIFAR-10 with synthetic label noise}
+\caption{Accuracies on CIFAR-10 with synthetic label noises.
+The label noises generated here only depend on the true labels but not the image content, which exactly match the assumption of~\cite{sukhbaatar2014learning} but are unfavored to our model.}
 \label{tab:accuracy_synthetic}
@@
 Notice that if an image has low probability of ``noise free'' (\ie, $p(\vec{z}_1=1|\vec{x})$ is small), then our model will believe it is likely to be mislabeled.
-In order to check the reliability of these predictions, we first estimate $p(\vec{z}_1=1|\vec{x})$ on the validation set and sort the images accordingly in ascending order.
-Then for each image, we check whether its noisy label mismatches its clean label.
+In order to check the reliability of these predictions, we estimate $p(\vec{z}_1=1|\vec{x})$ on the validation set and sort the images accordingly in ascending order.
+For the precision calculation, we consider a candidate image as true positive if its clean label mismatches its original noisy label, and our model predicts it as not ``noisy free''.
 The rank-precision curve is plotted in Figure~\ref{fig:noise_prediction_rp}.
@@
 \end{center}
-\caption{Rank-precision curve of label noise predictions}
+\caption{Rank-precision curve of label noise predictions.
+We rank the validation images from low to high according to their ``noise free'' probabilities.
+For the precision calculation, we consider a candidate image as true positive if its clean label mismatches its original noisy label, and our model predicts it as not ``noisy free''.}
 \label{fig:noise_prediction_rp}

### 2015-04-14 figure/make_zstat.py

@@ -16,10 +16,10 @@ def draw_zstat(file_path, output=None, topk=None):
         rank_precision = rank_precision[0:topk]
 
     plt.plot(rank_precision, linewidth=2.5, color='#111111')
-    plt.xlabel('Rank', fontsize=24, fontweight='bold')
-    plt.ylabel('Precision', fontsize=24, fontweight='bold')
+    plt.xlabel('Rank', fontsize=18, fontweight='bold')
+    plt.ylabel('Precision', fontsize=18, fontweight='bold')
     plt.ylim(0.0, 1.0)
-    plt.tick_params(labelsize='large')
+    plt.tick_params(labelsize=18)
 
     fig = plt.gcf()
     fig.set_figheight(6)
